---
title: "bocaccio_observations"
author: "Markus Min"
date: "6/9/2021"
output: html_document
---

### Description
In this document we will describe all recent Bocaccio occurrences through research surveys - by WDFW trawl survey, by ROV observation, and by hook and line surveys.


### Load libraries
```{r load_libraries}
library(tidyverse)
library(tidyverse)
library(readxl)
library(here)
library(rgdal)
library(broom)
library(ggpubr)
library(sf)
library(lubridate)

# Set figure directory
fig_dir <- here("figures", "bocaccio_observations")
```


### Create base map of Puget Sound
```{r PS_base_map}
# Load data
usa_spdf <- readOGR(dsn = here("map_files", "USA_adm0.shp"))

# Convert to df(ish)
usa_spdf_fort <- tidy(usa_spdf)

# Load BC data
BC_shp <- readOGR(dsn = here("map_files", "canada", "lpr_000b16a_e.shp"))
# proj4string(BC_shp)
BC_shp_transform <- spTransform(BC_shp, "+init=epsg:4326")
BC_spdf_fort <- tidy(BC_shp_transform)


# Create map in ggplot

greater_PS_map <- ggplot(usa_spdf_fort, aes(x = long, y = lat, group = group))+
  geom_polygon(color = "gray70", fill = rgb(251, 234, 194, max=255))+
  geom_polygon(data = BC_spdf_fort, aes(x = long, y = lat, group = group), inherit.aes = FALSE, color = "gray70", fill = rgb(251, 234, 194, max=255)) +
  ylab("Latitude")+
  xlab("Longitude")+
  coord_fixed(ylim = c(47.1,48.9),  xlim = c(-124.8,-122.1), ratio = 1.3)+
  theme(plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill="white", color = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank())+
  scale_x_continuous(breaks = c(-124.5, -124, -123.5, -123, -122.5), expand = c(0,0), labels=c(expression(paste(124.5*degree,"W")),
                                                                                expression(paste(124*degree,"W")),
                                                                                expression(paste(123.5*degree,"W")),
                                                                                expression(paste(123*degree,"W")),
                                                                                expression(paste(122.5*degree,"W"))))+
  scale_y_continuous(breaks = seq(47.5, 48.5, 0.5), expand = c(0,0), labels=c(expression(paste(47.5*degree,"N")),
                                                                    expression(paste(48*degree,"N")),
                                                                    expression(paste(48.5*degree,"N"))))+
  # Add line for DPS boundary - from 48.121536, -123.288602 (Green Point) to 48.411782, -123.294625 (McMicking Point in Victoria)
  annotate("segment", x = -123.288602, xend = -123.294625, y = 48.121536, yend = 48.411782, lty = 2, color = "firebrick4")+
  annotate("text", label = "DPS Boundary", x = -123.288602, 48.07, size = 4, color = "firebrick4")
  
```

## WDFW Trawl Survey

### Read in Bocaccio detections
```{r load_bocaccio_survey_data}
boc_bio <- read_excel(here("WDFW_trawl_survey_data", "bocaccio_lf_trawlsurvey.xlsx"))
boc_loc <- read_excel(here("WDFW_trawl_survey_data", "MarkusMin_BocaccioCoordinates_WDFWtrawl.xlsx"))

# Add the survey years
boc_loc$year <- as.character(c(2012, 2016, 2016, 2017, 2017, 2017, 2018, 2018, 2018))
```

### Plot Bocaccio detections - with years summarised
```{r plot_boc_detections}
boc_loc %>% 
  mutate(station = ifelse(TowCode %in% c("12JWWT1", "16JWWU1", "16JWWT1", "17JWWT1", "17JWWU1"), "JWW",
                          ifelse(TowCode == "17JWEV1", "JWE",
                                 ifelse(TowCode == "18JEWV1", "JEW",
                                        ifelse(TowCode == "18GBSV1", "GBS",
                                               ifelse(TowCode == "18SJNV1", "SJN", "Other")))))) %>% 
  group_by(station) %>% 
  mutate(years_seen = paste0(year, collapse = ", ")) %>% 
  distinct(station, years_seen, .keep_all = TRUE) %>% 
  dplyr::select(Start_Latitude, Start_Longitude, station, years_seen) %>% 
  mutate(years_seen = ifelse(years_seen == "2012, 2016, 2016, 2017, 2017", "2012, 2016, 2017", years_seen)) %>% 
  # Add field for inside/outside of DPS
  mutate(DPS = ifelse(Start_Longitude > -123.3, "Inside", "Outside")) -> boc_loc_summarised
  

boc_trawl_survey_map <- greater_PS_map+
  geom_point(data = boc_loc_summarised, aes(x = Start_Longitude, y = Start_Latitude, color = DPS), inherit.aes = FALSE)+
  # Plot all data except one right and above
  geom_text(data = subset(boc_loc_summarised, years_seen != "2017"), aes(x = Start_Longitude+0.01, y = Start_Latitude+0.04, label = years_seen, color = DPS), size = 5, inherit.aes = FALSE, hjust = 0) +
  # Plot 2017 data point right and below
    geom_text(data = subset(boc_loc_summarised, years_seen == "2017"), aes(x = Start_Longitude+0.01, y = Start_Latitude-0.04, label = years_seen, color = DPS), size = 5, inherit.aes = FALSE, hjust = 0)+
  scale_color_manual(values = c("Inside" = "firebrick4", "Outside" = "black"))+
  theme(legend.position = "none")

# boc_trawl_survey_map

ggsave(paste0(fig_dir, "/bocaccio_trawl_survey_map.png"), boc_trawl_survey_map, height = 6, width  = 7.1)
```




### Plot Bocaccio length comps

Look into strong Bocaccio recruitment event in 2016, as was referenced in DFO's assessment
  "There is evidence from the two most important trawl surveys and from the commercial fishery that a strong BOR cohort was spawned in 2016. This stock assessment estimates that this cohort is 44 times (5–95% range: 30–58) the average recruitment (1935-2019) estimated over the 85 year reconstruction period."
```{r plot_boc_lengths}
boc_lengths_plot <- ggplot(boc_bio, aes(x = Length, y = FishCount)) +
  geom_bar(stat = "identity")+
  facet_wrap(vars(SurveyYear)) +
  theme(panel.background = element_rect(fill = "white"))

boc_lengths_plot
```

```{r plot_boc_lengths_v2}
left_join(boc_bio, dplyr::select(boc_loc, TowCode, Start_Latitude, Start_Longitude), by = "TowCode") %>%
  mutate(DPS = ifelse(Start_Longitude > -123.3, "Inside", "Outside")) -> boc_bio

boc_lengths_plot <- ggplot(boc_bio, aes(x = Length, y = FishCount, fill = as.character(SurveyYear), color = DPS))+
  geom_bar(stat = "identity", size = 1) +
  ylab("Number of fish") +
  xlab("Length (cm)")+
  theme(plot.background = element_rect(fill = "white"),
        panel.background = element_rect(fill="white", color = "black"),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(0.9, 0.82),
        legend.text = element_text(size = 20),
        legend.key=element_blank(),
        legend.box.background = element_rect(color = "black"),
        legend.background = element_rect(fill = "gray90"),
        legend.title = element_text(size = 20),
        axis.title = element_text(size = 16),
        axis.text = element_text(size = 12))+
  scale_fill_manual(values = c("#ffffcc", "#a1dab4", "#41b6c4", "#225ea8"), name = "Year")+
  # scale_fill_manual(values = c("#c6dbef", "#6baed6", "#2171b5", "#08306b"), name = "Year")+
  scale_color_manual(values = c("Inside" = "firebrick4", "Outside" = "NA"), guide = FALSE)+
  scale_y_continuous(expand = c(0,0), limits = c(0, 5.5))

ggsave(paste0(fig_dir, "/bocaccio_trawl_survey_lengths.png"), boc_lengths_plot, height = 6, width  = 8)
```

## ROV Data
Bocaccio observations in ROV surveys:
- 2015-16 Puget Sound: 1 Bocaccio
- 2008 ROV survey: 4 Bocaccio

```{r load_ROV_data_15_16_PS}
ROV_data_path <- here("ROV_data")

PS_15_16_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2015-16 PS Species")
PS_15_16_transects <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2015-16 PS Transects")

bocaccio_15_16 <- subset(PS_15_16_species, SpeciesName == "Bocaccio")
# Convert to decimal degrees
bocaccio_15_16 %>% 
  mutate(., latitude = Lat_deg + Lat_decmin/60) %>% 
  mutate(., longitude = Long_deg - Long_decmin/60) %>% 
  dplyr::rename(depth = Depth) %>% 
  # add transect date
  left_join(., PS_15_16_transects, by = "Transect") %>% 
  dplyr::select(Date, depth, FishCount, latitude, longitude) -> bocaccio_15_16_forjoin

```

```{r load_ROV_data_2008}
SJI_2008_boc <- read.csv(paste0(ROV_data_path, "/2008_SJI_ROV_bocaccio.csv"))
SJI_2008_boc %>% 
  rename(latitude = Lat_DD, longitude = Long_DD, depth = Depth_m,
         FishCount = Count) %>% 
  mutate(Date = mdy(Date)) %>% 
  dplyr::select(Date, depth, FishCount, latitude, longitude) -> SJI_2018_boc_forjoin

```

```{r load_ROV_data_site_explorations}
boc_site_exploration <- read_excel(paste0(ROV_data_path, "/NOAA_ROV-ESA5yr_Bocaccio_site_explorations.xlsx"))
# Convert to decimal degrees
boc_site_exploration %>% 
  mutate(., latitude = LatitudeDegree + LatitudeDecimalMinute/60) %>% 
  mutate(., longitude = LongitudeDegree - LongitudeDecimalMinute/60) %>% 
  dplyr::rename(depth = DepthMeter)-> boc_site_exploration
boc_site_exploration %>% 
  dplyr::select(Date, depth, FishCount, latitude, longitude) -> boc_site_exploration_forjoin 
```

```{r join_ROV_boc_obs_reformat}
bocaccio_15_16_forjoin %>% 
  bind_rows(., SJI_2018_boc_forjoin) %>% 
  bind_rows(., boc_site_exploration_forjoin) -> boc_ROV_obs
```


### ROV observation map
```{r ROV_data_map}
boc_ROV_survey_map <- greater_PS_map+
  geom_point(data = boc_ROV_obs, aes(x = longitude, y = latitude), inherit.aes = FALSE)

boc_ROV_survey_map
```



## Hook and Line Data
```{r hook_and_line_bocaccio}

```

