---
title: "catch_reconstruction v2"
author: "Markus Min"
date: "`r format(Sys.time(), '%B %d %Y')`"
toc: TRUE
toc-depth: 3
output: pdf_document
header-includes:
- \usepackage{fancyhdr}
urlcolor: blue
---
\pagestyle{fancy}
\fancyhead[L]{Catch Reconstruction}
\fancyhead[R]{2021 5-year review}
\fancyfoot[C]{\thepage}

### Description
This R markdown file will go through the catch reconstruction of yelloweye rockfish and bocaccio catch in Puget Sound. This document will generate different plausible catch scenarios and address the uncertainty at each step of the analysis. This analysis will go in reverse chronological order and go through commercial catch first and then recreational catch.. For more notes on the catch reconstruction, please see "catch_reconstruction.Rmd" in the same "analysis" folder.
\\
Additionally, in accordance with the [2017 Rockfish Recovery Plan](https://www.fisheries.noaa.gov/resource/document/yelloweye-rockfish-and-bocaccio-recovery-plan), catches for three different geographic areas will be constructed:
1. The entire DPS (Canada and United States), minus the Hood Canal population
2. The Hood Canal population
3. The United States side of the DPS, excluding Hood Canal

### Load libraries, set fig_dir
```{r load_libraries}
library(tidyverse)
library(readxl)
library(here)
library(ggthemes)
library(ggpubr)

fig_dir <- here("figures", "catch_reconstruction")
```


# Commercial data

## 2004-2020

#### Notes:
This data period is characterized by 1) low catches of bocaccio and yelloweye following regulatory changes and 2) relatively high confidence in the data.

##### Catch areas
This data is split by region into the marine fish-shellfish marine catch reporting areas (WDFW). Areas in relation to DPSs:
1) Hood Canal: Regions 27A, 27B, and 27C. Note that Rickey's management region of "Hood Canal" includes area 25C in addition to these, but according to the rockfish recovery plan 25C is not part of the DPS. 27A appears to mostly be within the Hood Canal DPS, but a small section is outside.
2) U.S. DPS except Hood Canal: Everything else except areas 29 and 23C (these are West Juan de Fuca and outside of the DPS).

\\
We are currently lacking regional resolution for this time period which should hopefully be fixed soon.
#### Yelloweye catch scenarios
Yelloweye rockfish are a reporting category for this time period and as such will only have one catch estimate. 
\\
#### Bocaccio catch scenarios
Bocaccio rockfish are lumped into the "shelf rockfish" category and will have different catch scenarios (these could be amended if any species composition data comes available):
1. High catch: All "shelf rockfish" are bocaccio.
2. Medium catch: 50% of "shelf rockfish" are bocaccio.
3. Low catch: No "shelf rockfish" are bocaccio.

```{r 2004-2020_commercial_data}
PS_CL_1970_2020_path <- here("catch_reconstruction_data", "commercial", "Puget Sound commercial landings_1970-2020.xlsx")
PS_CL_1970_2020 <- read_excel(PS_CL_1970_2020_path, skip = 1, sheet = "By catch area")

# Create new categories and rename
PS_CL_1970_2020 %>% 
  dplyr::rename(catch_lbs = SumOfRoundPoundQuantity, year = Year, species = MarketSpeciesCategoryName) %>% 
  mutate(DPS = ifelse(CatchAreaCode %in% c("27A", "27B", "27C"), "Hood Canal",
                      ifelse(CatchAreaCode %in% c("29", "23C"), "Outside DPS","U.S. DPS except Hood Canal"))) %>% 
  dplyr::select(-c(CatchAreaCode, CatchAreaDescription, MarketSpeciesCategoryCode)) %>% 
  group_by(year, DPS, species) %>% 
  summarise(catch_lbs = sum(catch_lbs)) -> PS_CL_1970_2020


# Yelloweye are a market category; subset yelloweye
PS_CL_1970_2020 %>% 
  # Ungroup to prevent duplicated rows
  ungroup() %>% 
  subset(year >= 2004) %>% 
  subset(., species == "ROCKFISH (YELLOWEYE)") %>% 
  # Add zeros for years where there was no catch using tidyverse::complete
  complete(., DPS = c("U.S. DPS except Hood Canal", "Outside DPS", "Hood Canal"), year = seq(2004, 2020, 1), fill = list(catch_lbs = 0, species = "ROCKFISH (YELLOWEYE)")) %>% 
  subset(., DPS %in% c("U.S. DPS except Hood Canal", "Hood Canal")) %>% 
  # Drop species field
  dplyr::select(-species) -> YE_comm_2004_2020

# Generate three catch scenarios (all the same)
YE_comm_2004_2020 %>% 
  mutate(., high_catch = catch_lbs) %>% 
  mutate(., low_catch = catch_lbs) %>% 
  mutate(., medium_catch = catch_lbs) -> YE_comm_2004_2020 

# Bocaccio are not a market category, but are in the "shelf rockfish" group
PS_CL_1970_2020 %>% 
  # Ungroup to prevent duplicated rows
  ungroup() %>% 
  subset(year >= 2004) %>% 
  subset(., species == "SHELF ROCKFISH") %>% 
  # Add zeros for years where there was no catch using tidyverse::complete
  complete(., DPS = c("U.S. DPS except Hood Canal", "Outside DPS", "Hood Canal"), year = seq(2004, 2020, 1), fill = list(catch_lbs = 0, species = "SHELF ROCKFISH")) %>% 
  # Combine US side of DPS and Hood Canal for Bocaccio
  mutate(DPS = ifelse(DPS %in% c("Hood Canal", "U.S. DPS except Hood Canal"), "U.S. DPS except Hood Canal", DPS)) %>% 
  group_by(year, DPS) %>% 
  summarise(catch_lbs = sum(catch_lbs))  %>% 
  subset(., DPS %in% c("U.S. DPS except Hood Canal", "Hood Canal")) -> shelf_RF_comm_2004_2020

# Generate three catch scenarios
shelf_RF_comm_2004_2020 %>% 
  mutate(., high_catch = catch_lbs) %>% 
  mutate(., low_catch = 0) %>% 
  mutate(., medium_catch = 0.5*catch_lbs) -> shelf_RF_comm_2004_2020

# We don't have any data to assess what proportion of these might be bocaccio
```


## 1970-2003 (HISCOM)

#### Notes:
This data was provided by Wayne Palsson. For the time period 1970-2003, catch has already been prorated to species level based on catch composition data.
\\
#### Yelloweye catch scenarios
Yelloweye rockfish was estimated by prorating total rockfish catch based on reliable catch composition data for this time period. However, region 3 (Strait of Juan de Fuca) is about half in and half out of the DPS, as such, the different catch scenarios concern whether or not this data is included:
1. High catch: All catch from the Strait of Juan de Fuca is included.
2. Medium catch: 50% of the catch from the Strait of Juan de Fuca is included.
3. Low catch: No catch from the Strait of Juan de Fuca is included.
\\
#### Bocaccio catch scenarios
Bocaccio was estimated by prorating total rockfish catch based on reliable catch composition data for this time period and as such will only have one catch estimate. However, region 3 (Strait of Juan de Fuca) is about half in and half out of the DPS, as such, the different catch scenarios concern whether or not this data is included:
1. High catch: All catch from the Strait of Juan de Fuca is included.
2. Medium catch: 50% of the catch from the Strait of Juan de Fuca is included.
3. Low catch: No catch from the Strait of Juan de Fuca is included.

#### Prepare data
Here we load the HISCOM data and make edits to it, converting species, gear, and region codes to what they actually signify.
```{r load_HISCOM_data_and_edit}
HISCOM_path <- here("catch_reconstruction_data", "commercial", "HISCOM.xlsx")

HISCOM <- read_excel(HISCOM_path)

# Change types of certain columns
HISCOM %>% 
  mutate(., YEAR = as.numeric(YEAR)) %>% 
  mutate(., REGION = as.numeric(REGION)) %>% 
  mutate(EFFORT = as.numeric(EFFORT)) %>% 
  mutate(SPECIES = as.numeric(SPECIES)) %>% 
  dplyr::rename(species_code = SPECIES) -> HISCOM

# Change species column to species names rather than codes; use conversion table Wayne provided
recreational_weight_conversion_path <- here("catch_reconstruction_data", "recreational", "Recreationalconversion.xls")
recreational_weight_conversion <- read_excel(recreational_weight_conversion_path, sheet = "Sheet1", skip = 1)
recreational_weight_conversion %>% 
  dplyr::rename(species = "...2") %>% 
  dplyr::rename(species_code = "...1") %>% 
  # Drop weight conversions
  dplyr::select(-c(kg, lbs)) -> species_code_key

# Make some edits to make it consistent with the Rickey doc

# Add the missing codes
missing_codes <- data.frame(species_code = c(35, 36, 37), species = c("MONTHLY or ANNYAL TOTAL CATCH", "Total flatfish (excl. Pacific Halibut)", "Total rockfish"))
species_code_key <- dplyr::bind_rows(species_code_key, missing_codes)

species_code_key <- species_code_key[!is.na(species_code_key$species_code),]

# Merge on species_code; drop species_code
HISCOM %>% 
  dplyr::left_join(., species_code_key, by = "species_code") %>% 
  dplyr::select(-c(species_code)) -> HISCOM

# Change effort to text
effort_codes <- data.frame(EFFORT = c(1,2,3,4,5,6,7,8,9,10,11,12), gear = c("Handline jig", "Bottomfish troll (1980-)", "Other (salmon) troll (1980-)", "Set line", "Set net", "Salmon net", "Drag seine", "Other gear types", "Bottom trawl", "Midwater trawl", "Total commercial effort", "All (combined) troll (1970-1979)"))
# Merge on EFFORT; drop EFFORT
HISCOM %>% 
  dplyr::left_join(., effort_codes, by = "EFFORT") %>% 
  dplyr::select(-c(EFFORT)) -> HISCOM

# Create a region code to region name key (from Rickey)
HISCOM_regions <- data.frame(REGION = c(1,2,3,4,5,6,7,8,9), region = c("Gulf - Bellingham", "San Juan Islands", "Strait of Juan de Fuca", "Hood Canal", "Central Puget Sound", "Southern Puget Sound", "West Juan de Fuca", "PS + West Juan de Fuca", "All PS"))
# Change region numbers to region names
HISCOM %>% 
  left_join(., HISCOM_regions, by = "REGION") %>% 
  dplyr::select(-REGION) -> HISCOM
```

```{r subset_species_HISCOM}
# Subset yelloweye
HISCOM %>% 
  subset(., gear == "Total commercial effort") %>% 
  subset(., species == "Yelloweye rockfish") %>% 
  dplyr::select(c(YEAR, region, gear, TOTAL)) %>% 
  dplyr::rename(year = YEAR) %>% 
  # Add zeros for years where there was no catch using tidyverse::complete
  ungroup() %>% 
  complete(., region = c("Gulf - Bellingham", "San Juan Islands", "Strait of Juan de Fuca", "Hood Canal", "Central Puget Sound", "Southern Puget Sound", "West Juan de Fuca", "PS + West Juan de Fuca", "All PS"), gear = "Total commercial effort", year = seq(1955, 2003, 1), fill = list(TOTAL = 0)) -> YE_HISCOM

# Subset Hood Canal population - only one estimate
YE_HISCOM %>% 
  subset(., region == "Hood Canal") %>% 
  mutate(., DPS = "Hood Canal")  %>% 
  # add columns for joining
  mutate(., high_catch = TOTAL) %>% 
  mutate(., low_catch = TOTAL) %>% 
  mutate(., medium_catch = TOTAL) %>% 
  dplyr::rename(., catch_lbs = TOTAL) %>% 
  dplyr::select(-c(region, gear)) -> YE_HISCOM_hood_canal

# High catch scenario - including all catch from Strait of Juan de Fuca
YE_HISCOM %>% 
  subset(., region == "All PS") %>% 
  mutate(., DPS = "U.S. DPS except Hood Canal") %>% 
  dplyr::rename(high_catch = TOTAL) -> YE_HISCOM_USDPS_high

# Medium catch scenario - including 50% of catch from Strait of Juan de Fuca
YE_HISCOM %>% 
  subset(., region %in% c("All PS", "Strait of Juan de Fuca")) %>% 
  group_by(year) %>% 
  mutate(medium_catch = TOTAL - 0.5*TOTAL[region == "Strait of Juan de Fuca"]) %>% 
  mutate(., DPS = "U.S. DPS except Hood Canal") %>% 
  subset(., region == "All PS") -> YE_HISCOM_USDPS_medium

# Low catch scenario - including no catch from Strait of Juan de Fuca
YE_HISCOM %>% 
  subset(., region %in% c("All PS", "Strait of Juan de Fuca")) %>% 
  group_by(year) %>% 
  mutate(low_catch = TOTAL - TOTAL[region == "Strait of Juan de Fuca"]) %>% 
  mutate(., DPS = "U.S. DPS except Hood Canal") %>% 
  subset(., region == "All PS") -> YE_HISCOM_USDPS_low

# Subset bocaccio
HISCOM %>% 
  subset(., gear == "Total commercial effort") %>% 
  subset(., species == "Bocaccio") %>% 
  dplyr::select(c(YEAR, region, gear, TOTAL)) %>% 
  dplyr::rename(year = YEAR) %>% 
  # Add zeros for years where there was no catch using tidyverse::complete
  ungroup() %>% 
  complete(., region = c("Gulf - Bellingham", "San Juan Islands", "Strait of Juan de Fuca", "Hood Canal", "Central Puget Sound", "Southern Puget Sound", "West Juan de Fuca", "PS + West Juan de Fuca", "All PS"), gear = "Total commercial effort", year = seq(1955, 2003, 1), fill = list(TOTAL = 0)) -> BOC_HISCOM

# Subset Hood Canal population - only one estimate
BOC_HISCOM %>% 
  subset(., region == "Hood Canal") %>% 
  mutate(., DPS = "Hood Canal") %>% 
  # add columns for joining
  mutate(., high_catch = TOTAL) %>% 
  mutate(., low_catch = TOTAL) %>% 
  mutate(., medium_catch = TOTAL) %>% 
  dplyr::rename(., catch_lbs = TOTAL) %>% 
  dplyr::select(-c(region, gear)) -> BOC_HISCOM_hood_canal

# High catch scenario - including all catch from Strait of Juan de Fuca
BOC_HISCOM %>% 
  subset(., region == "All PS") %>% 
  mutate(., DPS = "U.S. DPS except Hood Canal") %>% 
  dplyr::rename(high_catch = TOTAL) -> BOC_HISCOM_USDPS_high

# Medium catch scenario - including 50% of catch from Strait of Juan de Fuca
BOC_HISCOM %>% 
  subset(., region %in% c("All PS", "Strait of Juan de Fuca")) %>% 
  group_by(year) %>% 
  mutate(medium_catch = TOTAL - 0.5*TOTAL[region == "Strait of Juan de Fuca"]) %>% 
  mutate(., DPS = "U.S. DPS except Hood Canal") %>% 
  subset(., region == "All PS") -> BOC_HISCOM_USDPS_medium

# Medium catch scenario - including no catch from Strait of Juan de Fuca
BOC_HISCOM %>% 
  subset(., region %in% c("All PS", "Strait of Juan de Fuca")) %>% 
  group_by(year) %>% 
  mutate(low_catch = TOTAL - TOTAL[region == "Strait of Juan de Fuca"]) %>% 
  mutate(., DPS = "U.S. DPS except Hood Canal") %>% 
  subset(., region == "All PS") -> BOC_HISCOM_USDPS_low
```

```{r make_exploratory_plots}
# Plot catch of yelloweye and bocaccio by region, to get a visual on how sensitive estimates will be to exclusion of Strait of Juan de Fuca data
YE_HISCOM_plot_region <- ggplot(subset(YE_HISCOM, !(region %in% c("All PS", "PS + West Juan de Fuca", "West Juan de Fuca"))), aes(x = year, y = TOTAL, fill = region)) +
  geom_bar(stat = "identity") +
  ggtitle("Yelloweye catch by region, 1955-2003") +
  scale_fill_tableau(palette = "Tableau 10")

ggsave(paste0(fig_dir, "/YE_HISCOM_plot_region.png"), YE_HISCOM_plot_region, height = 8, width = 10)

BOC_HISCOM_plot_region <- ggplot(subset(BOC_HISCOM, !(region %in% c("All PS", "PS + West Juan de Fuca", "West Juan de Fuca"))), aes(x = year, y = TOTAL, fill = region)) +
  geom_bar(stat = "identity") +
  ggtitle("Bocaccio catch by region, 1955-2003") +
  scale_fill_tableau(palette = "Tableau 10")

ggsave(paste0(fig_dir, "/BOC_HISCOM_plot_region.png"), BOC_HISCOM_plot_region, height = 8, width = 10)
```



```{r reformat_data_for_analysis}
YE_HISCOM_USDPS_low %>% 
  left_join(., YE_HISCOM_USDPS_medium, by = c("year", "region", "gear", "TOTAL", "DPS")) %>% 
  left_join(., YE_HISCOM_USDPS_high, by = c("year", "region", "gear", "DPS")) %>% 
  dplyr::rename(catch_lbs = TOTAL) %>% 
  dplyr::select(-c(region, gear)) %>% 
  # Add hood canal data
  bind_rows(., YE_HISCOM_hood_canal) %>% 
  # Subset years
  subset(., year >= 1970) -> YE_comm_1970_2003

BOC_HISCOM_USDPS_low %>% 
  left_join(., BOC_HISCOM_USDPS_medium, by = c("year", "region", "gear", "TOTAL", "DPS")) %>% 
  left_join(., BOC_HISCOM_USDPS_high, by = c("year", "region", "gear", "DPS")) %>% 
  dplyr::rename(catch_lbs = TOTAL) %>% 
  dplyr::select(-c(region, gear)) %>% 
  # Add hood canal data
  bind_rows(., BOC_HISCOM_hood_canal) %>% 
  # Subset years
  subset(., year >= 1970) -> BOC_comm_1970_2003
```

## 1955-1969

#### Notes:
This data was provided by Wayne Palsson. For this time period, we have three categories for rockfish: "general rockfish", "red snapper", and "black rockfish". We do not have any catch composition data for this time period.
\\
There are two main decisions to make regarding this time period:
1) Are yelloweye catches for this time period limited to "red snapper", or is it possible that in addition to "red snapper" there are actually yelloweye in the "general rockfish" category?
2) Should catches from the Strait of Juan de Fuca be included?
\\
For now, we will assume that yelloweye catch is only the "red snapper" catch. Bocaccio catch will be prorated based on the 1970-1987 catch composition data from Schmitt 1991.

#### Yelloweye catch scenarios
Region 3 (Strait of Juan de Fuca) is about half in and half out of the DPS, as such, the different catch scenarios concern whether or not this data is included:
1. High catch: All "red snapper" catch from the Strait of Juan de Fuca is included.
2. Medium catch: 50% of the "red snapper" catch from the Strait of Juan de Fuca is included.
3. Low catch: No "red snapper" catch from the Strait of Juan de Fuca is included.
\\
#### Bocaccio catch scenarios
Region 3 (Strait of Juan de Fuca) is about half in and half out of the DPS, as such, the different catch scenarios concern whether or not this data is included:
1. High catch: All catch from the Strait of Juan de Fuca is included.
2. Medium catch: 50% of the catch from the Strait of Juan de Fuca is included.
3. Low catch: No catch from the Strait of Juan de Fuca is included.
```{r 1955_1969_catch}

```





























## Different catch scenarios for analysis

What are the sources of uncertainty in our analysis?

- What about sources of uncertainty in our parameter estimates? Is there a concern that those in the DPS are different from those on the US coast? Should we use the same parameters as those used in the DFO assessment?

#### Commercial data
1) 2004-2020: None (high confidence)
2) 1970-2003: None (prorated catches have fairly high confidence)
3) 1955-1969
  - The catch composition data - do we apply comps from 1970-1987, or try something else?
  - Red snapper catches vs. prorated rockfish catch
4) 1921-1954
  - Missing data from 1934-1942 - how to estimate? Otherwise catches are treated as zero.
    - Bound Volume data - covers 1935-1941
      - missing 1934 and 1942
        - 1942: Don't have any specific rockfish data; however we are fairly sure that there is a big jump from 1941 (see PDF page 7 of Puget Sound catches; however, this data is likely not restricted to catch from Puget Sound)
        - 1940 and 1941 Puget Sound catch area totals are very similar (just a bit lower) than the total Puget Sound landings listed in this doc
        - Also note that for 1942, it says this: "Rock cod fishing by otter trawls was rigidly curtailed in the Lower Sound Area, Hood Canal, and along the west shore of Camano Island because of evidence of depletion. Less efficient types of gear such as drag seines, hook and lines, and set lines were still permitted, however, since it was believed that the stock could increase under this type of fishing and still be harvested in the minimum quantities necessary to satisfy the local demand for this particular type of rockfish. The less important species occurring offshore have until recently been ignored. This year, however, a remarkable total of 704,000 pounds has been taken and marketed as an aid to the war effort. Special marketing efforts will without a doubt establish a permanent market for these species".
          - So it sounds like they started fishing offshore more? But less otter trawl effort in PS... what does it mean
    
  - Prorating catch compositions:
    - Since we don't have any area information, how do we apply regional differences in catch compositions?
    - Do we apply comps from 1970-1987, or something else?

#### Recreational data
1) 2003-2020: None (catches are so low it shouldn't matter; could possibly look into variance of estimates)
2) 1994-2002: Possible underestimation
  - Bottomfish catch and effort estimates have been severely underestimated from 1994 to 2003 (Palsson et al. 2009)
  - Thus, need to generate a higher catch scenario for this time period (but how?)
3) 1970-2002
  - catch compositions - what proportions do we use to prorate catches?
  - See differences in proportion yelloweye/bocaccio from Palsson's work on recreational catch compositions
4) Pre-1970
  - how to estimate catches at all? We have no real data, but we know that there was some harvest
  - Palsson et al. 2009: “Several recreational fisheries have targeted rockfish or rockfish have been caught incidentally to other sport fishing activities. While recreational fishers have undoubtedly sought and harvested bottomfish prior to 1968 (Buckley 1967, 1968; Buckley and Satterthwaite 1970), statistical surveys were not implemented to estimate total recreational harvests in Puget Sound until 1970, and early estimates indicated that recreational harvests of rockfish were minimal (Palsson 1988)."
  - We have some sporadic documentation of recreational catch from pre-1970: e.g. in WDFW annual bulletins, there are numbers of rock cod caught (1938-1942 at least)
  - 1942 report notes "a considerable drop in the statistical returns from Puget Sound resort owners" - basically, there was no standardized system of recording catches, and therefore estimates are pretty spotty and unreliable. But I guess the estimates could be used as minimum recreational catch? There are even "red snapper" listed among the recreational catches.


### High catch scenario


### Medium catch scenario


### Low catch scenario


# Analysis

### Load libraries, set fig_dir
```{r load_libraries}
library(tidyverse)
library(readxl)
library(here)
library(ggthemes)
library(ggpubr)

fig_dir <- here("figures", "catch_reconstruction")
```

## Commercial Data


### DFO Data
Data is only for yelloweye rockfish (no Bocaccio in Canadian waters)

Load raw and reconstructed DFO data
```{r load_catch_reconstruction_DFO}
DFO_recons_path <- here("catch_reconstruction_data", "canada", "catch-reconstructed.csv")
DFO_recons <- read.csv(DFO_recons_path)

# Create new field to add all catch sources
DFO_recons %>% 
  mutate(total_catch = Rec + FSC + Comm) -> DFO_recons

DFO_raw_path <- here("catch_reconstruction_data", "canada", "catch.csv")
DFO_raw <- read.csv(DFO_raw_path)

# Create new field to add all catch sources
DFO_raw %>% 
  mutate(total_catch = Rec + FSC + Comm) -> DFO_raw
```

#### Plot DFO data
```{r plot_DFO_data}
DFO_recons_plot <- ggplot(DFO_recons, aes(x = Year, y = total_catch)) + 
  geom_line()+
  ggtitle("Inside Yelloweye - Reconstructed")

DFO_recons_plot


DFO_raw_plot <- ggplot(DFO_raw, aes(x = Year, y = total_catch)) + 
  geom_line()+
  ggtitle("Inside Yelloweye - Raw")

DFO_raw_plot

```

### Generate catch compositions from Cyreis Schmitt's work (data in HISCOM)
```{r load_HISCOM_data_for_catch_comps}
HISCOM_path <- here("catch_reconstruction_data", "commercial", "HISCOM.xlsx")

HISCOM <- read_excel(HISCOM_path)

# Change types of certain columns
HISCOM %>% 
  mutate(., YEAR = as.numeric(YEAR)) %>% 
  mutate(., REGION = as.numeric(REGION)) %>% 
  mutate(EFFORT = as.numeric(EFFORT)) %>% 
  mutate(SPECIES = as.numeric(SPECIES)) %>% 
  dplyr::rename(species_code = SPECIES) -> HISCOM

# Change species column to species names rather than codes; use conversion table Wayne provided
recreational_weight_conversion_path <- here("catch_reconstruction_data", "recreational", "Recreationalconversion.xls")
recreational_weight_conversion <- read_excel(recreational_weight_conversion_path, sheet = "Sheet1", skip = 1)
recreational_weight_conversion %>% 
  dplyr::rename(species = "...2") %>% 
  dplyr::rename(species_code = "...1") %>% 
  # Drop weight conversions
  dplyr::select(-c(kg, lbs)) -> species_code_key


# Make some edits to make it consistent with the Rickey doc

# Add the missing codes
missing_codes <- data.frame(species_code = c(35, 36, 37), species = c("MONTHLY or ANNYAL TOTAL CATCH", "Total flatfish (excl. Pacific Halibut)", "Total rockfish"))
species_code_key <- dplyr::bind_rows(species_code_key, missing_codes)

species_code_key <- species_code_key[!is.na(species_code_key$species_code),]



# Merge on species_code; drop species_code
HISCOM %>% 
  dplyr::left_join(., species_code_key, by = "species_code") %>% 
  dplyr::select(-c(species_code)) -> HISCOM

sort(unique(HISCOM$EFFORT))

# Change effort to text
effort_codes <- data.frame(EFFORT = c(1,2,3,4,5,6,7,8,9,10,11,12), gear = c("Handline jig", "Bottomfish troll (1980-)", "Other (salmon) troll (1980-)", "Set line", "Set net", "Salmon net", "Drag seine", "Other gear types", "Bottom trawl", "Midwater trawl", "Total commercial effort", "All (combined) troll (1970-1979)"))
# Merge on EFFORT; drop EFFORT
HISCOM %>% 
  dplyr::left_join(., effort_codes, by = "EFFORT") %>% 
  dplyr::select(-c(EFFORT)) -> HISCOM
```

Use years 1970-1987 to look at species compositions; this data is the result of Cyreis Schmitt's work
```{r}
HISCOM_70_87 <- subset(HISCOM, YEAR <= 1987 & YEAR >= 1970)

# Look at catch comps across all PS; subset REGION 9
HISCOM_70_87_reg9 <- subset(HISCOM_70_87, REGION == 9)

# Subset rockfishes
unique(HISCOM_70_87_reg9$species)
HISCOM_70_87_reg9_RF <- subset(HISCOM_70_87_reg9, species %in% c("Black rockfish", "Bocaccio",  "Brown rockfish", "Canary rockfish",  "Copper rockfish", "Quillback rockfish", "Yelloweye rockfish", "Yellowtail rockfish", "Misc. rockfish"))
# Here we aren't including "total rockfish" because it is the sum of all above rockfish

# Drop months
HISCOM_70_87_reg9_RF %>% 
  dplyr::select(YEAR, TOTAL, species, gear) -> HISCOM_70_87_reg9_RF

# Generate ratios for each year by gear
HISCOM_70_87_reg9_RF %>% 
  group_by(YEAR, gear) %>% 
  mutate(prop = TOTAL/sum(TOTAL)) %>% 
  # Change NAs to zeros; the reason we are getting NAs is because if the TOTAL is zero, then it's zero/zero which is NA
  mutate(prop = ifelse(is.na(prop), 0, prop)) -> RF_ratios_70_87
```
#### Plot proportions by gear type
```{r}
gear_types <- sort(unique(RF_ratios_70_87$gear))

spp_comp_plot_list <- list()

for (i in 1:length(gear_types)){
plot <- ggplot(data = subset(RF_ratios_70_87, gear == gear_types[i]), aes(x = YEAR, y = prop, fill = species))+
           geom_bar(stat = "identity")+
    scale_fill_tableau(palette = "Tableau 10")+
  ggtitle(paste0(gear_types[i]))+
    ylab("Proportion of catch") + 
    xlab("Year")

spp_comp_plot_list[[i]] <- plot
}

spp_comp_plot_list
```

#### Plot all catch with gear type as fill
```{r plot_catch_by_gear_1970_1987}
catch_by_gear_1970_1987 <- ggplot(subset(RF_ratios_70_87, gear != "Total commercial effort"), aes(x = YEAR, y = TOTAL, fill = gear)) +
    geom_bar(stat = "identity")+
    scale_fill_tableau(palette = "Tableau 20")+
    ggtitle("Total rockfish catch by gear type")+
    ylab("Catch (pounds)") + 
    xlab("Year")

catch_by_gear_1970_1987
```

#### Calculate ratios for each gear type, all years
```{r spp_comps_by_gear_type}
# Create RF_ratios_70_87_comb, which has proportion of each species in each gear type across all years
HISCOM_70_87_reg9_RF %>% 
  # Combine the three troll types ("All (combined) troll (1970-1979)", "Bottomfish troll (1980-)", and "Other (salmon) troll (1980-)") into one
  mutate(gear = ifelse(gear %in% c("All (combined) troll (1970-1979)", "Bottomfish troll (1980-)", "Other (salmon) troll (1980-)"), "All troll", gear)) %>% 
  group_by(gear, species) %>% 
  summarise(total_catch = sum(TOTAL))  %>%
  mutate(prop = total_catch/sum(total_catch)) -> RF_ratios_70_87_comb

# Take minimum and maximum proportions per year as well
RF_ratios_70_87 %>% 
  mutate(gear = ifelse(gear %in% c("All (combined) troll (1970-1979)", "Bottomfish troll (1980-)", "Other (salmon) troll (1980-)"), "All troll", gear)) %>% 
  group_by(species, gear) %>% 
  summarise(max_prop = max(prop), min_prop = min(prop)) -> RF_ratios_70_87_range

# Add the ranges to the mean proportions by gear type
RF_ratios_70_87_comb <- left_join(RF_ratios_70_87_comb, RF_ratios_70_87_range, by = c("species", "gear"))

# Mutate to add column for total catch by gear type
RF_ratios_70_87_comb %>% 
  group_by(gear) %>% 
  mutate(total_catch_by_gear = sum(total_catch)) -> RF_ratios_70_87_comb
  
# Sanity check that total catch hasn't changed
sum(HISCOM_70_87_reg9_RF$TOTAL)
sum(RF_ratios_70_87_comb$total_catch)

# Create a data frame that has the yelloweye and bocaccio proportions for each gear type
RF_ratios_70_87_comb %>% 
  subset(., species %in% c("Yelloweye rockfish", "Bocaccio")) %>% 
  dplyr::select(-c(total_catch, total_catch_by_gear)) %>% 
  mutate(., bocaccio_mean_prop = ifelse(species == "Bocaccio", prop, NA)) %>% 
  mutate(., bocaccio_min_prop = ifelse(species == "Bocaccio", min_prop, NA)) %>% 
  mutate(., bocaccio_max_prop = ifelse(species == "Bocaccio", max_prop, NA)) %>% 
  mutate(., yelloweye_mean_prop = ifelse(species == "Yelloweye rockfish", prop, NA)) %>% 
  mutate(., yelloweye_min_prop = ifelse(species == "Yelloweye rockfish", min_prop, NA)) %>% 
  mutate(., yelloweye_max_prop = ifelse(species == "Yelloweye rockfish", max_prop, NA)) %>% 
  # Drop species column (since this is in column header already), as well as prop, max_prop, and min_prop
  dplyr::select(-c(species, prop, max_prop, min_prop)) %>% 
  # Merge rows together, replacing NAs
  group_by(gear) %>% 
  summarise_each(funs(sum(., na.rm = TRUE))) -> YE_BOC_comps


# Add a column for yellowbook gear
YE_BOC_comps$yb_gear <- c("handline_troll", "otter_trawl", "drag_seine", NA, NA, "other_gear", NA, "set_line", "set_net", NA)
# YE_BOC_comps$yb_gear
# yellowbook_gears 

# Add a row with zeros for pound net and "unknown", duplicate bottom trawl for beam trawl
pound_net_unknown <- data.frame(gear = c(NA, NA), bocaccio_mean_prop = c(0,0), bocaccio_max_prop = c(0,0), bocaccio_min_prop = c(0,0), yelloweye_mean_prop = c(0,0), yelloweye_max_prop = c(0,0), yelloweye_min_prop = c(0,0), yb_gear = c("pound_net", "unknown"))

subset(YE_BOC_comps, gear == "Bottom trawl") %>% 
  mutate(yb_gear = "beam_trawl") -> beam_trawl

YE_BOC_comps <- bind_rows(bind_rows(YE_BOC_comps, pound_net_unknown), beam_trawl)

# Rename gears to make it match with yellow book
YE_BOC_comps %>% 
  dplyr::rename(schmitt_gear = gear, gear = yb_gear) -> YE_BOC_comps
```

From 1970-1987, yelloweye rockfish composed ~5% of total commercial catch, while Bocaccio composed ~2% of total commercial catch.

``` {r plot_comps_by_Gear_type}
# Plot compositions by each gear type
RF_ratios_70_87_comb_plot <- ggplot(RF_ratios_70_87_comb, aes(x = gear, y = prop, fill = species))+
    geom_bar(stat = "identity")+
    scale_fill_tableau(palette = "Tableau 10")+
    ggtitle("Catch compositions by gear type: 1970-1987")+
    ylab("Proportion of catch") + 
    xlab("Gear Type")+
    coord_flip()+
  scale_y_continuous(breaks = c(0, 0.25, 0.5, 0.75, 1), limits = c(0, 1.25)) +
  # Add total catch in pounds to plot
  geom_text(data = RF_ratios_70_87_comb[!duplicated(RF_ratios_70_87_comb[,c("gear")]),], aes(x = gear, y = 1.03, label = total_catch_by_gear), hjust = 0, size = 6)+
  theme(panel.background = element_rect(fill = "white", color = "black"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(size = 14),
        axis.text.y = element_text(size = 18),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 16),
        plot.title = element_text(size = 20),
        axis.title.x = element_text(size = 16),
        axis.title.y = element_text(size = 20))

RF_ratios_70_87_comb_plot

ggsave(paste0(fig_dir, "/RF_catch_comps_gear_70_87.png"), RF_ratios_70_87_comb_plot, height = 8, width = 10)
```

### 1921-1954 (minus 1934-1942)

We will have to apply some species composition ratios to the rockfish landings, ideally by gear type (and maybe area? but I don't think the data has the resolution for this)
\
For this time period we will use the yellow book data (same as what's in ROCKHIS.xlsx, which Wayne Palsson used for his analysis), but is broken down by gear type so we can apply species composition data.

```{r load_yellowbook_data}
yellowbook_path <- here("catch_reconstruction_data", "commercial", "yellowbook_1921_1954.csv")

yellowbook <- read.csv(yellowbook_path)

# convert to long format; drop non-gear type names
yellowbook %>% 
  dplyr::select(-c(total, species)) %>% 
  pivot_longer(., cols = colnames(yellowbook)[!colnames(yellowbook) %in% c("year", "species", "total")], names_to = "gear") -> yb_long

```

#### Plot catch by gear type
```{r}
gear_catch_21_54 <- ggplot(data = yb_long, aes(x = year, y = value, fill = gear))+
           geom_bar(stat = "identity")+
    scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Total catch by gear type (Yellow Book Data)")+
    ylab("Catch (pounds)") + 
    xlab("Year")

gear_catch_21_54
```

#### Match gear types from Cyreis Schmitt to those from Yellow Book
```{r match_gears_for_catch_comps}
yellowbook_gears <- colnames(yellowbook)[!colnames(yellowbook) %in% c("year", "species", "total")]

cyreis_schmitt_gears <- sort(unique(RF_ratios_70_87$gear))

yellowbook_gears
cyreis_schmitt_gears

# Add the matching yellowbook gear

RF_ratios_70_87_comb
```
| Yellow Book Gear | Schmitt Gear | Notes |
|-|-|-|
| pound_net | no analogue | Most common gear type in late 20s, but no longer used in 70s; however, these would have caught very shallow species (unlikely yelloweye or bocaccio) |
| drag_seine | Drag seine | identical |
| set_net | Set net | identical |
| otter_trawl | Bottom trawl |
| handline_troll | All (combined) troll (1970-1979), Bottomfish troll (1980-), and Other (salmon) troll (1980-) | Gear categories change, but can combine to stay consistent |
| Set line | Set line |
| Beam trawl | Bottom trawl |
| other_gear/unknown | Other gear types | not useful for catch comps |


#### Prorate catch for 1921-1954 based on catch compositions from 1970-1987
```{r prorate_1921_1954_catch}
yb_long %>% 
  left_join(., YE_BOC_comps, by = "gear") %>% 
  # Multiply by ratios (mean, max, and min)
  mutate(bocaccio_mean_catch = value * bocaccio_mean_prop) %>% 
  mutate(bocaccio_max_catch = value * bocaccio_max_prop) %>% 
  mutate(bocaccio_min_catch = value * bocaccio_min_prop) %>% 
  mutate(yelloweye_mean_catch = value * yelloweye_mean_prop) %>% 
  mutate(yelloweye_max_catch = value * yelloweye_max_prop) %>% 
  mutate(yelloweye_min_catch = value * yelloweye_min_prop) %>% 
  # Drop the ratios, schmitt_gear
  dplyr::select(-c(schmitt_gear, bocaccio_mean_prop, bocaccio_max_prop, bocaccio_min_prop, yelloweye_mean_prop, yelloweye_max_prop, yelloweye_min_prop)) -> yb_catch_estimates

# Sum across all gear types for each year
yb_catch_estimates %>% 
  # Drop the gear type
  dplyr::select(-c(gear)) %>% 
  # Group by year and sum across gear types
  group_by(year) %>% 
  # Note: reason that there are some NAs is because how gears were reported changed over time (see jump between 1933 and 1943)
  summarise_all(sum, na.rm = TRUE) -> yb_catch_estimate_sums
```


### 1935-1940 (Bound Volumes)
```{r load_BV_data}
BV_path <- here("catch_reconstruction_data", "commercial", "boundvolumes_OLDMFLnData36_60_ROCKFISH.xlsx")

BV_1936_60 <- read_excel(BV_path)

BV_35_42_path <- here("catch_reconstruction_data", "commercial", "boundvolumes_OLDMFLnData35_42_12570_Inc_wEdits.xlsx")

BV_1935_42 <- read_excel(BV_35_42_path)
# Subset rockfish
BV_1935_42 %>% 
  subset(., Species_Orig == "ROCK COD")  -> BV_1935_42

# Combine two dfs
setdiff(colnames(BV_1935_42), colnames(BV_1936_60))
setdiff(colnames(BV_1936_60), colnames(BV_1935_42))

# Drop the columns that aren't in both (these aren't informative)
# Rename certain columns

BV_1935_42 %>% 
  dplyr::select(-c("XRefSpeciesID_Fkey", "Utilization",  "XRef_GearCodeID _Fkey", "XRefAreaID_Fkey")) %>% 
  dplyr::rename(Norm_AmtLanded = Amount_Landed_Normalized) -> BV_1935_42

BV_1936_60 %>% 
  dplyr::select(-c(Select4Edit)) -> BV_1936_60

BV_1935_42 %>% 
  bind_rows(., BV_1936_60) -> BV_1935_60

# Load the catch area to region key
BC_catcharea_key_path <- here("catch_reconstruction_data", "commercial", "boundvolume_catcharea_key.xlsx")
BC_catcharea_key <- read_excel(BC_catcharea_key_path)

# Combine the two catch area columns, join with key
BV_1935_60 %>% 
  mutate(., catch_area = ifelse(is.na(Norm_CatchArea), CatchArea_Orig, Norm_CatchArea)) %>% 
  left_join(., BC_catcharea_key, by = "catch_area") -> BV_1935_60

# Drop the data from outside PS
BV_1935_60 %>% 
  subset(., !(region %in% c("OUTSIDE", "COAST", "COLUMBIA RIVER", "UNKNOWN"))) -> BV_PS

# Edit gears
BV_PS %>% 
  mutate(., gear = ifelse(is.na(Norm_Gear), Gear_Orig, Norm_Gear)) %>% 
  mutate(gear = ifelse(gear %in% c("BT", "Trawl - Otter", "Trawl - Beam"), "Trawl", gear)) %>% 
  mutate(gear = ifelse(gear %in% c("DS", "Drag Seine"), "Drag Seine", gear)) %>%          
  mutate(gear = ifelse(gear %in% c("H&L", "HL", "Hook and Line"), "Hook and Line", gear)) %>%   
  mutate(gear = ifelse(gear %in% c("SL", "Longline/Set Line"), "Set line", gear)) %>%     
  mutate(gear = ifelse(gear %in% c("PS", "Purse Seine", "Purse Seine  - (salmon)"), "Purse seine", gear)) %>%   
  mutate(gear = ifelse(gear %in% c("Troll - Unknown", "Troll - (salmon)", "Troll - Bottomfish"), "Troll", gear)) %>%    
  mutate(gear = ifelse(gear %in% c("Handline/Jigger"), "Handline jig", gear)) %>%    
  mutate(gear = ifelse(gear %in% c("Set Net/Gillnet - Tribal", "Drag Seine - Tribal"), "Tribal Fisheries", gear)) %>%    
  mutate(gear = ifelse(gear %in% c("Not reported", "Trap - Shellfish Pot (Dungeness)", "Beach Seine", "Gillnet - Drift (Salmon)"), "Other", gear)) -> BV_PS
           
unique(BV_PS$gear)

subset(BV_PS, YearLanded_Orig == 1941)

# Summarize by year to compare with yellow book data
BV_PS %>% 
  dplyr::select(YearLanded_Orig, Norm_AmtLanded) %>% 
  group_by(YearLanded_Orig) %>% 
  summarise(annual_catch = sum(Norm_AmtLanded, na.rm = TRUE)) %>% 
  mutate(data_source = "Bound Volumes")-> BV_PS_annual_sums
```


#### Plot BV Data

##### By species category
```{r BV_species_plot}
BV_species_catch_plot <- ggplot(BV_PS, aes(x = YearLanded_Orig, y = Norm_AmtLanded, fill = Species_Orig))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 20")+
  ggtitle("Bound Volume Rockfish Catch by Species")+
  ylab("Catch (pounds)") + 
  xlab("Year")

BV_species_catch_plot
```

##### By region
```{r BV_region_plot}
BV_region_catch_plot <- ggplot(BV_PS, aes(x = YearLanded_Orig, y = Norm_AmtLanded, fill = region))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 20")+
  ggtitle("Bound Volume Rockfish by Catch Region")+
  ylab("Catch (pounds)") + 
  xlab("Year")

BV_region_catch_plot
```

##### By gear type
```{r BV_gear_type_plot}
BV_gear_catch_plot <- ggplot(BV_PS, aes(x = YearLanded_Orig, y = Norm_AmtLanded, fill = gear))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 20")+
  ggtitle("Bound Volume Rockfish by Gear Type")+
  ylab("Catch (pounds)") + 
  xlab("Year")

BV_gear_catch_plot
```

### 1955-2003 (HISCOM)

Note: For the time period 1955-1969, the "yelloweye" data is equivalent to the "red snapper" data from the yellow book. Question - is it possible that there is yelloweye in the total rockfish landings from this same time period?

Note: HISCOM and COMBCATCH_2011 contain identical data. I checked this with some plots

For effort: code 11 is total commercial effort
For region: 9 is PSP (excludes West Juan de Fuca)
For species: Yelloweye is  code 20, Bocaccio is code 15, total RF is 37

#### Prepare data
HISCOM data was already loaded previously for catch comps
```{r load_1955-2003_HISCOM}
# Subset yelloweye
HISCOM %>% 
  subset(., REGION == 9) %>% 
  subset(., gear == "Total commercial effort") %>% 
  subset(., species == "Yelloweye rockfish") %>% 
  dplyr::select(c(YEAR, REGION, gear, TOTAL))  -> YE_HISCOM

# Subset bocaccio
HISCOM %>% 
  subset(., REGION == 9) %>% 
  subset(., gear == "Total commercial effort") %>% 
  subset(., species == "Bocaccio") %>% 
  dplyr::select(c(YEAR, REGION, gear, TOTAL))  -> BOC_HISCOM

# Subset total rockfish
HISCOM %>% 
  subset(., REGION == 9) %>% 
  subset(., gear == "Total commercial effort") %>% 
  subset(., species == "Total rockfish") %>% 
  dplyr::select(c(YEAR, REGION, gear, TOTAL))  -> TOTAL_RF_HISCOM

# Create a region code to region name key (from Rickey)
HISCOM_regions <- data.frame(REGION = c(1,2,3,4,5,6,7,8,9), region = c("Gulf - Bellingham", "San Juan Islands", "Strait of Juan de Fuca", "Hood Canal", "Central Puget Sound", "Southern Puget Sound", "West Juan de Fuca", "PS + West Juan de Fuca", "All PS"))
```

#### Plot catch by gear type
```{r plot_1955_2003_catch_by_gear}
# Reformat data for all rockfishes
HISCOM %>% 
  # subset(., species %in% c("Black rockfish", "Bocaccio",  "Brown rockfish", "Canary rockfish",  "Copper rockfish", "Quillback rockfish", "Yelloweye rockfish", "Yellowtail rockfish", "Misc. rockfish")) %>% 
  # Select the total rockfish category and the yelloweye category
  subset(., species %in% c("Total rockfish")) %>% 
  # Subtract yelloweye from total rockfish
  dplyr::select(c(YEAR, REGION, gear, TOTAL, species)) %>% 
  # Drop the total commercial effort category
  subset(., gear != "Total commercial effort") %>% 
  # combine the troll categories
    mutate(gear = ifelse(gear %in% c("All (combined) troll (1970-1979)", "Bottomfish troll (1980-)", "Other (salmon) troll (1980-)"), "All troll", gear)) %>% 
  # Look at all PS
  subset(., REGION == 9) -> HISCOM_totalRF_55_03

RF_gear_catch_55_03 <- ggplot(data = HISCOM_totalRF_55_03, aes(x = YEAR, y = TOTAL, fill = gear))+
           geom_bar(stat = "identity")+
    scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Total catch by gear type (Yellow Book Data)")+
    ylab("Catch (pounds)") + 
    xlab("Year")

RF_gear_catch_55_03
```



### Plot
```{r}
YE_HISCOM_plot <- ggplot(YE_HISCOM, aes(x = YEAR, y = TOTAL)) +
  geom_line()+
  xlim(1954,2004)+
  geom_vline(xintercept = 1969.5, lty = 2, color = "red") +
  annotate(geom = "text", label = "Change in reporting", angle = 90, x = 1968.5, y = 10000,color = "red") +
  ggtitle("Yelloweye Rockfish")

BOC_HISCOM_plot <- ggplot(BOC_HISCOM, aes(x = YEAR, y = TOTAL)) +
  geom_line()+
  xlim(1969,2004)+
  ggtitle("Bocaccio")

TOTAL_RF_HISCOM_plot <- ggplot(TOTAL_RF_HISCOM, aes(x = YEAR, y = TOTAL)) +
  geom_line()+
  xlim(1954,2004)+
  ggtitle("Total Rockfish")


YE_HISCOM_plot
BOC_HISCOM_plot
TOTAL_RF_HISCOM_plot
```
#### Pro-rate bocaccio and yelloweye catch through 1955-1969


##### First method: use the proportions of catches directly from Cyreis's statistics (these were generated by applying a table of species compositions)
For 1955-1969, the rockfish reporting categories were "red snapper" (yelloweye), "black rockfish", and "Miscellaneous and unidentified rockfish". These are summed up in "total rockfish".

In the yellow book PDFs though there is no "black rockfish" category, so I'm not sure where these values are coming from.

```{r}
# Change gear name column to match
YE_BOC_comps %>% 
  dplyr::select(-c("gear")) %>% 
  dplyr::rename(gear = schmitt_gear) -> YE_BOC_comps_schmitt

# Add species composition data; multiply against unidentified rockfishes
HISCOM %>% 
  # Subset years for which we need to prorate catch
  subset(., YEAR >= 1955 & YEAR <= 1969) %>% 
  # Subset only unidentified rockfishes
  subset(., species %in% c("Misc. rockfish")) %>% 
  dplyr::select(c(YEAR, REGION, gear, TOTAL, species)) %>% 
  # Drop the total commercial effort category
  subset(., gear != "Total commercial effort") %>% 
  # combine the troll categories
    mutate(gear = ifelse(gear %in% c("All (combined) troll (1970-1979)", "Bottomfish troll (1980-)", "Other (salmon) troll (1980-)"), "All troll", gear)) %>% 
  # Look at all PS
  subset(., REGION == 9) %>% 
    left_join(., YE_BOC_comps_schmitt, by = "gear") %>% 
  # Multiply by ratios (mean, max, and min)
  mutate(bocaccio_mean_catch = TOTAL * bocaccio_mean_prop) %>% 
  mutate(bocaccio_max_catch = TOTAL * bocaccio_max_prop) %>% 
  mutate(bocaccio_min_catch = TOTAL * bocaccio_min_prop) %>% 
  mutate(yelloweye_mean_catch = TOTAL * yelloweye_mean_prop) %>% 
  mutate(yelloweye_max_catch = TOTAL * yelloweye_max_prop) %>% 
  mutate(yelloweye_min_catch = TOTAL * yelloweye_min_prop) %>% 
  # Drop the ratios
  dplyr::select(-c(bocaccio_mean_prop, bocaccio_max_prop, bocaccio_min_prop, yelloweye_mean_prop, yelloweye_max_prop, yelloweye_min_prop)) -> HISCOM_RF_55_69_prorated
```

##### Second method: Use the same table that Cyreis did, which has compositions by gear type and area
Issue: Some reporting categories are not used in table 2 from Schmitt 1991:
- Salmon net (not a big deal, < 500 lb catch total)
- Drag seine (big deal ~20,000 lb catch total)
  - HOWEVER: In Cyreis Schmitt's work, everytime there is rockfish caught via drag seine OR salmon net, it's all misc./unidentified rockfishes. Probably because there was no available data on comps for drag seine or salmon net. So using this method isn't any worse than using the comps from her data directly. But it isn't good without knowing more about these methods (i.e. depths or bottom type targeted).
  
- Midwater trawl: this is not an issue because it wasn't used as a category before 1970.

```{r prorate_table2}
## Load species composition tables
comp_table_path <- here("catch_reconstruction_data", "commercial", "schmitt_1991_table2_spp_comp_region_gear.xlsx")
trawl_comps <- read_excel(comp_table_path, sheet = "trawl")
set_net_comps <- read_excel(comp_table_path, sheet = "set_net")
set_line_comps <- read_excel(comp_table_path, sheet = "set_line")
troll_comps <- read_excel(comp_table_path, sheet = "troll")
jig_comps <- read_excel(comp_table_path, sheet = "jig")

# Convert all to long format, and format for joining

# trawl_comps
trawl_comps %>% 
  pivot_longer(cols = colnames(trawl_comps)[c(2:length(colnames(trawl_comps)))], names_to = "region") %>% 
  # Change percentages to proportions
  mutate(., value = value/100) %>% 
  # Keep only yelloweye and bocaccio
  subset(., species %in% c("Yelloweye", "Bocaccio")) %>% 
  mutate(., bocaccio_prop = ifelse(species == "Bocaccio", value, NA)) %>% 
  mutate(., yelloweye_prop = ifelse(species == "Yelloweye", value, NA)) %>% 
  # Drop species column now that it's in column name; also drop "value" (since these are now separated into boc and ye props)
  dplyr::select(-c(species, value)) %>% 
  # Merge rows together, replacing NAs
  group_by(region) %>% 
  summarise_each(funs(sum(., na.rm = TRUE))) -> trawl_comps_YE_boc
  # Add region numbers
  trawl_comps_YE_boc$REGION = c(5,1,4,3,2,6,7)
  # Add gear type column
  trawl_comps_YE_boc$gear <- "Bottom trawl"
  
# set_net_comps
set_net_comps %>% 
  pivot_longer(cols = colnames(set_net_comps)[c(2:length(colnames(set_net_comps)))], names_to = "region") %>% 
  # Change percentages to proportions
  mutate(., value = value/100) %>% 
  # Keep only yelloweye and bocaccio
  subset(., species %in% c("Yelloweye", "Bocaccio")) %>% 
  mutate(., bocaccio_prop = ifelse(species == "Bocaccio", value, NA)) %>% 
  mutate(., yelloweye_prop = ifelse(species == "Yelloweye", value, NA)) %>% 
  # Drop species column now that it's in column name; also drop "value" (since these are now separated into boc and ye props)
  dplyr::select(-c(species, value)) %>% 
  # Merge rows together, replacing NAs
  group_by(region) %>% 
  summarise_each(funs(sum(., na.rm = TRUE))) -> set_net_comps_YE_boc
  # Add region numbers
  set_net_comps_YE_boc$REGION = c(5,1,4,3,2,6,7)
  # Add gear type column
  set_net_comps_YE_boc$gear <- "Set net"
  
# set_line_comps
set_line_comps %>% 
  pivot_longer(cols = colnames(set_line_comps)[c(2:length(colnames(set_line_comps)))], names_to = "region") %>% 
  # Change percentages to proportions
  mutate(., value = value/100) %>% 
  # Keep only yelloweye and bocaccio
  subset(., species %in% c("Yelloweye", "Bocaccio")) %>% 
  mutate(., bocaccio_prop = ifelse(species == "Bocaccio", value, NA)) %>% 
  mutate(., yelloweye_prop = ifelse(species == "Yelloweye", value, NA)) %>% 
  # Drop species column now that it's in column name; also drop "value" (since these are now separated into boc and ye props)
  dplyr::select(-c(species, value)) %>% 
  # Merge rows together, replacing NAs
  group_by(region) %>% 
  summarise_each(funs(sum(., na.rm = TRUE))) -> set_line_comps_YE_boc
  # Add region numbers
  set_line_comps_YE_boc$REGION = c(5,1,4,3,2,6,7)
  # Add gear type column
  set_line_comps_YE_boc$gear <- "Set line"
  
# troll_comps
troll_comps %>% 
  pivot_longer(cols = colnames(troll_comps)[c(2:length(colnames(troll_comps)))], names_to = "region") %>% 
  # Change percentages to proportions
  mutate(., value = value/100) %>% 
  # Keep only yelloweye and bocaccio
  subset(., species %in% c("Yelloweye", "Bocaccio")) %>% 
  mutate(., bocaccio_prop = ifelse(species == "Bocaccio", value, NA)) %>% 
  mutate(., yelloweye_prop = ifelse(species == "Yelloweye", value, NA)) %>% 
  # Drop species column now that it's in column name; also drop "value" (since these are now separated into boc and ye props)
  dplyr::select(-c(species, value)) %>% 
  # Merge rows together, replacing NAs
  group_by(region) %>% 
  summarise_each(funs(sum(., na.rm = TRUE))) -> troll_comps_YE_boc
  # Add region numbers
  troll_comps_YE_boc$REGION = c(5,1,4,3,2,6,7)
  # Add gear type column
  troll_comps_YE_boc$gear <- "All troll"

# jig_comps
jig_comps %>% 
  pivot_longer(cols = colnames(jig_comps)[c(2:length(colnames(jig_comps)))], names_to = "region") %>% 
  # Change percentages to proportions
  mutate(., value = value/100) %>% 
  # Keep only yelloweye and bocaccio
  subset(., species %in% c("Yelloweye", "Bocaccio")) %>% 
  mutate(., bocaccio_prop = ifelse(species == "Bocaccio", value, NA)) %>% 
  mutate(., yelloweye_prop = ifelse(species == "Yelloweye", value, NA)) %>% 
  # Drop species column now that it's in column name; also drop "value" (since these are now separated into boc and ye props)
  dplyr::select(-c(species, value)) %>% 
  # Merge rows together, replacing NAs
  group_by(region) %>% 
  summarise_each(funs(sum(., na.rm = TRUE))) -> jig_comps_YE_boc
  # Add region numbers
  jig_comps_YE_boc$REGION = c(5,1,4,3,2,6,7)
  # Add gear type column
  jig_comps_YE_boc$gear <- NA
  
# Join all comp data together
trawl_comps_YE_boc %>% 
  bind_rows(., set_net_comps_YE_boc) %>% 
  bind_rows(., set_line_comps_YE_boc) %>% 
  bind_rows(., troll_comps_YE_boc) %>% 
  bind_rows(., jig_comps_YE_boc) -> comp_tables

# Prep RF data
HISCOM %>% 
  # Subset years for which we need to prorate catch
  subset(., YEAR >= 1955 & YEAR <= 1969) %>% 
  # Subset only unidentified rockfishes
  subset(., species %in% c("Misc. rockfish")) %>% 
  dplyr::select(c(YEAR, REGION, gear, TOTAL, species)) %>% 
  # Drop the total commercial effort category
  subset(., gear != "Total commercial effort") %>% 
  # combine the troll categories
    mutate(gear = ifelse(gear %in% c("All (combined) troll (1970-1979)", "Bottomfish troll (1980-)", "Other (salmon) troll (1980-)"), "All troll", gear)) %>% 
  # Remove the summary regions
  subset(., !(REGION == 9 | REGION == 8)) %>% 
  # Add the comp table data
  left_join(., comp_tables, by = c("REGION", "gear")) %>% 
  # Multiple TOTAL by prop to get catch
  mutate(., yelloweye_catch_estimate = yelloweye_prop*TOTAL) %>% 
  mutate(., bocaccio_catch_estimate = bocaccio_prop*TOTAL) -> HISCOM_RF_55_69_prorated_2

```


### 2004-2020

```{r 2004-2020_commercial_data}
PS_CL_1970_2020_path <- here("catch_reconstruction_data", "commercial", "Puget Sound commercial landings_1970-2020.xlsx")
PS_CL_1970_2020 <- read_excel(PS_CL_1970_2020_path, skip = 1)

# Yelloweye are a market category; subset yelloweye
PS_CL_1970_2020 %>% 
  subset(Year >= 2004) %>% 
  dplyr::select(c(Year, "ROCKFISH (YELLOWEYE)")) %>% 
  dplyr::rename(YE_catch_lbs = "ROCKFISH (YELLOWEYE)") -> YE_comm_2004_2020

# Bocaccio are not a market category, but are in the "shelf rockfish" group
PS_CL_1970_2020 %>% 
  subset(Year >= 2004) %>% 
  dplyr::select(c(Year, "SHELF ROCKFISH")) %>% 
  dplyr::rename(SHELF_RF_catch_lbs = "SHELF ROCKFISH") -> shelf_RF_comm_2004_2020

# We don't have any data to assess what proportion of these might be bocaccio
```


### Combine all commercial data

Columns we need:
1) Year
2) Catch ("yelloweye_catch_estimate" or "bocaccio_catch_estimate")
  - If 1970 onwards, from Cyreis Schmitt/subsequent work pro-rating catch or direct estimates (2004-2020)
  - If pre-1970, we need min, max, and mean - less confidence
3) Source

#### Total rockfish
```{r}

# 1921-1954: YB (yes gear, no region)
yb_long %>% 
  mutate(region = "All PS") %>% 
  dplyr::rename(total_RF_lbs = value) -> total_RF_21_54

# 1955-2003: HISCOM (yes gear, yes region)
HISCOM %>% 
  subset(species == "Total rockfish") %>% 
  dplyr::select(YEAR, REGION, TOTAL, gear) %>% 
  # Drop the summary regions
  subset(., !(REGION %in% c(8,9))) %>% 
  # Drop West Juan de Fuca
  subset(., REGION != 7) %>% 
  # Change region codes to region names
  left_join(., HISCOM_regions, by = "REGION") %>% 
  dplyr::select(-REGION) %>% 
  dplyr::rename(year = YEAR, total_RF_lbs = TOTAL) %>% 
  # Drop the "total commercial effort category
  subset(., gear != "Total commercial effort")-> total_RF_55_03

# 2004 onwards: PS_CL_1970_2020 (no gear, no region)
PS_CL_1970_2020 %>% 
  mutate(., total_RF_lbs = rowSums(dplyr::select(., -c(Year)), na.rm = TRUE)) %>% 
  dplyr::select(Year, total_RF_lbs) %>% 
  mutate(region = "All PS", gear = "all gear types") %>% 
  dplyr::rename(year = Year) %>% 
  subset(., year >= 2004) -> total_RF_04_20

# Combine all DFs
total_RF_21_54 %>% 
  bind_rows(., total_RF_55_03) %>% 
  bind_rows(., total_RF_04_20)  -> total_RF_21_20

sort(unique(total_RF_21_20$gear))

# Change gear names to be consistent
total_RF_21_20 %>% 
  mutate(., gear = ifelse(gear %in% c("All (combined) troll (1970-1979)", "Bottomfish troll (1980-)", "handline_troll", "Other (salmon) troll (1980-)"), "Troll", gear)) %>% 
  mutate(., gear = ifelse(gear %in% c("beam_trawl", "Bottom trawl", "Midwater trawl", "otter_trawl"), "Trawl", gear)) %>% 
  mutate(., gear = ifelse(gear %in% c("drag_seine", "Drag seine"), "Drag Seine", gear)) %>% 
  mutate(., gear = ifelse(gear %in% c("other_gear", "unknown", "Other gear types"), "Unknown", gear)) %>% 
  mutate(., gear = ifelse(gear == "pound_net", "Pound Net", gear)) %>% 
  mutate(., gear = ifelse(gear %in% c("Handline jig"), "Jig", gear)) %>% 
  mutate(., gear = ifelse(gear %in% c("Salmon net"), "Salmon net" , gear)) %>% 
  mutate(., gear = ifelse(gear %in% c("Set line", "set_line"), "Set line", gear)) %>% 
  mutate(., gear = ifelse(gear %in% c("Set line", "set_line"), "Set line", gear)) %>% 
  mutate(., gear = ifelse(gear %in% c("Set net" , "set_net"), "Set net", gear)) -> total_RF_21_20

```



#### Yelloweye - version 1
```{r combine_commercial_data_1}
# 1921-1933; 1943-1954
yb_catch_estimate_sums %>% 
  dplyr::select(-c(value, bocaccio_mean_catch, bocaccio_min_catch, bocaccio_max_catch)) %>% 
  # Change the "yelloweye_mean_catch" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = yelloweye_mean_catch) %>% 
  mutate(., source = "prorated catch") -> YE_catch_21_54

# 1955-1969
HISCOM_RF_55_69_prorated %>% 
  dplyr::rename(., year = YEAR) %>% 
  dplyr::select(-c(REGION, gear, TOTAL, species, bocaccio_mean_catch, bocaccio_min_catch, bocaccio_max_catch)) %>% 
  # Change the "yelloweye_mean_catch" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = yelloweye_mean_catch) %>% 
  # Sum across all gear types
  group_by(year) %>% 
  summarise_all(sum) %>% 
  mutate(., source = "prorated catch") -> YE_prorated_catch_55_69

# For 1955-1969, add "red snapper" catch to pro-rated 1955-1969 catch
YE_HISCOM %>% 
  dplyr::rename(., year = YEAR) %>% 
  # Change the "TOTAL" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = TOTAL) %>% 
  mutate(., source = "red snapper") %>% 
  dplyr::select(-c(REGION, gear)) %>% 
  # Populate columns with NAs to facilitate joining
  mutate(., yelloweye_min_catch = NA) %>% 
  mutate(., yelloweye_max_catch = NA) %>% 
  subset(., year <= 1969 & year >= 1955) -> red_snapper_catch_55_69

# 1970-2003
YE_HISCOM %>% 
  dplyr::rename(., year = YEAR) %>% 
  # Change the "TOTAL" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = TOTAL) %>% 
  mutate(., source = "cyreis_schmitt") %>% 
  dplyr::select(-c(REGION, gear)) %>% 
  # Populate columns with NAs to facilitate joining
  mutate(., yelloweye_min_catch = NA) %>% 
  mutate(., yelloweye_max_catch = NA) %>% 
  subset(., year <= 2003 & year >= 1970) -> yelloweye_catch_70_03

# 2004-2020
YE_comm_2004_2020 %>% 
  dplyr::rename(., year = Year) %>% 
  # Change the "YE_catch_lbs" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = YE_catch_lbs) %>% 
  mutate(., source = "LiFT System") %>% 
  # Populate columns with NAs to facilitate joining
  mutate(., yelloweye_min_catch = NA) %>% 
  mutate(., yelloweye_max_catch = NA) -> yelloweye_catch_04_20

# Join all sources
YE_catch_21_54 %>% 
  bind_rows(., YE_prorated_catch_55_69) %>% 
  bind_rows(., red_snapper_catch_55_69) %>% 
  bind_rows(., yelloweye_catch_70_03) %>% 
  bind_rows(., yelloweye_catch_04_20) -> YE_catch_estimates_1921_2020
```

Years of overlap with Cyreis Schmitt don't match because my values don't include any catch from West Juan de Fuca.

#### Yelloweye - version 2
```{r combine_commercial_data_YE_2}
# 1921-1933; 1943-1954
yb_catch_estimate_sums %>% 
  dplyr::select(-c(value, bocaccio_mean_catch, bocaccio_min_catch, bocaccio_max_catch)) %>% 
  # Change the "yelloweye_mean_catch" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = yelloweye_mean_catch) %>% 
  mutate(., source = "prorated catch") -> YE_catch_21_54

# 1955-1969
HISCOM_RF_55_69_prorated_2 %>% 
  dplyr::rename(., year = YEAR) %>% 
  dplyr::select(-c(REGION, gear, TOTAL, species, bocaccio_catch_estimate, bocaccio_prop, yelloweye_prop, region)) %>% 
  # Change the "yelloweye_mean_catch" to "yelloweye_catch_estimate"
  # dplyr::rename(., yelloweye_catch_estimate = yelloweye_mean_catch) %>% 
  # Sum across all gear types
  group_by(year) %>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  mutate(., source = "prorated catch") -> YE_prorated_catch_55_69

# For 1955-1969, add "red snapper" catch to pro-rated 1955-1969 catch
YE_HISCOM %>% 
  dplyr::rename(., year = YEAR) %>% 
  # Change the "TOTAL" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = TOTAL) %>% 
  mutate(., source = "red snapper") %>% 
  dplyr::select(-c(REGION, gear)) %>% 
  # Populate columns with NAs to facilitate joining
  mutate(., yelloweye_min_catch = NA) %>% 
  mutate(., yelloweye_max_catch = NA) %>% 
  subset(., year <= 1969 & year >= 1955) -> red_snapper_catch_55_69

# 1970-2003
YE_HISCOM %>% 
  dplyr::rename(., year = YEAR) %>% 
  # Change the "TOTAL" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = TOTAL) %>% 
  mutate(., source = "cyreis_schmitt") %>% 
  dplyr::select(-c(REGION, gear)) %>% 
  # Populate columns with NAs to facilitate joining
  mutate(., yelloweye_min_catch = NA) %>% 
  mutate(., yelloweye_max_catch = NA) %>% 
  subset(., year <= 2003 & year >= 1970) -> yelloweye_catch_70_03

# 2004-2020
YE_comm_2004_2020 %>% 
  dplyr::rename(., year = Year) %>% 
  # Change the "YE_catch_lbs" to "yelloweye_catch_estimate"
  dplyr::rename(., yelloweye_catch_estimate = YE_catch_lbs) %>% 
  mutate(., source = "LiFT System") %>% 
  # Populate columns with NAs to facilitate joining
  mutate(., yelloweye_min_catch = NA) %>% 
  mutate(., yelloweye_max_catch = NA) -> yelloweye_catch_04_20

# Join all sources
YE_catch_21_54 %>% 
  bind_rows(., YE_prorated_catch_55_69) %>% 
  bind_rows(., red_snapper_catch_55_69) %>% 
  bind_rows(., yelloweye_catch_70_03) %>% 
  bind_rows(., yelloweye_catch_04_20) -> YE_catch_estimates_1921_2020_2
```


#### Bocaccio
```{r combine_commercial_data_boc}
# 1921-1933; 1943-1954
yb_catch_estimate_sums %>% 
  dplyr::select(-c(value, yelloweye_mean_catch, yelloweye_min_catch, yelloweye_max_catch)) %>% 
  # Change the "yelloweye_mean_catch" to "yelloweye_catch_estimate"
  dplyr::rename(., bocaccio_catch_estimate = bocaccio_mean_catch) %>% 
  mutate(., source = "prorated catch") -> BOC_catch_21_54

# 1955-1969
HISCOM_RF_55_69_prorated_2 %>% 
  dplyr::rename(., year = YEAR) %>% 
  dplyr::select(-c(REGION, gear, TOTAL, species, yelloweye_catch_estimate, yelloweye_prop, bocaccio_prop, region)) %>% 
  # Change the "bocaccio_mean_catch" to "bocaccio_catch_estimate"
  # dplyr::rename(., bocaccio_catch_estimate = bocaccio_mean_catch) %>% 
  # Sum across all gear types
  group_by(year) %>% 
  summarise_all(sum, na.rm = TRUE) %>% 
  mutate(., source = "prorated catch") -> BOC_prorated_catch_55_69

# 1970-2003
BOC_HISCOM %>% 
  dplyr::rename(., year = YEAR) %>% 
  # Change the "TOTAL" to "bocaccio_catch_estimate"
  dplyr::rename(., bocaccio_catch_estimate = TOTAL) %>% 
  mutate(., source = "cyreis_schmitt") %>% 
  dplyr::select(-c(REGION, gear)) %>% 
  # Populate columns with NAs to facilitate joining
  mutate(., bocaccio_min_catch = NA) %>% 
  mutate(., bocaccio_max_catch = NA) %>% 
  subset(., year <= 2003 & year >= 1970) -> bocaccio_catch_70_03

# 2004-2020
# shelf_RF_comm_2004_2020
# We can't currently prorate the shelf RF catch without any comps data - but it's already so little...
# From Wayne: ">2004 bococcio are shelf species records, could be greenstriped, redstriped too."
# shelf_RF_comm_2004_2020 %>% 
#   dplyr::rename(., year = Year) %>% 
#   # Change the "BOC_catch_lbs" to "bocaccio_catch_estimate"
#   dplyr::rename(., bocaccio_catch_estimate = BOC_catch_lbs) %>% 
#   mutate(., source = "LiFT System") %>% 
#   # Populate columns with NAs to facilitate joining
#   mutate(., bocaccio_min_catch = NA) %>% 
#   mutate(., bocaccio_max_catch = NA) -> bocaccio_catch_04_20

# Join all sources
BOC_catch_21_54 %>% 
  bind_rows(., BOC_prorated_catch_55_69) %>% 
  bind_rows(., bocaccio_catch_70_03) -> BOC_catch_estimates_1921_2003
```

### Plot all commercial catch - Puget Sound

#### Total RF - by gear
```{r plot_total_RF_gear}
RF_commercial_catch_gear_plot <- ggplot(total_RF_21_20, aes(x = year, y = total_RF_lbs, fill = gear))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Total Rockfish Catch by Gear Type")+
  ylab("Catch (pounds)") + 
  xlab("Year")

RF_commercial_catch_gear_plot

ggsave(paste0(fig_dir, "/total_RF_catch_gear.png"), RF_commercial_catch_gear_plot, height = 6, width = 10)

```


#### Total RF - by region
```{r plot_total_RF_region}
RF_commercial_catch_region_plot <- ggplot(total_RF_21_20, aes(x = year, y = total_RF_lbs, fill = region))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Total Commercial Rockfish Catch by Region")+
  ylab("Catch (pounds)") + 
  xlab("Year")

RF_commercial_catch_region_plot

ggsave(paste0(fig_dir, "/total_RF_catch_region.png"), RF_commercial_catch_region_plot, height = 6, width = 10)

```

#### Total RF - Compare Yellow Book and Bound Volumes
```{r}
total_RF_21_20 %>% 
  group_by(year) %>% 
  summarise(annual_catch = sum(total_RF_lbs, na.rm = TRUE)) %>% 
  subset(., year <= 1960 & year >= 1935) %>% 
  mutate(data_source = "Yellow Book") -> YB_PS_annual_sums

BV_PS_annual_sums %>% 
  dplyr::rename(year = YearLanded_Orig) %>% 
  bind_rows(., YB_PS_annual_sums) -> BV_vs_YB_PS_annual_sums

BV_vs_YB_plot <- ggplot(BV_vs_YB_PS_annual_sums, aes(x = year, y = annual_catch, fill = data_source))+
  geom_bar(stat = "identity", width = 0.5, position = "dodge")+
  scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Total Rockfish Catch - Bound Volumes vs. Yellow Book")+
  ylab("Catch (pounds)") + 
  xlab("Year")

BV_vs_YB_plot
```



#### Yelloweye version 1
```{r plot_yelloweye_comm_catch}
YE_commercial_catch_plot <- ggplot(YE_catch_estimates_1921_2020, aes(x = year, y = yelloweye_catch_estimate, fill = source))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Commercial Yelloweye Catch")+
  ylab("Catch (pounds)") + 
  xlab("Year")+
  geom_errorbar(data = subset(YE_catch_estimates_1921_2020, !(year >= 1955 & year <= 1969)), aes(ymin = yelloweye_min_catch, ymax = yelloweye_max_catch), width = 0.25)+
  geom_errorbar(data = subset(YE_catch_estimates_1921_2020, !(year <= 1954 | year >= 1970)), aes(ymin = yelloweye_min_catch+subset(YE_catch_estimates_1921_2020, !(year <= 1954 | year >= 1970) & source == "red snapper")$yelloweye_catch_estimate, ymax = yelloweye_max_catch+subset(YE_catch_estimates_1921_2020, !(year <= 1954 | year >= 1970) & source == "red snapper")$yelloweye_catch_estimate), width = 0.25)

YE_commercial_catch_plot

ggsave(paste0(fig_dir, "/yelloweye_catch_history_1.png"), YE_commercial_catch_plot, height = 6, width = 10)
```

#### Yelloweye version 2
```{r plot_yelloweye_comm_catch}
YE_commercial_catch_plot <- ggplot(YE_catch_estimates_1921_2020_2, aes(x = year, y = yelloweye_catch_estimate, fill = source))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Commercial Yelloweye Catch")+
  ylab("Catch (pounds)") + 
  xlab("Year")+
  geom_errorbar(data = subset(YE_catch_estimates_1921_2020_2, !(year >= 1955 & year <= 1969)), aes(ymin = yelloweye_min_catch, ymax = yelloweye_max_catch), width = 0.25)+
  geom_errorbar(data = subset(YE_catch_estimates_1921_2020_2, !(year <= 1954 | year >= 1970)), aes(ymin = yelloweye_min_catch+subset(YE_catch_estimates_1921_2020_2, !(year <= 1954 | year >= 1970) & source == "red snapper")$yelloweye_catch_estimate, ymax = yelloweye_max_catch+subset(YE_catch_estimates_1921_2020_2, !(year <= 1954 | year >= 1970) & source == "red snapper")$yelloweye_catch_estimate), width = 0.25)

YE_commercial_catch_plot

ggsave(paste0(fig_dir, "/yelloweye_catch_history_2.png"), YE_commercial_catch_plot, height = 6, width = 10)
```

Okay so these two yelloweye plots look very different for the pro-rated yellowbook data (1921-1954), and I think it's because of the changes in region fished. If we apply the region and gear ratios from 1970-1987, there's a lot of effort in the Strait of Juan de Fuca, where the proportion of yelloweye caught is much higher. And I don't think that for the earlier part of this time series that there was much effort in the Strait. So we need to apply some sort of region data to the earlier time series, or else you're going to get very high estimates that are almost certainly off.

What sources do we have for regional effort?
- Rockfish0.xls from Theresa might help
- Bound Volumes have data for 1935 onward... Might help
- Can just make some assumptions and apply those?

#### Bocaccio
```{r plot_yelloweye_comm_catch}
BOC_commercial_catch_plot <- ggplot(BOC_catch_estimates_1921_2003, aes(x = year, y = bocaccio_catch_estimate, fill = source))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Commercial Bocaccio Catch")+
  ylab("Catch (pounds)") + 
  xlab("Year")+
  geom_errorbar(data = subset(BOC_catch_estimates_1921_2003, !(year >= 1955 & year <= 1969)), aes(ymin = bocaccio_min_catch, ymax = bocaccio_max_catch), width = 0.25)

BOC_commercial_catch_plot

ggsave(paste0(fig_dir, "/bocaccio_commercial_catch_history.png"), BOC_commercial_catch_plot, height = 6, width = 10)
```

### Plot Puget Sound + Canada Inside Yelloweye catch

#### Combine commercial catch from Canada and Puget Sound
```{r Canada_PS_combined_yelloweye}
# Reformat DFO data to join with PS data
DFO_recons %>% 
  dplyr::rename(., year = Year) %>% 
  # convert metric tons to pounds
  mutate(., total_catch_lbs = total_catch * 2204.62) %>% 
  mutate(., country = "Canada") %>% 
  dplyr::select(c(year, total_catch_lbs, country)) -> canadian_yelloweye_catch

# Reformat PS data
YE_catch_estimates_1921_2020_2 %>% 
  dplyr::rename(., total_catch_lbs = yelloweye_catch_estimate) %>% 
  dplyr::select(year, total_catch_lbs) %>% 
  mutate(., country = "USA") -> PS_yelloweye_catch

bind_rows(canadian_yelloweye_catch, PS_yelloweye_catch) -> comb_yelloweye_catch
```

#### Plot
```{r plot_yelloweye_comm_catch_Canada_PS_combined}
combined_YE_commercial_catch_plot <- ggplot(comb_yelloweye_catch, aes(x = year, y = total_catch_lbs, fill = country))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Historical Commercial Yelloweye Catch - Canada + USA")+
  ylab("Catch (pounds)") + 
  xlab("Year")

combined_YE_commercial_catch_plot

ggsave(paste0(fig_dir, "/yelloweye_commercial_catch_canada_PS.png"), combined_YE_commercial_catch_plot, height = 6, width = 10)
```



## Recreational Data


### Recreational conversion tables
Necessary for converting number of individuals to weight (kg or lbs)
```{r}
recreational_weight_conversion_path <- here("catch_reconstruction_data", "recreational", "Recreationalconversion.xls")
recreational_weight_conversion <- read_excel(recreational_weight_conversion_path, sheet = "Sheet1", skip = 1)
recreational_weight_conversion %>% 
  dplyr::rename(species = "...2") %>% 
  dplyr::select(-"...1") -> recreational_weight_conversion

# Extract values for yelloweye, bocaccio, all RF
YE_lbs_per_individual <- recreational_weight_conversion[recreational_weight_conversion$species == "Yelloweye rockfish",]$lbs
BOC_lbs_per_individual <- recreational_weight_conversion[recreational_weight_conversion$species == "Bocaccio",]$lbs
RF_lbs_per_individual <- recreational_weight_conversion[recreational_weight_conversion$species == "Misc. rockfish",]$lbs
```

### 1970-2002

Need to compare data from Wayne and Theresa for this time period.

#### Theresa's data: (1975-2002)
```{r load_PS_SL}
PS_SL_path <- here("catch_reconstruction_data", "recreational", "PugetSound_SportLanding.xlsx")
PS_SL <- read_excel(PS_SL_path, skip = 1)
```

There are some significant categories that may include some of our species of interest:
"Bottomfish - Misc" (only 1986)
"Misc. Bottomfish" (1991-2002)
"Misc. Foodfishes" (1987-1990)
"Unclassified" (1975-1985)

The entire year of 1992 is missing from this data

NOTE: According to DPS designation for yelloweye, DPS doesn't extend to MCA 5, which is included in data. However, there are other data sources where MCA is included in a larger region grouping that must be included.

```{r subset_species_PS_SL}
# Subset yelloweye catch
PS_SL_YE <- subset(PS_SL, species == "Yelloweye Rockfish")
# Convert individuals to weights
PS_SL_YE %>% 
  mutate(., catch_lbs = catch*YE_lbs_per_individual) -> PS_SL_YE
# Yelloweye data only from 1975 to 1986
range(PS_SL_YE$year)
# Catch data from all MCAs 5-13
sort(unique(PS_SL_YE$area))

# Subset bocaccio catch
PS_SL_BOC <- subset(PS_SL, species == "Bocaccio")
# Convert individuals to weights
PS_SL_BOC %>% 
  mutate(., catch_lbs = catch*BOC_lbs_per_individual) -> PS_SL_BOC
# Bocaccio data only from 1975 to 1986
range(PS_SL_BOC$year)
# Catch data from all MCAs 5-13
sort(unique(PS_SL_BOC$area))

# Subset total RF catch
PS_SL_RF <- subset(PS_SL, species == "Rockfish - Unclassified") 
# Convert individuals to weights
PS_SL_RF %>% 
  mutate(., catch_lbs = catch*RF_lbs_per_individual) -> PS_SL_RF
# Rockfish data from 1975-2002 (entire length of data), but used most commonly starting in 1987, which conincides with end of many species-specific categories
range(PS_SL_RF$year)
# Catch data from all MCAs 5-13
sort(unique(PS_SL_RF$area))

PS_SL_RF %>% 
  subset(., area != 5) %>% 
  group_by(year) %>% 
  summarise(yearly_lb_total = sum(catch_lbs)) -> PS_SL_RF_annual_totals
```


##### Make plots of data

```{r yelloweye_plot_PS_SL}
PS_SL_YE_plot <- ggplot(PS_SL_YE, aes(x = year, y = catch_lbs, fill = as.factor(area))) +
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  guides(fill=guide_legend(title="MCA"))+
  ylab("Catch (lbs)") +
  xlab("Year") + 
  xlim(1974, 2003)+
  ggtitle("Puget Sound Sport Landings: \"Yelloweye Rockfish\"")

PS_SL_YE_plot
```

```{r bocaccio_plot_PS_SL}
PS_SL_BOC_plot <- ggplot(PS_SL_BOC, aes(x = year, y = catch_lbs, fill = as.factor(area))) +
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  guides(fill=guide_legend(title="MCA"))+
  ylab("Catch (lbs)") +
  xlab("Year") + 
  xlim(1974, 2003)+
  ggtitle("Puget Sound Sport Landings: \"Bocaccio\"")

PS_SL_BOC_plot
```

```{r total_RF_plot_PS_SL}
PS_SL_RF_plot <- ggplot(PS_SL_RF, aes(x = year, y = catch_lbs, fill = as.factor(area))) +
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  guides(fill=guide_legend(title="MCA"))+
  ylab("Catch (lbs)") +
  xlab("Year") + 
  xlim(1974, 2003)+
  ggtitle("Puget Sound Sport Landings: \"Rockfish - unclassified\"")

PS_SL_RF_plot
```

```{r combined_PS_SL_plots}
combined_PS_SL_plot <- ggarrange(PS_SL_YE_plot, PS_SL_BOC_plot, PS_SL_RF_plot, ncol = 1)

ggsave(paste0(fig_dir, "/PugetSound_SportLandings.png"), combined_PS_SL_plot, height = 10, width = 7)

```




#### Wayne's data: (1970-1998)
```{r load_COMREC}
COMREC_path <- here("catch_reconstruction_data", "recreational", "COMREC.xlsx")
COMREC <- read_excel(COMREC_path)
```
```{r subset_species_COMREC}
# Subset yelloweye catch
COMREC_YE <- subset(COMREC, NAME == "Yelloweye rockfish")
# Yelloweye data from 1970-1998
range(COMREC_YE$YEAR)
# Remove summary regions and West Juan de Fuca
COMREC_YE <- subset(COMREC_YE, !(REGION %in% c(7,8,9)))

# Subset bocaccio catch
COMREC_BOC <- subset(COMREC, NAME == "Bocaccio")
# Bocaccio data from 1970-1998
range(COMREC_BOC$YEAR)
# Remove summary regions
COMREC_BOC <- subset(COMREC_BOC, !(REGION %in% c(7,8,9)))

# Subset total RF catch
COMREC_RF <- subset(COMREC, NAME == "Total rockfish") 
# Rockfish data from 1970-1998
range(COMREC_RF$YEAR)
# Remove summary regions
COMREC_RF <- subset(COMREC_RF, !(REGION %in% c(7,8,9)))
```


##### Make plots of data

```{r yelloweye_plot_COMREC}
COMREC_YE_plot <- ggplot(COMREC_YE, aes(x = YEAR, y = RECCAT, fill = as.factor(REGION))) +
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  guides(fill=guide_legend(title="Region"))+
  ylab("Catch (lbs)") +
  xlab("Year") + 
  xlim(1969, 1999)+
  ggtitle("Palsson COMREC Data: \"Yelloweye rockfish\"")

COMREC_YE_plot
```

```{r bocaccio_plot_COMREC}
COMREC_BOC_plot <- ggplot(COMREC_BOC, aes(x = YEAR, y = RECCAT, fill = as.factor(REGION))) +
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  guides(fill=guide_legend(title="Region"))+
  ylab("Catch (lbs)") +
  xlab("Year") + 
  xlim(1969, 1999)+
  ggtitle("Palsson COMREC Data: \"Bocaccio\"")

COMREC_BOC_plot
```

```{r total_RF_plot_COMREC}
COMREC_RF_plot <- ggplot(COMREC_RF, aes(x = YEAR, y = RECCAT, fill = as.factor(REGION))) +
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  guides(fill=guide_legend(title="Region"))+
  ylab("Catch (lbs)") +
  xlab("Year") + 
  xlim(1969, 1999)+
  ggtitle("Palsson COMREC Data: \"Total rockfish\"")

COMREC_RF_plot
```

```{r combined_COMREC_plots}
combined_COMREC_plot <- ggarrange(COMREC_YE_plot, COMREC_BOC_plot, COMREC_RF_plot, ncol = 1)

ggsave(paste0(fig_dir, "/COMREC_Palsson_recreational.png"), combined_COMREC_plot, height = 10, width = 7)

```




#### Catch by numbers of fish (MOST ACCURATE, I THINK)

Here, we're taking the numbers of rockfishes caught by recreational anglers (this is the data that Wayne published in 2009) and prorating it based on the recreational catch compositions from Wayne.
```{r load_rec_catch_70_09}
# Load catch numbers
rec_catch_nos_path <- here("catch_reconstruction_data", "recreational", "rec_catch_numbers_1970_2009.xlsx")

rec_NPS <- read_excel(rec_catch_nos_path, sheet = "North Sound")
rec_NPS[is.na(rec_NPS)] <- 0
rec_SPS <- read_excel(rec_catch_nos_path, sheet = "South Sound")
rec_SPS[is.na(rec_SPS)] <- 0

# Load species composition data
rec_spp_comp_NPS_path <- here("catch_reconstruction_data", "recreational", "north_sound_rec_comps.xlsx")
rec_spp_comp_SPS_path <- here("catch_reconstruction_data", "recreational", "south_sound_rec_comps.xlsx")
# Mean across time periods
rec_mean_spp_comp_path <- here("catch_reconstruction_data", "recreational", "mean_rec_comps.xlsx")

# Load data, replace all NAs with 0s
rec_spp_comp_NPS <- read_excel(rec_spp_comp_NPS_path)
rec_spp_comp_NPS[is.na(rec_spp_comp_NPS)] <- 0
rec_spp_comp_SPS <- read_excel(rec_spp_comp_SPS_path)
rec_spp_comp_SPS[is.na(rec_spp_comp_SPS)] <- 0
rec_mean_spp_comp_NPS <- read_excel(rec_mean_spp_comp_path, sheet = "North Sound")
rec_mean_spp_comp_NPS[is.na(rec_mean_spp_comp_NPS)] <- 0
rec_mean_spp_comp_SPS <- read_excel(rec_mean_spp_comp_path, sheet = "South Sound")
rec_mean_spp_comp_SPS[is.na(rec_mean_spp_comp_SPS)] <- 0
```

When we prorate catch, we'll have a low estimate (1980-1989 proportions) and a high estimate (1965-1967 proportions)
```{r prorate_rec_catch_north_sound}
# North Sound
rec_NPS %>% 
  dplyr::select(Year, `Bocaccio`, `Yelloweye Rockfish`, `Rockfish - General`) -> rec_NPS_subset

# Add the catch composition data
rec_NPS_subset$boc_prop_high <- subset(rec_mean_spp_comp_NPS, Species == "Bocaccio")$`1965-1967a`
rec_NPS_subset$boc_prop_low <- subset(rec_mean_spp_comp_NPS, Species == "Bocaccio")$`1980-1989`

rec_NPS_subset$ye_prop_high <- subset(rec_mean_spp_comp_NPS, Species == "Yelloweye")$`1965-1967a`
rec_NPS_subset$ye_prop_low <- subset(rec_mean_spp_comp_NPS, Species == "Yelloweye")$`1980-1989`

# Prorate, estimate weight
rec_NPS_subset %>% 
  mutate(., Bocaccio_high = Bocaccio + `Rockfish - General`*boc_prop_high/100) %>% 
  mutate(., boc_high_lbs = Bocaccio_high*BOC_lbs_per_individual) %>% 
  mutate(., Bocaccio_low = Bocaccio + `Rockfish - General`*boc_prop_low/100) %>% 
  mutate(., boc_low_lbs = Bocaccio_low*BOC_lbs_per_individual) %>% 
  mutate(., Yelloweye_high = `Yelloweye Rockfish` + `Rockfish - General`*ye_prop_high/100) %>% 
  mutate(., ye_high_lbs = Yelloweye_high*YE_lbs_per_individual) %>% 
  mutate(., Yelloweye_low = `Yelloweye Rockfish` + `Rockfish - General`*ye_prop_low/100) %>% 
  mutate(., ye_low_lbs = Yelloweye_low*YE_lbs_per_individual) %>% 
  mutate(., region = "North Sound") -> rec_NPS_subset
```

```{r prorate_rec_catch_south_sound}
# North Sound
rec_SPS %>% 
  dplyr::select(Year, `Bocaccio`, `Yelloweye Rockfish`, `Rockfish - General`) -> rec_SPS_subset

# Add the catch composition data
rec_SPS_subset$boc_prop_high <- subset(rec_mean_spp_comp_SPS, Species == "Bocaccio")$`1965-1967a`
rec_SPS_subset$boc_prop_low <- subset(rec_mean_spp_comp_SPS, Species == "Bocaccio")$`1980-1989`

rec_SPS_subset$ye_prop_high <- subset(rec_mean_spp_comp_SPS, Species == "Yelloweye")$`1965-1967a`
rec_SPS_subset$ye_prop_low <- subset(rec_mean_spp_comp_SPS, Species == "Yelloweye")$`1980-1989`

# Prorate, estimate weight
rec_SPS_subset %>% 
  mutate(., Bocaccio_high = Bocaccio + `Rockfish - General`*boc_prop_high/100) %>% 
  mutate(., boc_high_lbs = Bocaccio_high*BOC_lbs_per_individual) %>% 
  mutate(., Bocaccio_low = Bocaccio + `Rockfish - General`*boc_prop_low/100) %>% 
  mutate(., boc_low_lbs = Bocaccio_low*BOC_lbs_per_individual) %>% 
  mutate(., Yelloweye_high = `Yelloweye Rockfish` + `Rockfish - General`*ye_prop_high/100) %>% 
  mutate(., ye_high_lbs = Yelloweye_high*YE_lbs_per_individual) %>% 
  mutate(., Yelloweye_low = `Yelloweye Rockfish` + `Rockfish - General`*ye_prop_low/100) %>% 
  mutate(., ye_low_lbs = Yelloweye_low*YE_lbs_per_individual) %>% 
  mutate(., region = "South Sound") -> rec_SPS_subset
```


```{r combine_rec_north_south_sound}
rec_NPS_subset %>% 
  bind_rows(., rec_SPS_subset) %>% 
  dplyr::select(Year, boc_high_lbs, boc_low_lbs, ye_high_lbs, ye_low_lbs) %>% 
  # Group by year and sum across regions
  group_by(Year) %>% 
  summarise_all(sum) %>% 
  subset(., Year <= 2002) -> rec_all_PS_70_02

```





### 2003-2019

Will need to follow up with Theresa to understand how catch and variance were estimated based on raw creel data.

How do we deal with different variances for different MCAs within the DPS?
```{r load_2003_2019_recreational}
# Read in sport landing data
PSP_sport_2003_2019_path <- here("catch_reconstruction_data", "recreational", "PSP Sport Estimates 2003-2019.xlsx")
PSP_sport_2003_2019 <- read_excel(PSP_sport_2003_2019_path, sheet = "All")

# Fix column names
names(PSP_sport_2003_2019) <- gsub(x = names(PSP_sport_2003_2019), pattern = "\r\n", replacement = "_")
names(PSP_sport_2003_2019) <- gsub(x = names(PSP_sport_2003_2019), pattern = "\\.", replacement = "")
names(PSP_sport_2003_2019) <- gsub(x = names(PSP_sport_2003_2019), pattern = " ", replacement = "_")

# Replace zeros with NAs for variance in catch when catch is zero
PSP_sport_2003_2019[PSP_sport_2003_2019$Est_Catch == 0,]$Var_Catch <- NA

# Subset MCAs that are in DPS
# MCAs 4 and 5 are included in this data but are too far west to be in DPS (see Federal Register from 2017)
PSP_sport_all <- subset(PSP_sport_2003_2019, !(MCA %in% c("4", "5")))

# Subset yelloweye
yelloweye_sport_2003_2019 <- subset(PSP_sport_all, Common_Name == "Yelloweye Rockfish")

# Combine all data to get estimates of recreational catch by year
yelloweye_sport_2003_2019 %>% 
  group_by(Year) %>% 
  summarise(., rec_catch = sum(Est_Catch), rec_catch_mean_var = mean(Var_Catch, na.rm = TRUE)) %>% 
    # convert to weight
  mutate(rec_catch_lbs = rec_catch * YE_lbs_per_individual, rec_catch_lbs_mean_var = rec_catch_mean_var * YE_lbs_per_individual) %>% 
 # Drop columns for individuals
dplyr::select(!c(rec_catch, rec_catch_mean_var)) -> yelloweye_rec_2003_2019

# Subset bocaccio
bocaccio_sport_2003_2019 <- subset(PSP_sport_all, Common_Name == "Bocaccio")

# Combine all data to get estimates of recreational catch by year
bocaccio_sport_2003_2019 %>% 
  group_by(Year) %>% 
  summarise(., rec_catch = sum(Est_Catch), rec_catch_mean_var = mean(Var_Catch, na.rm = TRUE)) %>% 
  # convert to weight
  mutate(rec_catch_lbs = rec_catch * BOC_lbs_per_individual, rec_catch_lbs_mean_var = rec_catch_mean_var * BOC_lbs_per_individual) %>% 
 # Drop columns for individuals
dplyr::select(!c(rec_catch, rec_catch_mean_var)) -> bocaccio_rec_2003_2019


# Fill missing years in yelloweye and bocaccio data with rows with zeros using tidyverse::complete
yelloweye_rec_2003_2019 %>% 
  complete(Year = seq(2003, 2019, 1), fill = list(rec_catch_lbs = 0, rec_catch_lbs_mean_var = NA)) -> yelloweye_rec_2003_2019

bocaccio_rec_2003_2019 %>% 
  complete(Year = seq(2003, 2019, 1), fill = list(rec_catch_lbs = 0, rec_catch_lbs_mean_var = NA)) -> bocaccio_rec_2003_2019
```

### Combine recreational catch statistics
```{r combine_rec}
# Yelloweye
rec_all_PS_70_02 %>% 
  dplyr::select(Year, ye_high_lbs, ye_low_lbs) %>% 
  bind_rows(., yelloweye_rec_2003_2019) %>% 
  mutate(., rec_catch_lbs_SD = sqrt(rec_catch_lbs_mean_var)) %>% 
  # Convert to long format
  pivot_longer(cols = c("ye_high_lbs", "ye_low_lbs", "rec_catch_lbs"), names_to = "catch_source") -> YE_rec_1970_2019

# Bocaccio
rec_all_PS_70_02 %>% 
  dplyr::select(Year, boc_high_lbs, boc_low_lbs) %>% 
  bind_rows(., bocaccio_rec_2003_2019) %>% 
  mutate(., rec_catch_lbs_SD = sqrt(rec_catch_lbs_mean_var)) %>% 
  # Convert to long format
  pivot_longer(cols = c("boc_high_lbs", "boc_low_lbs", "rec_catch_lbs"), names_to = "catch_source")-> boc_rec_1970_2019
```

### Plot recreational catch
```{r rec_catch_plot}
# change catch source to factor for plotting
YE_rec_1970_2019 %>% 
  mutate(catch_source = ifelse(catch_source == "ye_high_lbs", "High Catch Estimate", catch_source)) %>% 
  mutate(catch_source = ifelse(catch_source == "ye_low_lbs", "Low Catch Estimate", catch_source)) %>% 
  mutate(catch_source = ifelse(catch_source == "rec_catch_lbs", "Creel Survey (2003-2020)", catch_source)) %>% 
  mutate(catch_source = factor(catch_source, levels = c("High Catch Estimate", "Low Catch Estimate", "Creel Survey (2003-2020)"))) -> YE_rec_1970_2019 

YE_rec_catch_plot <- ggplot(YE_rec_1970_2019, aes(x = Year, y = value, fill = catch_source))+
  geom_bar(stat = "identity", width = 1, position = "dodge")+
  scale_fill_manual(values = c("#1f78b4", "#e31a1c", "#ff7f00"))+
  ggtitle("Recreational Yelloweye Catch")+
  ylab("Catch (pounds)") + 
  xlab("Year")

YE_rec_catch_plot

ggsave(paste0(fig_dir, "/YE_rec_catch.png"), YE_rec_catch_plot, height = 6, width = 10)

# change catch source to factor for plotting
boc_rec_1970_2019 %>% 
  mutate(catch_source = ifelse(catch_source == "boc_high_lbs", "High Catch Estimate", catch_source)) %>% 
  mutate(catch_source = ifelse(catch_source == "boc_low_lbs", "Low Catch Estimate", catch_source)) %>% 
  mutate(catch_source = ifelse(catch_source == "rec_catch_lbs", "Creel Survey (2003-2020)", catch_source)) %>% 
  mutate(catch_source = factor(catch_source, levels = c("High Catch Estimate", "Low Catch Estimate", "Creel Survey (2003-2020)"))) -> boc_rec_1970_2019

boc_rec_catch_plot <- ggplot(boc_rec_1970_2019, aes(x = Year, y = value, fill = catch_source))+
  geom_bar(stat = "identity", width = 1, position = "dodge")+
  scale_fill_manual(values = c("#1f78b4", "#e31a1c", "#ff7f00"))+
  ggtitle("Recreational Yelloweye Catch")+
  ylab("Catch (pounds)") + 
  xlab("Year")

boc_rec_catch_plot

ggsave(paste0(fig_dir, "/boc_rec_catch.png"), boc_rec_catch_plot, height = 6, width = 10)
```

## Combine commercial and recreational catch, plot
```{r rec_commercial_combine_data}
# Yelloweye
YE_rec_1970_2019 %>% 
  dplyr::select(-c(rec_catch_lbs_mean_var, rec_catch_lbs_SD)) %>% 
  group_by(Year) %>% 
  summarise_all(mean, na.rm = TRUE) %>% 
  dplyr::select(Year, value) %>% 
  dplyr::rename(year = Year, catch_lbs = value) %>% 
  mutate(., catch = "Recreational") -> YE_rec_estimates_1970_2019
  
YE_catch_estimates_1921_2020_2 %>% 
  dplyr::select(year, yelloweye_catch_estimate) %>% 
  dplyr::rename(catch_lbs = yelloweye_catch_estimate) %>% 
  mutate(., catch = "Commercial") -> YE_commercial_catch_1921_2020

YE_rec_estimates_1970_2019 %>% 
  bind_rows(., YE_commercial_catch_1921_2020) -> YE_total_catch_history

# Save the yelloweye catch history to share with Jason
YE_total_catch_history[order(YE_total_catch_history$year),] %>% 
  dplyr::rename(catch_type = catch)  -> YE_catch_history
write.csv(YE_catch_history, paste0(here("catch_reconstruction_data"), "/yelloweye_catch_history.csv"))
# Sum recreational and commercial catch
YE_catch_history %>% 
  group_by(year) %>% 
  summarise(total_catch_lbs = sum(catch_lbs, na.rm = TRUE)) -> YE_catch_history_summed
write.csv(YE_catch_history_summed, paste0(here("catch_reconstruction_data"), "/yelloweye_catch_history_summed.csv"))

# Bocaccio
boc_rec_1970_2019
BOC_catch_estimates_1921_2003

boc_rec_1970_2019 %>% 
  dplyr::select(-c(rec_catch_lbs_mean_var, rec_catch_lbs_SD)) %>% 
  group_by(Year) %>% 
  summarise_all(mean, na.rm = TRUE) %>% 
  dplyr::select(Year, value) %>% 
  dplyr::rename(year = Year, catch_lbs = value) %>% 
  mutate(., catch = "Recreational") -> boc_rec_estimates_1970_2019
  
BOC_catch_estimates_1921_2003 %>% 
  dplyr::select(year, bocaccio_catch_estimate) %>% 
  dplyr::rename(catch_lbs = bocaccio_catch_estimate) %>% 
  mutate(., catch = "Commercial") -> BOC_commercial_catch_1921_2003

boc_rec_estimates_1970_2019 %>% 
  bind_rows(., BOC_commercial_catch_1921_2003) -> BOC_total_catch_history
```

### Plot combined catch history
```{r plot_combined_catch_history}
ye_catch_history_plot <- ggplot(YE_total_catch_history, aes(x = year, y = catch_lbs, fill = catch))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = c("#1f78b4", "#33a02c"))+
  ggtitle("Total Yelloweye Catch")+
  ylab("Catch (pounds)") + 
  xlab("Year")

ye_catch_history_plot

ggsave(paste0(fig_dir, "/yelloweye_rockfish_catch_history.png"), ye_catch_history_plot, height = 6, width = 10)


boc_catch_history_plot <- ggplot(BOC_total_catch_history, aes(x = year, y = catch_lbs, fill = catch))+
  geom_bar(stat = "identity")+
  scale_fill_manual(values = c("#1f78b4", "#33a02c"))+
  ggtitle("Total Bocaccio Catch")+
  ylab("Catch (pounds)") + 
  xlab("Year")

boc_catch_history_plot

ggsave(paste0(fig_dir, "/bocaccio_catch_history.png"), boc_catch_history_plot, height = 6, width = 10)
```


## Combine DFO with USA data, commercial AND recreational
```{r YE_USA_CAN_com_rec}
YE_total_catch_history %>% 
  dplyr::rename(total_catch_lbs = catch_lbs) %>% 
  mutate(., country = paste0("USA - ", catch)) %>% 
  bind_rows(., canadian_yelloweye_catch) -> USA_CAN_YE_combined_catch

combined_USA_CANYE_total_catch_plot <- ggplot(USA_CAN_YE_combined_catch, aes(x = year, y = total_catch_lbs, fill = country))+
  geom_bar(stat = "identity")+
  scale_fill_tableau(palette = "Tableau 10")+
  ggtitle("Historical Yelloweye Catch - Canada + USA")+
  ylab("Catch (pounds)") + 
  xlab("Year")

combined_USA_CANYE_total_catch_plot

ggsave(paste0(fig_dir, "/YE_USA_CAN_catch.png"), combined_USA_CANYE_total_catch_plot, height = 6, width = 10)

```


