---
title: "CPUE_modeling"
author: "Markus Min"
date: "`r format(Sys.time(), '%B %d %Y')`"
output: pdf_document
geometry:
- top=1.5in
- bottom=1.5in
- left=1in
- right=1in
---

### Description

This R markdown file will go through fitting a model to our CPUE data to isolate the effect of survey (year) on CPUE of ESA-listed rockfishes.

#### Load libraries
```{r load_libraries, message = FALSE, warning = FALSE}
library(here)
library(tidyverse)
library(pscl)
```


### Import data
```{r}
dat <- read.csv(here("hook_and_line_data", "CPUE_data_for_model.csv"), row.names = 1)
dat$month <- as.character(dat$month)
```

### Plot data distributions

#### Catch
```{r catch_histograms, message = FALSE, warning = FALSE}
fig_dir <- here("figures", "CPUE_data_distributions")

YE_catch_histogram <- ggplot(dat, aes(x = yelloweye_catch, fill = survey)) +
  geom_histogram()+
  scale_x_continuous(breaks = seq(1,10,2))+
  ggtitle("Yelloweye")

YE_catch_histogram
table(dat$yelloweye_catch)

ggsave(paste0(fig_dir, "/yelloweye_catch_hist.png"), width = 5, height = 5, YE_catch_histogram)

boc_catch_histogram <- ggplot(dat, aes(x = bocaccio_catch, fill = survey)) +
  geom_histogram()+
  scale_x_continuous(breaks = seq(1,10,2))+
  ggtitle("Bocaccio")

boc_catch_histogram
table(dat$bocaccio_catch)

ggsave(paste0(fig_dir, "/bocaccio_catch_hist.png"), width = 5, height = 5, boc_catch_histogram)
```

#### Depth
```{r depth_histograms, message = FALSE, warning = FALSE}
depth_histogram <- ggplot(dat, aes(x = mean_depth, fill = survey)) +
  geom_histogram()

depth_histogram

ggsave(paste0(fig_dir, "/effort_depth_hist.png"), width = 5, height = 5, depth_histogram)
```


#### Effort

```{r effort_histograms, message = FALSE, warning = FALSE}
effort_histogram <- ggplot(dat, aes(x = angler_hours, fill = survey)) +
  geom_histogram()

effort_histogram

ggsave(paste0(fig_dir, "/effort_time_hours.png"), width = 5, height = 5, effort_histogram)
```


#### Basin

```{r basin_histogram, message = FALSE, warning = FALSE}
basin_histogram <- ggplot(dat, aes(x = basin, fill = survey)) +
  geom_histogram(stat = "count")+
  theme(axis.text.x = element_text(angle = 90))

basin_histogram

ggsave(paste0(fig_dir, "/basin_histogram.png"), width = 5, height = 5, basin_histogram)
```

#### Month
```{r month_histogram, message = FALSE, warning = FALSE}
month_histogram <- ggplot(dat, aes(x = as.factor(as.numeric(month)), fill = survey)) +
  geom_histogram(stat = "count")+
  xlab("Month")

month_histogram

ggsave(paste0(fig_dir, "/month_histogram.png"), width = 5, height = 5, month_histogram)
```




#### Bait


```{r bait_histogram, message = FALSE, warning = FALSE}
bait_histogram <- ggplot(dat, aes(x = bait, fill = survey)) +
  geom_histogram(stat = "count")+
  theme(axis.text.x = element_text(angle = 90))

bait_histogram 

ggsave(paste0(fig_dir, "/bait_histogram.png"), width = 5, height = 5, bait_histogram)
```

#### Lure


```{r lure_histogram, message = FALSE, warning = FALSE}
lure_histogram <- ggplot(dat, aes(x = lure, fill = survey)) +
  geom_histogram(stat = "count")+
  theme(axis.text.x = element_text(angle = 90))

lure_histogram 
ggsave(paste0(fig_dir, "/lure_histogram.png"), width = 5, height = 5, lure_histogram)

table(dat$lure)
```

#### Lure and bait


```{r lure_histogram, message = FALSE, warning = FALSE}
lure_bait_histogram <- ggplot(dat, aes(x = lure_bait, fill = survey)) +
  geom_histogram(stat = "count")+
  theme(axis.text.x = element_text(angle = 90))

lure_bait_histogram 
ggsave(paste0(fig_dir, "/lure_bait_histogram.png"), width = 5, height = 5, lure_bait_histogram)
```


# Fit models for yelloweye

### Fit model for yelloweye, all data
We will fit a GLM with ZIP distribution of catch, with fixed effects for depth, bait, lure, effort (angler_hours), month (seasonality), basin, and SURVEY.

```{r}
yelloweye_zip_effort_depth <- zeroinfl(yelloweye_catch ~ 
                            offset(angler_hours) | 
                            # Predictors of detection
                            mean_depth, data = dat)

yelloweye_zip_effort_depth <- zeroinfl(yelloweye_catch ~ 
                              # Predictors of counts
                              offset(angler_hours) | 
                              # Predictors of detection
                              mean_depth, data = dat)


summary(yelloweye_zip_effort_depth)
AIC(yelloweye_zip_effort_depth)

# Angler hours not as offset
yelloweye_zip_effort_depth <- zeroinfl(yelloweye_catch ~ 
                            angler_hours| 
                            # Predictors of detection
                            mean_depth, data = dat)
summary(yelloweye_zip_effort_depth)
AIC(yelloweye_zip_effort_depth)
mm <- model.matrix(yelloweye_zip_effort_depth)

# Plot predicted
newdata <- data.frame(cbind(rep(mean(dat$angler_hours), 200), c(1:200)))
colnames(newdata) <- c("angler_hours", "mean_depth")
yelloweye_predicts <- data.frame(c(1:200), predict(yelloweye_zip_effort_depth, newdata = newdata))
colnames(yelloweye_predicts) <- c("mean_depth", "predicted_yelloweye")
ggplot(yelloweye_predicts, aes(x = mean_depth, y = predicted_yelloweye)) + 
  geom_point()

# Angler hours not as offset, remove intercept
yelloweye_zip_effort_depth <- zeroinfl(yelloweye_catch ~ 
                            angler_hours -1 | 
                            # Predictors of detection
                            mean_depth -1, data = dat)

summary(yelloweye_zip_effort_depth)
AIC(yelloweye_zip_effort_depth)
```

#### Add survey and basin
Plot predicted for mean angler hours, in Central Sound, at mean depth
```{r}
# change surveys to factor levels
dat$survey <- factor(dat$survey, levels = c("Percy_Washington", "ESA_Genetics", "lingcod_bycatch" ))
yelloweye_zip_effort_depth_basin_survey <- zeroinfl(yelloweye_catch ~ 
                            offset(angler_hours)| 
                            # Predictors of detection
                            mean_depth + basin + survey, data = dat)
summary(yelloweye_zip_effort_depth_basin_survey)
AIC(yelloweye_zip_effort_depth_basin_survey)
mm <- model.matrix(yelloweye_zip_effort_depth_basin_survey)
# The output is relative to the PW survey now

# Try a new model with survey on the count side
yelloweye_zip_effort_depth_basin_survey <- zeroinfl(yelloweye_catch ~ 
                            offset(angler_hours) + survey | 
                            # Predictors of detection
                            mean_depth + basin, data = dat)


unique(dat$basin)
# Plot predicted

# Create df for predicted values
angler_hours = rep(mean(dat$angler_hours), 3)
mean_depth = rep(mean(dat$mean_depth, na.rm = TRUE), 3)
basin = factor(rep("Central Sound", 3), levels = c("Central Sound", "Whidbey Island", "South Sound", "Straits of Juan de Fuca", "Hood Canal", "San Juan Islands"))
survey = factor(c("Percy_Washington", "ESA_Genetics", "lingcod_bycatch"), levels = c("Percy_Washington", "ESA_Genetics", "lingcod_bycatch" ))
newdata <- data.frame(angler_hours, mean_depth, basin, survey)


# Get predicted values
newdata$phat <- predict(yelloweye_zip_effort_depth_basin_survey, newdata = newdata)
newdata$exp_phat <- exp(newdata$phat)

ggplot(newdata, aes(x = survey, y = exp_phat)) + 
  geom_point()
```


### Fit simple model for PSP only
```{r}
PSP_dat <- subset(dat, basin %in% c("Central Sound",  "Whidbey Island", "South Sound"))
table(subset(PSP_dat, survey == "Percy_Washington")$yelloweye_catch)
table(subset(PSP_dat, survey == "ESA_Genetics")$yelloweye_catch)
table(subset(PSP_dat, survey == "lingcod_bycatch")$yelloweye_catch)

# change surveys to factor levels
PSP_dat$survey <- factor(PSP_dat$survey, levels = c("Percy_Washington", "ESA_Genetics", "lingcod_bycatch" ))

# Survey on detection side
yelloweye_zip_effort_depth_survey <- zeroinfl(yelloweye_catch ~ 
                            offset(angler_hours)| 
                            # Predictors of detection
                            mean_depth + survey -1, data = PSP_dat)
summary(yelloweye_zip_effort_depth_survey)
AIC(yelloweye_zip_effort_depth_survey)
mm <- model.matrix(yelloweye_zip_effort_depth_survey)
# The output is relative to the PW survey now

# Try a new model with survey on the count side
yelloweye_zip_effort_depth_survey <- zeroinfl(yelloweye_catch ~ 
                            offset(angler_hours) + survey -1 | 
                            # Predictors of detection
                            mean_depth, data = PSP_dat)

summary(yelloweye_zip_effort_depth_survey)


unique(dat$basin)
# Plot predicted

# Create df for predicted values
angler_hours = rep(mean(dat$angler_hours), 3)
mean_depth = rep(mean(dat$mean_depth, na.rm = TRUE), 3)
survey = factor(c("Percy_Washington", "ESA_Genetics", "lingcod_bycatch"), levels = c("Percy_Washington", "ESA_Genetics", "lingcod_bycatch" ))
newdata <- data.frame(angler_hours, mean_depth, survey)


# Get predicted values
newdata$phat <- predict(yelloweye_zip_effort_depth_survey, newdata = newdata, type = "count")
# newdata$exp_phat <- exp(newdata$phat)

ggplot(newdata, aes(x = survey, y = phat)) + 
  geom_point()
```


#### Fit the most simple model

For all models, bait, lure, and month don't work (`fitted probabilities numerically 0 or 1 occurredsystem is computationally singular`)
```{r}
yelloweye_zip <- zeroinfl(yelloweye_catch ~ 
                            # Predictors of counts
                            mean_depth + bait + lure + month + basin + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth + bait + lure + month + basin + survey + angler_hours, data = dat)



summary(yelloweye_zip)
AIC(yelloweye_zip)

# Remove bait/lure
yelloweye_zip <- zeroinfl(yelloweye_catch ~ 
                            # Predictors of counts
                            mean_depth + month + basin + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth + month + basin + survey + angler_hours, data = dat)

summary(yelloweye_zip)
AIC(yelloweye_zip)

# Keep only survey, depth, and angler hours
yelloweye_zip <- zeroinfl(yelloweye_catch ~ 
                            # Predictors of counts
                            mean_depth + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth + survey + angler_hours, data = dat)

summary(yelloweye_zip)
AIC(yelloweye_zip)

# Keep only survey, depth, basin, and angler hours
yelloweye_zip <- zeroinfl(yelloweye_catch ~ 
                            # Predictors of counts
                            mean_depth + basin + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth  + basin + survey + angler_hours, data = dat)

summary(yelloweye_zip) 
AIC(yelloweye_zip)
```

So with ZIP models (or other zero-inflated models), there are two processes being modeled: the probability of detection (binomial) and the count process (Poisson). As we see from the model outputs, each of these has its own significance values and estimates of effect size etc.

For the best model (`zeroinfl(formula = yelloweye_catch ~ mean_depth + basin + survey + angler_hours | mean_depth + basin + survey + angler_hours, data = dat)`), angler_hours is the only significant variable for counts, whereas mean depth and basin (Hood Canal or San Juan Islands) are significant in the detection process.



#### Diagnostic plots for best model

##### QQ plot of residuals
```{r}
## qq resids
qqnorm(residuals(yelloweye_zip), main = "QQ plot (residuals)", las = 1, pch = 16)
qqline(residuals(yelloweye_zip))
```
Not great!

##### Residuals vs. fitted
```{r}
plot(fitted(yelloweye_zip), residuals(yelloweye_zip), las = 1, pch = 16,
     xlab = "Fitted", ylab = "Residuals",
     main = "Residuals vs fitted")
abline(h=0, lty = "dashed")
```
Again, not great!

##### ACF
```{r}
## Type-I error
alpha_crit <- 0.05

nsamples <- length(residuals(yelloweye_zip))
nvariables <- 3
## threshold value for rho (correlation)
(rho_crit <- qnorm(1 - alpha_crit/2) / sqrt(nsamples))

## rearrange residuals into matrix
rr <- matrix(residuals(yelloweye_zip), nsamples, nvariables)

## get ACF
ACF <- apply(rr, 2, acf, lag.max = 5, plot = FALSE)
ACF <- lapply(ACF, function(x) x$acf)
## convert list to matrix; don't need row 1 b/c rho_0 = 1
ACF <- do.call(cbind, ACF)[-1,]

## check if any |values| > rho_crit
any(abs(ACF) > rho_crit)
```

I'm not sure I did this right, but looks like no autocorrelation.

### Fit model for yelloweye, only PSP
We will fit a GLM with ZIP distribution of catch, with fixed effects for depth, bait, lure, effort (angler_hours), month (seasonality), basin, and SURVEY.
```{r}
unique(dat$basin)
PSP_dat <- subset(dat, basin %in% c("Central Sound",  "Whidbey Island", "South Sound"))
# yelloweye_zip <- zeroinfl(yelloweye_catch ~ 
#                             # Predictors of counts
#                             mean_depth + bait + lure + month + basin + survey + angler_hours | 
#                             # Predictors of detection
#                             mean_depth + bait + lure + month + basin + survey + angler_hours, data = PSP_dat)
# 
# 
# 
# summary(yelloweye_zip)
# AIC(yelloweye_zip)

# Remove bait/lure
yelloweye_zip <- zeroinfl(yelloweye_catch ~ 
                            # Predictors of counts
                            mean_depth + month + basin + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth + month + basin + survey + angler_hours, data = PSP_dat)

summary(yelloweye_zip)
AIC(yelloweye_zip)

# Keep only survey, depth, basin, and angler hours
yelloweye_zip <- zeroinfl(yelloweye_catch ~ 
                            # Predictors of counts
                            mean_depth + basin + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth  + basin + survey + angler_hours, data = PSP_dat)

summary(yelloweye_zip)
AIC(yelloweye_zip)

# Keep only survey, depth, and angler hours
yelloweye_zip <- zeroinfl(yelloweye_catch ~ 
                            # Predictors of counts
                            mean_depth + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth + survey + angler_hours, data = PSP_dat)

summary(yelloweye_zip)
AIC(yelloweye_zip)
```

Here, the best model by AIC is `zeroinfl(formula = yelloweye_catch ~ mean_depth + survey + angler_hours | mean_depth + survey + angler_hours, data = PSP_dat)`.

In this model, mean depth is the only significant predictor of presence, whereas angler hours and survey (Percy Washington) are significant for counts.


#### Diagnostic plots for best model

##### QQ plot of residuals
```{r}
## qq resids
qqnorm(residuals(yelloweye_zip), main = "QQ plot (residuals)", las = 1, pch = 16)
qqline(residuals(yelloweye_zip))
```
Not great!

##### Residuals vs. fitted
```{r}
plot(fitted(yelloweye_zip), residuals(yelloweye_zip), las = 1, pch = 16,
     xlab = "Fitted", ylab = "Residuals",
     main = "Residuals vs fitted")
abline(h=0, lty = "dashed")
```
Again, not great!

##### ACF
```{r}
## Type-I error
alpha_crit <- 0.05

nsamples <- length(residuals(yelloweye_zip))
nvariables <- 3
## threshold value for rho (correlation)
(rho_crit <- qnorm(1 - alpha_crit/2) / sqrt(nsamples))

## rearrange residuals into matrix
rr <- matrix(residuals(yelloweye_zip), nsamples, nvariables)

## get ACF
ACF <- apply(rr, 2, acf, lag.max = 5, plot = FALSE)
ACF <- lapply(ACF, function(x) x$acf)
## convert list to matrix; don't need row 1 b/c rho_0 = 1
ACF <- do.call(cbind, ACF)[-1,]

## check if any |values| > rho_crit
any(abs(ACF) > rho_crit)
```

#### Plot estimated probability of non-detection and expected count as a function of explanatory variables

How do we modify this code for multiple explanatory variables? I guess we could model each separately?


##### As function of mean depth
Well, I couldn't quite get this to run. Complicated to select only the relevant elements for a single explanatory variable...
```{r eval = FALSE}
# Remove NAs from dat
dat_noNA <- subset(dat, !is.na(mean_depth) & !is.na(basin))

# Sample size
nn <- dim(dat_noNA)[1]

## fitted for detection prob (pi)
mean_depth <- sort(dat$mean_depth)
gamma_hat_0 <- coef(yelloweye_zip)[2]
gamma_hat_1 <- coef(yelloweye_zip)[12]
pi_hat <- 1/(1+exp(-(gamma_hat_0 + gamma_hat_1 * mean_depth)))

## matrix of derivatives
derivs <- matrix(NA, nrow = nn, ncol = 4)
derivs[,1] <- derivs[,2] <- 0
derivs[,3] <- (exp(gamma_hat_0 + gamma_hat_1*mean_depth))/((exp(gamma_hat_0 + gamma_hat_1*mean_depth)+1)^2)
derivs[,4] <- (mean_depth*exp(gamma_hat_0 + gamma_hat_1*mean_depth))/((exp(gamma_hat_0 + gamma_hat_1*mean_depth)+1)^2) 
se <- sqrt( diag ( derivs %*% vcov(yelloweye_zip) %*% t(derivs) ))
lower <- pi_hat - se * qt(0.025, nn-2, lower.tail = FALSE)
upper <- pi_hat + se * qt(0.025, nn-2, lower.tail = FALSE)

## fitted for mean & var (lambda)
beta_hat_0 <- coef(yelloweye_zip)[1]
beta_hat_1 <- coef(yelloweye_zip)[2]
lambda_hat <- exp(beta_hat_0 + beta_hat_1*mean_depth)

## matrix of derivatives
derivs_2 <- matrix(NA, nrow = nn, ncol = 4)
derivs_2[,1] <- exp(beta_hat_0+beta_hat_1*mean_depth)
derivs_2[,2] <- mean_depth*exp(beta_hat_0+beta_hat_1*mean_depth) 
derivs_2[,3] <- derivs_2[,4] <- 0
se_2 <- sqrt( diag ( derivs_2 %*% vcov(yelloweye_zip) %*% t(derivs_2) ))
lower_2 <- lambda_hat - se_2 * qt(0.025, nn-2, lower.tail = FALSE)
upper_2 <- lambda_hat + se_2 * qt(0.025, nn-2, lower.tail = FALSE)

## set plot area
par(mfrow = c(1, 2),
    mai = c(0.9, 0.9, 0.6, 0.1),
    omi = c(0, 0, 0, 0), bg = NA,
    cex.main = 1.2, cex.lab = 1.2)
## detections
plot(mean_depth, pi_hat, type = "l", las = 1, ylim = c(0, 1), lwd = 2, col = "darkgreen",
     xlab = "Tree density", ylab = expression(pi), main = "Missed detection")
lines(mean_depth, lower, lty = 2,  col = "darkgreen", lwd = 2)
lines(mean_depth, upper, lty = 2,  col = "darkgreen", lwd = 2)
## counts
plot(mean_depth, lambda_hat, type = "l", las = 1, ylim = c(0, 20), lwd = 2, col = "darkgreen",
     xlab = "Tree density", ylab = expression(lambda), main = "Counts")
lines(mean_depth, lower_2, lty = 2, col = "darkgreen", lwd = 2)
lines(mean_depth, upper_2, lty = 2, col = "darkgreen", lwd = 2)
```


# Fit models for bocaccio

I think the bocaccio models are having fits with the fact that there were no bocaccio caught during the lingcod bycatch survey... maybe?

### Fit model for bocaccio, all data
We will fit a GLM with ZIP distribution of catch, with fixed effects for depth, bait, lure, effort (angler_hours), month (seasonality), basin, and SURVEY.
```{r}
# Can't include bait/lure
# bocaccio_zip <- zeroinfl(bocaccio_catch ~ 
#                             # Predictors of counts
#                             mean_depth + bait + lure + month + basin + survey + angler_hours | 
#                             # Predictors of detection
#                             mean_depth + bait + lure + month + basin + survey + angler_hours, data = dat)
# 
# 
# 
# summary(bocaccio_zip)
# AIC(bocaccio_zip)

# Remove bait/lure
# bocaccio_zip <- zeroinfl(bocaccio_catch ~ 
#                             # Predictors of counts
#                             mean_depth + month + basin + survey + angler_hours | 
#                             # Predictors of detection
#                             mean_depth + month + basin + survey + angler_hours, data = dat)
# 
# summary(bocaccio_zip)
# AIC(bocaccio_zip)

# Keep only survey, depth, and angler hours
bocaccio_zip <- zeroinfl(bocaccio_catch ~ 
                            # Predictors of counts
                            mean_depth + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth + survey + angler_hours, data = dat)

summary(bocaccio_zip)
AIC(bocaccio_zip)

# Keep only survey, depth, basin, and angler hours
bocaccio_zip <- zeroinfl(bocaccio_catch ~ 
                            # Predictors of counts
                            mean_depth + basin + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth  + basin + survey + angler_hours, data = dat)

summary(bocaccio_zip) 
AIC(bocaccio_zip)
```


For the best model (`zeroinfl(formula = bocaccio_catch ~ mean_depth + basin + survey + angler_hours | mean_depth + basin + survey + angler_hours, data = dat)`), depth, South Sound, Whidbey Island, Percy Washington Survey, and angler hours are all significant for counts. Interestingly, the effect is only positive for depth and PW survey, and negative for all others. There are no significant variables for the detection process.


#### Diagnostic plots for best model

##### QQ plot of residuals
```{r}
## qq resids
qqnorm(residuals(bocaccio_zip), main = "QQ plot (residuals)", las = 1, pch = 16)
qqline(residuals(bocaccio_zip))
```
Not great!
  
##### Residuals vs. fitted
```{r}
plot(fitted(bocaccio_zip), residuals(bocaccio_zip), las = 1, pch = 16,
     xlab = "Fitted", ylab = "Residuals",
     main = "Residuals vs fitted")
abline(h=0, lty = "dashed")
```
Much better than the same plots for yelloweye... but still not great?
  
##### ACF
```{r}
## Type-I error
alpha_crit <- 0.05

nsamples <- length(residuals(bocaccio_zip))
nvariables <- 3
## threshold value for rho (correlation)
(rho_crit <- qnorm(1 - alpha_crit/2) / sqrt(nsamples))

## rearrange residuals into matrix
rr <- matrix(residuals(bocaccio_zip), nsamples, nvariables)

## get ACF
ACF <- apply(rr, 2, acf, lag.max = 5, plot = FALSE)
ACF <- lapply(ACF, function(x) x$acf)
## convert list to matrix; don't need row 1 b/c rho_0 = 1
ACF <- do.call(cbind, ACF)[-1,]

## check if any |values| > rho_crit
any(abs(ACF) > rho_crit)
```

I'm not sure I did this right, but looks like no autocorrelation.

### Fit model for bocaccio, only PSP
We will fit a GLM with ZIP distribution of catch, with fixed effects for depth, bait, lure, effort (angler_hours), month (seasonality), basin, and SURVEY.
```{r}
unique(dat$basin)
PSP_dat <- subset(dat, basin %in% c("Central Sound",  "Whidbey Island", "South Sound"))

# Bait and lure break the model
# bocaccio_zip <- zeroinfl(bocaccio_catch ~ 
#                             # Predictors of counts
#                             mean_depth + bait + lure + month + basin + survey + angler_hours | 
#                             # Predictors of detection
#                             mean_depth + bait + lure + month + basin + survey + angler_hours, data = PSP_dat)
# 
# 
# 
# summary(bocaccio_zip)
# AIC(bocaccio_zip)

# Remove bait/lure
# this doesn't work though
# bocaccio_zip <- zeroinfl(bocaccio_catch ~
#                             # Predictors of counts
#                             mean_depth + month + basin + survey + angler_hours |
#                             # Predictors of detection
#                             mean_depth + month + basin + survey + angler_hours, data = PSP_dat)
# 
# summary(bocaccio_zip)
# AIC(bocaccio_zip)

# Keep only survey, depth, and angler hours
bocaccio_zip <- zeroinfl(bocaccio_catch ~ 
                            # Predictors of counts
                            mean_depth + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth + survey + angler_hours, data = PSP_dat)

summary(bocaccio_zip)
AIC(bocaccio_zip)

# Keep only survey, depth, basin, and angler hours
bocaccio_zip <- zeroinfl(bocaccio_catch ~ 
                            # Predictors of counts
                            mean_depth + basin + survey + angler_hours | 
                            # Predictors of detection
                            mean_depth  + basin + survey + angler_hours, data = PSP_dat)

summary(bocaccio_zip)
AIC(bocaccio_zip)

```

Here, the best model by AIC is `zeroinfl(formula = bocaccio_catch ~ mean_depth + basin + survey + angler_hours | mean_depth + basin + survey + angler_hours, data = PSP_dat)`.

In this model, there are no significant predictors of presence. However, PW survey and depth are significant positive predictors of counts, whereas South Sound, Whidbey Island, and angler hours (???) are negative predictors of counts.


#### Diagnostic plots for best model

##### QQ plot of residuals
```{r}
## qq resids
qqnorm(residuals(bocaccio_zip), main = "QQ plot (residuals)", las = 1, pch = 16)
qqline(residuals(bocaccio_zip))
```
Not great!

##### Residuals vs. fitted
```{r}
plot(fitted(bocaccio_zip), residuals(bocaccio_zip), las = 1, pch = 16,
     xlab = "Fitted", ylab = "Residuals",
     main = "Residuals vs fitted")
abline(h=0, lty = "dashed")
```
Again, not great but better than yelloweye.

##### ACF
```{r}
## Type-I error
alpha_crit <- 0.05

nsamples <- length(residuals(bocaccio_zip))
nvariables <- 3
## threshold value for rho (correlation)
(rho_crit <- qnorm(1 - alpha_crit/2) / sqrt(nsamples))

## rearrange residuals into matrix
rr <- matrix(residuals(bocaccio_zip), nsamples, nvariables)

## get ACF
ACF <- apply(rr, 2, acf, lag.max = 5, plot = FALSE)
ACF <- lapply(ACF, function(x) x$acf)
## convert list to matrix; don't need row 1 b/c rho_0 = 1
ACF <- do.call(cbind, ACF)[-1,]

## check if any |values| > rho_crit
any(abs(ACF) > rho_crit)
```
