---
title: "DFO_yelloweye_inside_analysis"
author: "Markus Min"
date: "7/20/2021"
output: html_document
---


#### Description
This Rmd file contains the investigation of the DFO assessment of the inside Yelloweye Rockfish population, which is essentially the Canadian portion of the Puget Sound/Georgia Basin DPS.



#### Load libraries
```{r load_libraries}
library(tidyverse)
library(here)
library(readxl)
library(ggpubr)
library(egg)
library(grid)
library(r4ss)
```

### Load data from US Side for comparison
Load the re-run from Jason that has comparable units
```{r load_USDPS_rerun}
# Change here directory to where SS outputs are stored
SS_dir <- "/Users/markusmin/Documents/ESA_RF_2021_SS_runs"
YE_USDPS_sum <- SSsummarize(list(YE_USDPS_rerun))

YE_USDPS_rerun <- SS_output(paste0(SS_dir,"/re_run_2021_07_23"),covar=FALSE,ncols=149)

# Get spawning biomass time series
YE_USDPS_rerun$timeseries %>% 
  dplyr::select(Yr, Bio_smry) -> YE_USDPS_spawnbio_mt

# Approximate uncertainty for smry biomass
YE_USDPS_sum$SpawnBio %>% 
  dplyr::rename(spawn_output = model1) %>% 
  dplyr::select(Yr, spawn_output) -> YE_USDPS_spawnoutput

YE_USDPS_sum$SpawnBioSD %>% 
  dplyr::rename(spawn_output_SD = model1) %>% 
  dplyr::select(Yr, spawn_output_SD) -> YE_USDPS_spawnoutputSD

YE_USDPS_spawnoutput %>% 
  left_join(., YE_USDPS_spawnoutputSD, by = "Yr") %>% 
  mutate(., CV = spawn_output_SD/spawn_output) %>% 
  dplyr::select(Yr, CV) -> YE_USDPS_spawnoutputCV

YE_USDPS_spawnbio_mt %>% 
  left_join(., YE_USDPS_spawnoutputCV, by = "Yr") %>% 
  mutate(Bio_smry_SD = CV*Bio_smry) %>% 
  mutate(Bio_smry_upr = Bio_smry + Bio_smry_SD*1.96) %>% 
  mutate(Bio_smry_low = max(0, Bio_smry-Bio_smry_SD*1.96)) -> YE_USDPS_spawnbio_uncertainty

# Get B_ratio
YE_USDPS_sum$Bratio %>% 
  dplyr::rename(US_rel_ssb_median = model1) %>% 
  dplyr::select(Yr, US_rel_ssb_median) -> YE_USDPS_Bratio_median
YE_USDPS_sum$BratioLower %>% 
  dplyr::rename(US_rel_ssb_lower = model1) %>% 
  dplyr::select(Yr, US_rel_ssb_lower) -> YE_USDPS_Bratio_lwr
YE_USDPS_sum$BratioUpper %>% 
  dplyr::rename(US_rel_ssb_upper = model1) %>% 
  dplyr::select(Yr, US_rel_ssb_upper) -> YE_USDPS_Bratio_upr

YE_USDPS_Bratio_median %>% 
  left_join(., YE_USDPS_Bratio_lwr, by = "Yr") %>% 
  left_join(., YE_USDPS_Bratio_upr, by = "Yr") %>% 
  dplyr::rename(year = Yr) -> YE_USDPS_Bratio
```


### Load DFO data
Here we will plot the outputs from the model fit by DFO (Haggarty et al. 2021)
```{r load_data}
DFO_ye_modeloutputs <- read_excel(here("yelloweye-inside", "insideyecosewic.xlsx"))

# Generate proportion relative to unfished
DFO_ye_modeloutputs %>% 
  group_by(scenario) %>% 
  # Biomass
  mutate(., rel_biomass_lwr = biomass_lwr/max(biomass_lwr)) %>% 
  mutate(., rel_biomass_med = biomass_med/max(biomass_med)) %>% 
  mutate(., rel_biomass_upr = biomass_upr/max(biomass_upr)) %>% 
  # SSB
  mutate(., rel_ssb_lwr = ssb_lwr/max(ssb_lwr)) %>% 
  mutate(., rel_ssb_med = ssb_med/max(ssb_med)) %>% 
  mutate(., rel_ssb_upr = ssb_upr/max(ssb_upr)) %>% 
  dplyr::select(-c(`...1`)) %>% 
  # Remove the catch columns
  dplyr::select(-c(Rec_t, Comm_t)) %>% 
  ungroup() -> DFO_ye_modeloutputs

# Convert to long
DFO_ye_modeloutputs %>% 
  pivot_longer(., cols = colnames(DFO_ye_modeloutputs[,3:ncol(DFO_ye_modeloutputs)]), names_to = "metric") -> DFO_ye_modeloutputs_long

# Subset total biomass
DFO_ye_tot_biomass_long <- subset(DFO_ye_modeloutputs_long, metric %in% c("biomass_lwr", "biomass_med", "biomass_upr"))

# Subset total SSB
DFO_ye_tot_ssb_long <- subset(DFO_ye_modeloutputs_long, metric %in% c("ssb_lwr", "ssb_med", "ssb_upr"))

# Subset relative biomass
DFO_ye_rel_biomass_long <- subset(DFO_ye_modeloutputs_long, metric %in% c("rel_biomass_lwr", "rel_biomass_med", "rel_biomass_upr"))

# Subset relative SSB
DFO_ye_rel_ssb_long <- subset(DFO_ye_modeloutputs_long, metric %in% c("rel_ssb_lwr", "rel_ssb_med", "rel_ssb_upr"))

```


```{r plot_biomass_ssb}
# Base model
# Total biomass
ggplot(subset(DFO_ye_tot_biomass_long, scenario == "(1) Base"), aes(x = year, y = value, color = metric)) + 
  geom_line()

# Total SSB
ggplot(subset(DFO_ye_tot_ssb_long, scenario == "(1) Base"), aes(x = year, y = value, color = metric)) + 
  geom_line()

# Relative biomass
ggplot(subset(DFO_ye_rel_biomass_long, scenario == "(1) Base"), aes(x = year, y = value, color = metric)) + 
  geom_line()+
  scale_y_continuous(lim = c(0,1))

# Relative SSB
ggplot(subset(DFO_ye_rel_ssb_long, scenario == "(1) Base"), aes(x = year, y = value, color = metric)) + 
  geom_line()+
  scale_y_continuous(lim = c(0,1))
```



### Make plots for review

#### Prepare data
```{r subset_data_for_plots}
# Replace \r\r with \n
DFO_ye_modeloutputs$scenario <- gsub("\r\r\n",  "\n", DFO_ye_modeloutputs$scenario)
unique(DFO_ye_modeloutputs$scenario)

DFO_basemodel <- subset(DFO_ye_modeloutputs, scenario == "(1) Base")
DFO_lowcatch <- subset(DFO_ye_modeloutputs, scenario == "(2) Low catch")
# DFO_epirec <- subset(DFO_ye_modeloutputs, scenario == "(3) Episodic\r\r\nrecruitment")
# DFO_HBLL_selec <- subset(DFO_ye_modeloutputs, scenario == "(4) Estimate\r\r\nHBLL selectivity")
DFO_epirec <- subset(DFO_ye_modeloutputs, scenario == "(3) Episodic\nrecruitment")
DFO_HBLL_selec <- subset(DFO_ye_modeloutputs, scenario == "(4) Estimate\nHBLL selectivity")
DFO_lowM <- subset(DFO_ye_modeloutputs, scenario == "(A) Low M")
DFO_highHBLLCV <- subset(DFO_ye_modeloutputs, scenario == "(B) High HBLL CV" )
```

### Prepare combined DFO + NOAA relative stock status
```{r rel_DFO_NOAA_data}
YE_USDPS_Bratio

DFO_ye_modeloutputs %>% 
  subset(., scenario == "(1) Base") %>% 
  dplyr::select(year, rel_ssb_lwr, rel_ssb_med, rel_ssb_upr) %>% 
  dplyr::rename(CAN_rel_ssb_lwr = rel_ssb_lwr, CAN_rel_ssb_med = rel_ssb_med, CAN_rel_ssb_upr = rel_ssb_upr) -> DFO_ye_Bratio

DFO_ye_Bratio %>% 
  left_join(., YE_USDPS_Bratio, by = "year") -> CAN_US_YE_Bratio
```

### Prepare combined DFO + NOAA absolute SSB
```{r rel_DFO_NOAA_data}
YE_USDPS_spawnbio_uncertainty %>% 
  dplyr::rename(year = Yr, USA_ssb_upr = Bio_smry_upr, USA_ssb_med = Bio_smry, USA_ssb_lwr = Bio_smry_low) %>% 
  dplyr::select(year, USA_ssb_upr, USA_ssb_med, USA_ssb_lwr) -> YE_USDPS_SSB

DFO_ye_modeloutputs %>% 
  subset(., scenario == "(1) Base") %>% 
  dplyr::select(year, ssb_lwr, ssb_med, ssb_upr) %>% 
  dplyr::rename(CAN_ssb_lwr = ssb_lwr, CAN_ssb_med = ssb_med, CAN_ssb_upr = ssb_upr) -> DFO_ye_abs_SSB

DFO_ye_abs_SSB %>% 
  left_join(., YE_USDPS_SSB, by = "year") -> CAN_US_YE_SSB
```


#### Make functions for plotting
```{r make_abs_SSB_plot_function}
abs_ssb_ggplot <- function(data){
  plot <- ggplot(data, aes(year))+
  geom_ribbon(aes(ymin = ssb_lwr, ymax = ssb_upr), fill = "grey90") +
  geom_line(aes(y = ssb_med))+
  theme(panel.background = element_rect(fill = "white", color = "black"),
        panel.grid = element_blank(),
        legend.position = c(0.9, 0.8),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 15),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        plot.title = element_text(hjust = 0.5, vjust = 2, size = 15),
        axis.text = element_text(size = 12),
        # axis.title = element_text(size = 16)
        axis.title = element_blank())+
  # xlab("Year")+
  # ylab("SSB (metric tons)")+
  ggtitle(unique(data$scenario))+
  scale_y_continuous(expand = c(0,0), limits = c(0, 8000))+
  scale_x_continuous(expand = c(0,0), breaks = seq(1920, 2020, 20))
  plot
}

abs_ssb_ggplot(data = DFO_basemodel)
```

```{r make_rel_SSB_plot_function}
rel_ssb_ggplot <- function(data){
  plot <- ggplot(data = data, aes(year))+
  geom_ribbon(aes(ymin = rel_ssb_lwr, ymax = rel_ssb_upr), fill = "grey90") +
  geom_line(aes(y = rel_ssb_med))+
  theme(axis.text = element_text(size = 12),
        # axis.title = element_text(size = 16),
        axis.title = element_blank(),
        panel.background = element_rect(fill = "white", color = "black"),
        panel.grid = element_blank(),
        legend.position = c(0.9, 0.8),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 15),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        plot.title = element_text(hjust = 0.5, vjust = 2, size = 15))+
  # xlab("Year")+
  # ylab(expression("SSB/SSB"[0]))+
  scale_y_continuous(expand = c(0,0), limits = c(0, 1))+
      ggtitle(unique(data$scenario))+
  scale_x_continuous(expand = c(0,0), breaks = seq(1920, 2020, 20))+
  # Add a reference line - say for 25% of unfished? Since this is detailed in the RRP
  geom_hline(yintercept = 0.25, lty = 2)
  plot
}

rel_ssb_ggplot(data = DFO_basemodel)
```

#### Make combined plots for export
```{r plot_abs_ssb}
abs_ssb_combined_plot <- egg::ggarrange(abs_ssb_ggplot(data = DFO_basemodel), 
                                   abs_ssb_ggplot(data = DFO_lowcatch),
                                   abs_ssb_ggplot(data = DFO_epirec),
                                   abs_ssb_ggplot(data = DFO_HBLL_selec),
                                   abs_ssb_ggplot(data = DFO_lowM),
                                   abs_ssb_ggplot(data = DFO_highHBLLCV),
                                   nrow = 2, ncol = 3,
                                   left = textGrob("SSB (metric tons)", rot = 90, gp = gpar(cex = 1.7)))

# abs_ssb_combined_plot

ggsave(here("figures", "DFO_model_outputs", "abs_ssb_plot.png"), abs_ssb_combined_plot, height = 8, width = 12)
```

```{r plot_rel_ssb}
rel_ssb_combined_plot <- egg::ggarrange(rel_ssb_ggplot(data = DFO_basemodel), 
                                   rel_ssb_ggplot(data = DFO_lowcatch),
                                   rel_ssb_ggplot(data = DFO_epirec),
                                   rel_ssb_ggplot(data = DFO_HBLL_selec),
                                   rel_ssb_ggplot(data = DFO_lowM),
                                   rel_ssb_ggplot(data = DFO_highHBLLCV),
                                   nrow = 2, ncol = 3,
                                   left = textGrob(expression("SSB/SSB"[0]), rot = 90, gp = gpar(cex = 1.7)))

# rel_ssb_combined_plot

ggsave(here("figures", "DFO_model_outputs", "rel_ssb_plot.png"), rel_ssb_combined_plot, height = 8, width = 12)
```


### Plot combined CAN + USA stock status plot
```{r CAN_USA_rel_SSB_plot}

# scale_fill_manual(values = c("#b2182b", "#d6604d", "#f4a582", "#08519c", "#4292c6", "#9ecae1"))+
country_colors <- c("Canada" = "#b2182b", "USA" = "#08519c")

CAN_USA_Bratio_plot <- ggplot(CAN_US_YE_Bratio, aes(year))+
  # uncertainty for Canada
  geom_ribbon(aes(ymin = CAN_rel_ssb_lwr, ymax = CAN_rel_ssb_upr), fill = "#d6604d", alpha = 0.2) +
  # line for Canada median
  geom_line(aes(y = CAN_rel_ssb_med, color = "Canada"), size = 1.5)+
  # uncertainty for US
  geom_ribbon(aes(ymin = US_rel_ssb_lower, ymax = US_rel_ssb_upper), fill = "#4292c6", alpha = 0.2) +
  # line for US median
  geom_line(aes(y = US_rel_ssb_median, color = "USA"), size = 1.5)+
  theme(panel.background = element_rect(fill = "white", color = "black"),
        panel.grid = element_blank(),
        legend.position = c(0.1, 0.9),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 22),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        plot.title = element_text(hjust = 0.5, vjust = 2, size = 15),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 20))+
  labs(x = "Year", y = "Fraction of unfished", color = "Country")+
  scale_y_continuous(expand = c(0,0), limits = c(0, 1.5), breaks = c(0, 0.25, 0.5, 1, 1.5))+
  scale_x_continuous(expand = c(0,0), breaks = seq(1920, 2020, 20))+
  scale_color_manual(values = country_colors)+
  guides(color = guide_legend(override.aes = list(size = 3)))+
  # Add a reference line - say for 25% of unfished? Since this is detailed in the RRP
  geom_hline(yintercept = 0.25, lty = 2)
  
ggsave(here("figures", "DFO_model_outputs", "CAN_USA_Bratio.png"), CAN_USA_Bratio_plot, height = 8, width = 12)
```

### Plot combined CAN + USA biomass plot
```{r CAN_USA_absolute_SSB_plot}
CAN_USA_SSB_plot <- ggplot(CAN_US_YE_SSB, aes(year))+
  # uncertainty for Canada
  geom_ribbon(aes(ymin = CAN_ssb_lwr, ymax = CAN_ssb_upr), fill = "#d6604d", alpha = 0.2) +
  # line for Canada median
  geom_line(aes(y = CAN_ssb_med, color = "Canada"), size = 1.5)+
  # uncertainty for US
  geom_ribbon(aes(ymin = USA_ssb_lwr, ymax = USA_ssb_upr), fill = "#4292c6", alpha = 0.2) +
  # line for US median
  geom_line(aes(y = USA_ssb_med, color = "USA"), size = 1.5)+
  theme(panel.background = element_rect(fill = "white", color = "black"),
        panel.grid = element_blank(),
        legend.position = c(0.9, 0.9),
        legend.text = element_text(size = 18),
        legend.title = element_text(size = 22),
        panel.border = element_rect(colour = "black", fill=NA, size=1),
        plot.title = element_text(hjust = 0.5, vjust = 2, size = 15),
        axis.text = element_text(size = 16),
        axis.title = element_text(size = 20))+
  labs(x = "Year", y = "Spawning stock biomass (metric tons)", color = "Country")+
  scale_y_continuous(expand = c(0,0), limits = c(0, 8000))+
  scale_x_continuous(expand = c(0,0), breaks = seq(1920, 2020, 20))+
  scale_color_manual(values = country_colors)+
  guides(color = guide_legend(override.aes = list(size = 3)))

ggsave(here("figures", "DFO_model_outputs", "CAN_USA_SSB.png"), CAN_USA_SSB_plot, height = 8, width = 12)
```

### Get values for review
```{r get_values}
# When was the minimum?
DFO_basemodel[DFO_basemodel$rel_ssb_med == min(DFO_basemodel$rel_ssb_med),]
# 2002 is the minimum biomass; median is 0.2177, 95% quantiles are 0.1065-0.6147

# What was the stock status in the most recent year?
subset(DFO_basemodel, year == 2019)
# Relative SSB: 0.3209 (95% quantiles 0.151-0.6837)

# Compare current stock sizes between Canada and USA
subset(CAN_US_YE_SSB, year == 2019)
subset(CAN_US_YE_SSB, year == 2019)$USA_ssb_med/subset(CAN_US_YE_SSB, year == 2019)$CAN_ssb_med
# USA portion of stock in 2019 estimated to be at 24.7% of Canadian
# 95% CI: 0-29.2%
subset(CAN_US_YE_SSB, year == 2019)$USA_ssb_lwr/subset(CAN_US_YE_SSB, year == 2019)$CAN_ssb_lwr
subset(CAN_US_YE_SSB, year == 2019)$USA_ssb_upr/subset(CAN_US_YE_SSB, year == 2019)$CAN_ssb_upr

# Compare unfished stock sizes between Canada and USA
subset(CAN_US_YE_SSB, year == 1919)$USA_ssb_med/subset(CAN_US_YE_SSB, year == 1919)$CAN_ssb_med
# Unfished (1919): USA portion of stock estimated to be 9.6% of Canadian
# 95% CI: 0-21.0%
subset(CAN_US_YE_SSB, year == 1919)$USA_ssb_lwr/subset(CAN_US_YE_SSB, year == 1919)$CAN_ssb_lwr
subset(CAN_US_YE_SSB, year == 1919)$USA_ssb_upr/subset(CAN_US_YE_SSB, year == 1919)$CAN_ssb_upr

```



### Hook and line data
To get the hook and line data, we can't use the gfdata package that is used by DFO, because you need access to the PBS network and permissions to access the groundfish databases.

So instead, we will read in the data that was generated from that database by the "01-get-hook-data.R" file.
```{r investigate_HL_data}
yelloweye_rockfish_ins_privacy <- readRDS(here("yelloweye-inside", "data-generated", "yelloweye-rockfish-ins-privacy.rds"))
hbll_joint_index <- readRDS(here("yelloweye-inside", "data-generated", "hbll-joint-index.rds"))
dogfish_index <- readRDS(here("yelloweye-inside", "data-generated", "dogfish-index.rds"))
```

```{r plot_indices}
hbll_joint_index %>% 
  mutate(index = "HBLL") %>% 
  bind_rows(., dogfish_index) %>% 
  mutate(index = ifelse(is.na(index), "Dogfish", index))
```


