---
title: "hook_and_line_analysis"
author: "Markus Min"
date: "7/5/2021"
output: html_document
---

#### Description
This Rmd file goes over the hook and line data/analysis to be included in the 5-year review. It follow the script "CPUE_data_prep.R," which reformats/cleans up the hook and line data.

1. Length composition data
2. CPUE


```{r load_libraries}
library(tidyverse)
library(here)
library(janitor)
library(readxl)
```


#### Load data
```{r load_hook_and_line_data}
CPUE_data <- read.csv(here("hook_and_line_data", "CPUE_data_for_model.csv"), row.names = 1)

pw_orig <- clean_names(read_excel(here("hook_and_line_data", "Washington_et_al_74-77_Puget_Sound_data.xlsx")))

ESA_genetics_orig <- clean_names(read_excel(here("hook_and_line_data","2014_2015_genetics_survey.xlsx"), sheet = "data"))

lingcod_bycatch_orig <- clean_names(read.csv(here("hook_and_line_data","2017_2019_bycatch_survey_catch.csv")))
```

### Calculate CPUE by survey

First we need to make sure the same geographic area is being covered by each survey. For Percy Washington, this is already limited to Puget Sound proper. However, I think we should take out Hood Canal, since PW was barely there and it's a different population.

I don't really think we can compare the lingcod bycatch survey - the issue is that the depths are very different (shallow), targeting a different species (lingcod), and it's mostly limited to Central Sound and the SJI, with a little bit of effort around Whidbey Island
```{r subset_PS_for_surveys}
# Subset PS proper for each survey
unique(CPUE_data$basin)
unique(CPUE_data$survey)

# Percy Washington
PW_CPUE_PSP <- subset(CPUE_data, survey == "Percy_Washington" & basin != "Hood Canal")

# ESA Genetics
ESA_CPUE_PSP <- subset(CPUE_data, survey == "ESA_Genetics" & basin %in% c("Central Sound", "Whidbey Island",  "South Sound"))

# Lingcod bycatch
lingcod_bycatch_CPUE_PSP <- subset(CPUE_data, survey == "lingcod_bycatch"  & basin %in% c("Central Sound", "Whidbey Island",  "South Sound"))

```

```{r calculate_CPUE_by_survey}
### Percy Washington

# Yelloweye
PW_ye_CPUE <- sum(PW_CPUE_PSP$yelloweye_catch)/sum(PW_CPUE_PSP$angler_hours)

# Bocaccio
PW_boc_CPUE <- sum(PW_CPUE_PSP$bocaccio_catch)/sum(PW_CPUE_PSP$angler_hours)



### ESA genetics

# Yelloweye
ESA_genetics_ye_CPUE <- sum(ESA_CPUE_PSP$yelloweye_catch)/sum(ESA_CPUE_PSP$angler_hours)

# Bocaccio
ESA_genetics_boc_CPUE <- sum(ESA_CPUE_PSP$bocaccio_catch)/sum(ESA_CPUE_PSP$angler_hours)


### Lingcod bycatch

# Yelloweye
lingcod_bycatch_ye_CPUE <- sum(lingcod_bycatch_CPUE_PSP$yelloweye_catch)/sum(lingcod_bycatch_CPUE_PSP$angler_hours)

# Bocaccio
lingcod_bycatch_boc_CPUE <- sum(lingcod_bycatch_CPUE_PSP$bocaccio_catch)/sum(lingcod_bycatch_CPUE_PSP$angler_hours)

# Mean depth for each survey
mean(ESA_CPUE_PSP$mean_depth, na.rm = TRUE)
mean(PW_CPUE_PSP$mean_depth, na.rm = TRUE)

# Total angler hours by survey
sum(ESA_CPUE_PSP$angler_hours, na.rm = TRUE)
sum(PW_CPUE_PSP$angler_hours, na.rm = TRUE)
```

### Table of results
Here we will export a table with the following columns:
- survey names
- survey years
- total yelloweye
- total bocaccio
- yelloweye CPUE
- bocaccio CPUE
- total angler hours

```{r generate_table_for_review}
surveys <- c("Percy Washington", "ESA Genetics", "Lingcod Bycatch")
years <- c("1974-1977", "2014-2015", "2017-2019")
total_ye <- c(sum(PW_CPUE_PSP$yelloweye_catch), sum(ESA_CPUE_PSP$yelloweye_catch), sum(lingcod_bycatch_CPUE_PSP$yelloweye_catch))
total_boc <- c(sum(PW_CPUE_PSP$bocaccio_catch), sum(ESA_CPUE_PSP$bocaccio_catch), sum(lingcod_bycatch_CPUE_PSP$bocaccio_catch))
ye_CPUE <- c(PW_ye_CPUE, ESA_genetics_ye_CPUE, lingcod_bycatch_ye_CPUE)
boc_CPUE <- c(PW_boc_CPUE, ESA_genetics_boc_CPUE, lingcod_bycatch_boc_CPUE)
angler_hours <- c(sum(PW_CPUE_PSP$angler_hours), sum(ESA_CPUE_PSP$angler_hours), sum(lingcod_bycatch_CPUE_PSP$angler_hours))

CPUE_table <- data.frame(surveys = surveys, survey_years = years, total_ye = total_ye, total_boc = total_boc, angler_hours = angler_hours, ye_CPUE = ye_CPUE, boc_CPUE = boc_CPUE)

# Round selected values for export
CPUE_table %>% 
  mutate(angler_hours = round(angler_hours, 0)) %>% 
  mutate(ye_CPUE = round(ye_CPUE, 4)) %>% 
  mutate(boc_CPUE = round(boc_CPUE, 4)) -> CPUE_table

# Export CPUE table
write.csv(CPUE_table, paste0(here("outputs"), "/HL_CPUE_table.csv"), row.names = FALSE)
```





