---
title: "hook_and_line_analysis"
author: "Markus Min"
date: "7/5/2021"
output: html_document
---

#### Description
This Rmd file goes over the hook and line data/analysis to be included in the 5-year review. It follow the script "CPUE_data_prep.R," which reformats/cleans up the hook and line data.

1. Length composition data
2. CPUE


```{r load_libraries}
library(tidyverse)
library(here)
library(janitor)
```


#### Load data
```{r load_hook_and_line_data}
CPUE_data <- read.csv(here("hook_and_line_data", "CPUE_data_for_model.csv"), row.names = 1)

pw_orig <- clean_names(read_excel(here("hook_and_line_data", "Washington_et_al_74-77_Puget_Sound_data.xlsx")))

ESA_genetics_orig <- clean_names(read_excel(here("hook_and_line_data","2014_2015_genetics_survey.xlsx"), sheet = "data"))

lingcod_bycatch_orig <- clean_names(read.csv(here("hook_and_line_data","2017_2019_bycatch_survey_catch.csv")))
```

### Calculate CPUE by survey

First we need to make sure the same geographic area is being covered by each survey. For Percy Washington, this is already limited to Puget Sound proper. However, I think we should take out Hood Canal, since PW was barely there and it's a different population.

I don't really think we can compare the lingcod bycatch survey - the issue is that the depths are very different (shallow), targeting a different species (lingcod), and it's mostly limited to Central Sound and the SJI, with a little bit of effort around Whidbey Island
```{r subset_PS_for_surveys}
# Subset PS proper for each survey
PW_CPUE_PSP <- subset(CPUE_data, survey == "Percy_Washington" & basin != "Hood Canal")

ESA_CPUE_PSP <- subset(CPUE_data, survey == "ESA_Genetics" & basin %in% c("Central Sound", "Whidbey Island",  "South Sound", "Straits of Juan de Fuca", "San Juan Islands"))
```

```{r calculate_CPUE_by_survey}
### Percy Washington

# Yelloweye
PW_ye_CPUE <- sum(PW_CPUE_PSP$yelloweye_catch/sum(PW_CPUE_PSP$angler_hours))

# Bocaccio
PW_boc_CPUE <- sum(PW_CPUE_PSP$bocaccio_catch/sum(PW_CPUE_PSP$angler_hours))



### ESA genetics

# Yelloweye
ESA_genetics_ye_CPUE <- sum(ESA_CPUE_PSP$yelloweye_catch/sum(ESA_CPUE_PSP$angler_hours))

# Bocaccio
ESA_genetics_boc_CPUE <- sum(ESA_CPUE_PSP$bocaccio_catch/sum(ESA_CPUE_PSP$angler_hours))

PW_ye_CPUE
PW_boc_CPUE
ESA_genetics_ye_CPUE
ESA_genetics_boc_CPUE


# Mean depth for each survey
mean(ESA_CPUE_PSP$mean_depth, na.rm = TRUE)
mean(PW_CPUE_PSP$mean_depth, na.rm = TRUE)

# Total angler hours by survey
sum(ESA_CPUE_PSP$angler_hours, na.rm = TRUE)
sum(PW_CPUE_PSP$angler_hours, na.rm = TRUE)
```







