---
title: "ROV_analysis"
author: "Markus Min"
date: "4/15/2021"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

### Load libraries, set fig_dir

```{r load_libraries}
library(tidyverse)
library(readxl)
library(here)
library(ggthemes)
library(ggpubr)

# Libraries for creating maps
library(rgdal)
library(broom)
library(ggpubr)
library(sf)

fig_dir <- here("figures", "ROV")
```

# 2015-16 Puget Sound Survey

### Load data

Note: The only species data that has lat/longs of detections is the
2015-2016 PS Survey

Note about unclipped transects: "A number of the transects could not be
fully processed due to missing time values that are needed to clip out
unusable sections, and some cannot be processed because I don't have any
tracking data and that needs to be hand-keyed (these are identified in
one of the attached spreadsheets)."

```{r load_ROV_data_15_16_PS}
ROV_data_path <- here("ROV_data")

PS_15_16_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2015-16 PS Species")

# Convert DMS to decimal degrees
PS_15_16_species %>% 
  mutate(., latitude = Lat_deg + Lat_decmin/60) %>% 
  mutate(., longitude = Long_deg - Long_decmin/60) -> PS_15_16_species

# Order so that Bocaccio is on the bottom and gets plotted on top
PS_15_16_species[order(PS_15_16_species$SpeciesName),] %>% map_df(rev) -> PS_15_16_species

# Load segments data
PS_15_16_segments <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2015-16 PS Segments")

# For the line lengths, keep only the R values (columns 9 - 15)

# Read in clipped lines
# Note: columns 9:15 are the R script results, while columns 1:7 are the ArcGIS results. For consistency with the unclipped segments, we'll use the ArcGIS results
# R results
# read_excel(paste0(ROV_data_path, "/2015-16_smoothed_line_lengths.xlsx"), sheet = "2015-16 High clipped", skip = 7)[,c(9:15)] %>% 
#   dplyr::rename(Tran_ID = Tran_ID...9, Tran_seg = Tran_seg...10, stdev = stdev...15) -> PS_15_16_linelengths_clipped
# ArcGIS results
read_excel(paste0(ROV_data_path, "/2015-16_smoothed_line_lengths.xlsx"), sheet = "2015-16 High clipped", skip = 7)[,c(1:7)] %>%
  dplyr::rename(Tran_ID = Tran_ID...1, Tran_seg = Tran_seg...2, length_m_25 = length_m...3, length_m_50 = length_m...4, length_m_100 = length_m...5, stdev = stdev...7) -> PS_15_16_linelengths_clipped

# Read in unclipped lines
# Note: The other columns on this sheet are the same as the area swept calculations sheet for the clipped segments
read_excel(paste0(ROV_data_path, "/2015-16_smoothed_line_lengths.xlsx"), sheet = "2015-16 High unclipped", skip = 3)[,c(1:6)] -> PS_15_16_linelengths_unclipped

PS_15_16_linelengths_unclipped %>% 
  dplyr::rename(Tran_ID = `tolerance (m)`) -> PS_15_16_linelengths_unclipped


read_excel(paste0(ROV_data_path, "/2015-16_areaswept_12May2021.xlsx"), skip = 3)[,c(1:4)] %>% 
  dplyr::rename(avg_tran_len_m = `avg tran length (m)`, avg_tran_width_m = `avg tran width (m)`, area_swept_m = `area swept (m)`) -> PS_15_16_area_swept

PS_15_16_transects <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2015-16 PS Transects")

PS_15_16_transects %>% 
  mutate(., Survey = "2015-16 PS") %>% 
  mutate(., missingtime = "FALSE") %>% 
  dplyr::select(-AreaSwept) -> PS_15_16_transects

# Load transect locations
# NOTE: These files contain transects that weren't completed; need to subset those
PS_15_transects <- read_excel(paste0(ROV_data_path, "/2015-16 station locations.xlsx"), sheet = "2015 stations")
PS_16_transects <- read_excel(paste0(ROV_data_path, "/2015-16 station locations.xlsx"), sheet = "2016 stations")
PS_15_transects %>% 
  bind_rows(., PS_16_transects) %>% 
  dplyr::rename(Tran_ID = StationID) %>% 
  # Keep only transects that were completed
  subset(., Status == "completed") %>% 
  # Make Tran_ID triple digits (add leading zeros) for joining
  mutate(., Tran_ID = gsub("H", "", Tran_ID)) %>% 
  mutate(., Tran_ID = str_pad(Tran_ID, 3, pad = "0")) %>% 
  mutate(., Tran_ID = paste0("H", Tran_ID)) %>% 
  dplyr::select(Tran_ID, Latitude, Longitude) %>% 
  # Determine if transect in Hood Canal
  mutate(DPS = ifelse(Longitude < -122.71 & Latitude > 47.33 & Latitude < 47.85, "Hood Canal", "U.S. DPS")) -> PS_15_16_transects

# Join lat/longs to area swept
PS_15_16_area_swept %>% 
  left_join(., PS_15_16_transects, by = "Tran_ID")  -> PS_15_16_area_swept

# Make a map to confirm that transects are labeled correctly
# Load shapefile data
usa_spdf <- readOGR(dsn = here("map_files", "USA_adm0.shp"))
usa_spdf_fort <- tidy(usa_spdf)

# Create base map
PS_map <- ggplot(usa_spdf_fort, aes(x = long, y = lat, group = group))+
  # Create grid using geom_vline and geom_hline
  # geom_vline(xintercept = seq(-123.1, min_lon, 1/nm), color = "gray50", size = 0.1)+
  # geom_hline(yintercept = seq(min_lat, 48.5, 1/60), color = "gray50", size = 0.1)+
  #base map
  geom_polygon(color = "gray20")+
  ylab("Latitude")+
  coord_fixed(ylim = c(47.1,48.25),  xlim = c(-123.1,-122.1), ratio = 1.3)+
  theme(plot.background = element_rect(fill = "white"),
        panel.grid = element_blank())

# Add locations
PS_map +
  geom_point(data = PS_15_16_area_swept, aes(x = Longitude, y = Latitude, color = DPS), inherit.aes = FALSE)
```
There's one transect just north of Thorndyke Bay that may or may not be included in Hood Canal, depending on your definition. 

```{r calculate_basin_areas}
# Load areas (these are from Bob and are in hectares)
neah_bay_ha <- 30627
west_JDF_ha <- 99400
east_JDF_ha <- 168330
gulf_bellingham_ha <- 143615
SJI_ha <- 147623
whidbey_basin_ha <- 124854
central_PS_ha <- 222800
south_PS_ha <- 130466
HC_ha <- 125123

basin_areas <- data.frame(basin = c("neah_bay", "west_JDF", "east_JDF", "gulf_bellingham", "SJI", "whidbey_basin", "central_PS", "south_PS", "HC"), area = c(neah_bay_ha, west_JDF_ha, east_JDF_ha, gulf_bellingham_ha, SJI_ha, whidbey_basin_ha, central_PS_ha, south_PS_ha, HC_ha))
```




## Map individuals from survey

### 2015-2016 Puget Sound Survey Map

```{r map_ESA_rockfishes_PS}
# Load shapefile data
usa_spdf <- readOGR(dsn = here("map_files", "USA_adm0.shp"))
usa_spdf_fort <- tidy(usa_spdf)

# Create base map
PS_map <- ggplot(usa_spdf_fort, aes(x = long, y = lat, group = group))+
  # Create grid using geom_vline and geom_hline
  # geom_vline(xintercept = seq(-123.1, min_lon, 1/nm), color = "gray50", size = 0.1)+
  # geom_hline(yintercept = seq(min_lat, 48.5, 1/60), color = "gray50", size = 0.1)+
  #base map
  geom_polygon(color = "gray20")+
  ylab("Latitude")+
  coord_fixed(ylim = c(47.1,48.25),  xlim = c(-123.1,-122.1), ratio = 1.3)+
  theme(plot.background = element_rect(fill = "white"),
        panel.grid = element_blank())

# Add locations
ESA_ROV_detections_map <- PS_map +
  geom_point(data = PS_15_16_species, aes(x = longitude, y = latitude, color = SpeciesName), inherit.aes = FALSE)

# ESA_ROV_detections_map

ggsave(paste0(fig_dir, "/PS_15_16_ROV_map.png"), ESA_ROV_detections_map, height = 8, width = 8)
```

## 2015-2016 Puget Sound Survey Analysis

1)  PS_15_16_species has species observations, linked to transect and segment number
2)  PS_15_16_area_swept has the area swept totals for each transect


```{r reformat_15_16_PS_survey_data}
PS_15_16_species %>% 
  # Rename "Transect" as "Tran_ID" to match area_swept sheet
  dplyr::rename(Tran_ID = Transect) -> PS_15_16_species

# Rename some transects
PS_15_16_species[PS_15_16_species$Tran_ID == "H560 Part 2",]$Tran_ID <- "H560"
PS_15_16_species[PS_15_16_species$Tran_ID == "H408 Part 2",]$Tran_ID <- "H408"

PS_15_16_area_swept
PS_15_16_segments
PS_15_16_linelengths_clipped
```

### Hood Canal population
```{r prepare_HC_data}
# Get list of HC Transects
PS_15_16_HC_transects <- subset(PS_15_16_area_swept, DPS == "Hood Canal")$Tran_ID

# Subset HC species detections
HC_PS_15_16_species <- subset(PS_15_16_species, Tran_ID %in% PS_15_16_HC_transects)
```


#### Calculate stratum density

The area swept for each transect ($A_i$) was the product of the mean transect width ($\overline{W_i}$) and the smoothed transect length ($L_i$). Taxon densities for individual transects ($D_i$) were estimated by dividing the species count ($C_i$) by the transect area: 

$$
D_i = \frac{C_i} {L_i\overline{W_i}} = \frac{C_i} {\overline{A_i}}
$$

```{r HC_PS_15_16_calculate_taxon_densities_for_individual_transects}
# Summarise fish observations for each transect
HC_PS_15_16_species %>% 
  group_by(Tran_ID) %>% 
  # Subset only yelloweye
  subset(SpeciesName == "Yelloweye rockfish") %>% 
  summarise(., total_ye = sum(FishCount)) -> HC_PS_15_16_ye_counts

# Join species observation and area swept values
HC_PS_15_16_ye_counts %>% 
  left_join(., PS_15_16_area_swept, by = "Tran_ID") %>% 
  mutate(., ye_density = total_ye/area_swept_m) -> HC_PS_15_16_ye_density

HC_PS_15_16_ye_density
```

The mean stratum density ($\overline{D_s}$) for a given taxon was then the sum of the individual transect densities divided by the number of transects ($N_s$): 

$$
\overline{D_s} = \frac{\sum\limits_{i=1}^N D_i} {N_s}
$$

```{r HC_PS_15_16_calculate_mean_stratum_density}
# Subset Hood Canal transects
HC_PS_15_16_transects <- subset(PS_15_16_transects, DPS == "Hood Canal")
# Determine number of transects (replace part 1/part 2 with nothing)
HC_PS_15_16_transects %>% 
  mutate(Tran_ID = gsub(" .*", "", Tran_ID)) %>% 
  # Keep only high values
  subset(., grepl("H", Tran_ID)) -> HC_PS_15_16_transects_unique_high
  
HC_PS_15_16_ye_mean_high_stratum_density <- sum(HC_PS_15_16_ye_density$ye_density)/length(unique(HC_PS_15_16_transects_unique_high$Tran_ID))


```

The variance of the mean stratum density was calculated as: 
$$
Var(\overline{D_s}) = \frac{\sum\limits_{i=1}^N (D_i-\overline{D_s})^2} {N_s - 1}
$$

```{r HC_PS_15_16_calculate_mean_stratum_density_variance}
HC_PS_15_16_ye_density %>% 
  mutate(., mean_ye_density = HC_PS_15_16_ye_mean_high_stratum_density) %>% 
  mutate(., square_dens_diff = (ye_density - mean_ye_density)^2) -> HC_PS_15_16_ye_density

HC_PS_15_16_mean_high_stratum_density_var <- sum(HC_PS_15_16_ye_density$square_dens_diff)/(length(unique(HC_PS_15_16_transects_unique_high$Tran_ID))-1)
```

#### Calculate abundance estimates

Total abundance ($P$) in numbers of individuals was the product of the
stratum surface area ($SA_s$) and the mean taxon density ($D$), with
variance calculated as the product of the square of surface area and the variance of
mean stratum density: 

$$
P_s = SA_s\overline{D_s};Var(P_s) = SA_s^2Var(\overline{D_s})
$$

```{r HC_PS_15_16_abundance_estimate}
# Value from Bob: High stratum surface area in Hood Canal (see email on 5/17/21)
HC_PS_15_16_high_surface_area_m2 <- 44859795

HC_PS_15_16_high_stratum_YE_abundance <- HC_PS_15_16_high_surface_area_m2*HC_PS_15_16_ye_mean_high_stratum_density

HC_PS_15_16_high_stratum_YE_variance <- HC_PS_15_16_high_surface_area_m2^2*HC_PS_15_16_mean_high_stratum_density_var
```

Coefficients of variation for each taxon (as percentages) were calculated as the standard deviation of mean stratum density ($\overline{D}$) divided by the product of the square root of the station count ($N$) multiplied by the mean stratum density ($\overline{D}$):

$$
CV = \frac{\sqrt{Var(\overline{D})}} {\sqrt{N}*\overline{D}} * 100
$$

```{r HC_PS_15_16_CV}
HC_PS_15_16_CV <- sqrt(HC_PS_15_16_mean_high_stratum_density_var)/(sqrt(length(unique(HC_PS_15_16_transects_unique_high$Tran_ID)))*HC_PS_15_16_ye_mean_high_stratum_density)*100
```



### non-Hood Canal population
```{r prepare_nonHC_data}
# Get list of nonHC Transects (for subsetting species)
PS_15_16_nonHC_transects <- subset(PS_15_16_area_swept, DPS == "U.S. DPS")$Tran_ID

# Subset nonHC species detections
nonHC_PS_15_16_species <- subset(PS_15_16_species, Tran_ID %in% PS_15_16_nonHC_transects)
```


#### Calculate stratum density

The area swept for each transect ($A_i$) was the product of the mean transect width ($\overline{W_i}$) and the smoothed transect length ($L_i$). Taxon densities for individual transects ($D_i$) were estimated by dividing the species count ($C_i$) by the transect area: 
  
$$
D_i = \frac{C_i} {L_i\overline{W_i}} = \frac{C_i} {\overline{A_i}}
$$
  
```{r nonHC_PS_15_16_calculate_taxon_densities_for_individual_transects}
# Summarise fish observations for each transect
nonHC_PS_15_16_species %>% 
  group_by(Tran_ID) %>% 
  # Subset only yelloweye
  subset(SpeciesName == "Yelloweye rockfish") %>% 
  summarise(., total_ye = sum(FishCount)) -> nonHC_PS_15_16_ye_counts

# Join species observation and area swept values
nonHC_PS_15_16_ye_counts %>% 
  left_join(., PS_15_16_area_swept, by = "Tran_ID") %>% 
  mutate(., ye_density = total_ye/area_swept_m) -> nonHC_PS_15_16_ye_density

nonHC_PS_15_16_ye_density
```

The mean stratum density ($\overline{D_s}$) for a given taxon was then the sum of the individual transect densities divided by the number of transects ($N_s$): 
  
$$
\overline{D_s} = \frac{\sum\limits_{i=1}^N D_i} {N_s}
$$
  
```{r nonHC_PS_15_16_calculate_mean_stratum_density}
# Subset non Hood Canal transects
nonHC_PS_15_16_transects <- subset(PS_15_16_transects, DPS == "U.S. DPS")

# Determine number of transects (replace part 1/part 2 with nothing)
nonHC_PS_15_16_transects %>% 
  mutate(Tran_ID = gsub(" .*", "", Tran_ID)) %>% 
  # Keep only high values
  subset(., grepl("H", Tran_ID)) -> nonHC_PS_15_16_transects_unique_high

nonHC_PS_15_16_ye_mean_high_stratum_density <- sum(nonHC_PS_15_16_ye_density$ye_density)/length(unique(nonHC_PS_15_16_transects_unique_high$Tran_ID))
```

The variance of the mean stratum density was calculated as: 
$$
Var(\overline{D_s}) = \frac{\sum\limits_{i=1}^N (D_i-\overline{D_s})^2} {N_s - 1}
$$
  
```{r nonPS_15_16_calculate_mean_stratum_density_variance}
nonHC_PS_15_16_ye_density %>% 
  mutate(., mean_ye_density = nonHC_PS_15_16_ye_mean_high_stratum_density) %>% 
  mutate(., square_dens_diff = (ye_density - mean_ye_density)^2) -> nonHC_PS_15_16_ye_density

nonHC_PS_15_16_mean_high_stratum_density_var <- sum(nonHC_PS_15_16_ye_density$square_dens_diff)/(length(unique(nonHC_PS_15_16_transects_unique_high$Tran_ID))-1)
```

#### Calculate abundance estimates

Total abundance ($P$) in numbers of individuals was the product of the stratum surface area ($SA_s$) and the mean taxon density ($D$), with variance calculated as the product of the square of surface area and the variance of mean stratum density: 
  
$$
P_s = SA_s\overline{D_s};Var(P_s) = SA_s^2Var(\overline{D_s})
$$
  
```{r nonHC_PS_15_16_abundance_estimate}
# Value from Bob: High stratum surface area in Hood Canal (see email on 5/17/21)
nonHC_PS_15_16_high_surface_area_m2 <- 92876441

nonHC_PS_15_16_high_stratum_YE_abundance <- nonHC_PS_15_16_high_surface_area_m2*nonHC_PS_15_16_ye_mean_high_stratum_density

nonHC_PS_15_16_high_stratum_YE_variance <- nonHC_PS_15_16_high_surface_area_m2^2*nonHC_PS_15_16_mean_high_stratum_density_var
```

Coefficients of variation for each taxon (as percentages) were calculated as the standard deviation of mean stratum density ($\overline{D}$) divided by the product of the square root of the station count ($N$) multiplied by the mean stratum density ($\overline{D}$):
  
$$
CV = \frac{\sqrt{Var(\overline{D})}} {\sqrt{N}*\overline{D}} * 100
$$
  
```{r nonHC_PS_15_16_CV}
nonHC_PS_15_16_CV <- sqrt(nonHC_PS_15_16_mean_high_stratum_density_var)/(sqrt(length(unique(nonHC_PS_15_16_transects_unique_high$Tran_ID)))*nonHC_PS_15_16_ye_mean_high_stratum_density)*100
```

# 2018 San Juan Islands Survey

```{r load_ROV_data_2018_SJI}
ROV_data_path <- here("ROV_data")

SJI_2018_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2018 SJI Species")

# Convert DMS to decimal degrees (no lat/long info currently so this doesn't do anything)
SJI_2018_species %>% 
  mutate(., latitude = Lat_deg + Lat_decmin/60) %>% 
  mutate(., longitude = Long_deg - Long_decmin/60) -> SJI_2018_species

# Fix transect names
SJI_2018_species %>% 
  dplyr::rename(Tran_ID = Transect) %>% 
  mutate(Tran_ID = gsub("-18SJI", "", Tran_ID)) -> SJI_2018_species


# Order so that Bocaccio is on the bottom and gets plotted on top
SJI_2018_species[order(SJI_2018_species$SpeciesName),] %>% map_df(rev) -> SJI_2018_species

# Load segments data
SJI_2018_segments <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2018 SJI Segments")

# Load area swept data
read_excel(paste0(ROV_data_path, "/2018 SJI area swept estimates_25May2021.xlsx"), skip = 3)[,c(1:4)] %>% 
  dplyr::rename(avg_tran_len_m = `avg tran length (m)`, avg_tran_width_m = `avg tran width (m)`, area_swept_m = `area swept (m)`) -> SJI_2018_area_swept

# For now, drop the one problematic transect (H014) in area swept and species files - but no yelloweye in this transect
SJI_2018_area_swept <- subset(SJI_2018_area_swept, !(Tran_ID %in% c("H014")))
SJI_2018_species <- subset(SJI_2018_species, !(Tran_ID %in% c("H014")))

SJI_2018_transects <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2018 SJI Transects")


```


#### Calculate stratum density

The area swept for each transect ($A_i$) was the product of the mean transect width ($\overline{W_i}$) and the smoothed transect length ($L_i$). Taxon densities for individual transects ($D_i$) were estimated by dividing the species count ($C_i$) by the transect area: 

$$
D_i = \frac{C_i} {L_i\overline{W_i}} = \frac{C_i} {\overline{A_i}}
$$

```{r SJI_2018_calculate_taxon_densities_for_individual_transects}
# Summarise fish observations for each transect
SJI_2018_species %>% 
  group_by(Tran_ID) %>% 
  summarise(., total_ye = sum(FishCount)) -> SJI_2018_ye_counts

# Join species observation and area swept values
SJI_2018_ye_counts %>% 
  left_join(., SJI_2018_area_swept, by = "Tran_ID") %>% 
  mutate(., ye_density = total_ye/area_swept_m) -> SJI_2018_ye_density

SJI_2018_ye_density
```

The mean stratum density ($\overline{D_s}$) for a given taxon was then the sum of the individual transect densities divided by the number of transects ($N_s$): 

$$
\overline{D_s} = \frac{\sum\limits_{i=1}^N D_i} {N_s}
$$

```{r SJI_2018_calculate_mean_stratum_density}
# Determine number of transects (replace part 1/part 2 with nothing)
SJI_2018_transects %>% 
  mutate(Transect = gsub(" .*", "", Transect)) %>% 
  # Keep only high values
  subset(., grepl("H", Transect)) -> SJI_2018_transects_unique_high
  
SJI_2018_ye_mean_high_stratum_density <- sum(SJI_2018_ye_density$ye_density)/length(unique(SJI_2018_transects_unique_high$Transect))


```

The variance of the mean stratum density was calculated as: 
$$
Var(\overline{D_s}) = \frac{\sum\limits_{i=1}^N (D_i-\overline{D_s})^2} {N_s - 1}
$$

```{r SJI_2018_calculate_mean_stratum_density_variance}
SJI_2018_ye_density %>% 
  mutate(., mean_ye_density = SJI_2018_ye_mean_high_stratum_density) %>% 
  mutate(., square_dens_diff = (ye_density - mean_ye_density)^2) -> SJI_2018_ye_density

SJI_2018_mean_high_stratum_density_var <- sum(SJI_2018_ye_density$square_dens_diff)/(length(unique(SJI_2018_transects_unique_high$Transect))-1)
```

#### Calculate abundance estimates

Total abundance ($P$) in numbers of individuals was the product of the
stratum surface area ($SA_s$) and the mean taxon density ($D$), with
variance calculated as the product of the square of surface area and the variance of
mean stratum density: 

$$
P_s = SA_s\overline{D_s};Var(P_s) = SA_s^2Var(\overline{D_s})
$$

Areas here are from the survey design notes

```{r SJI_2018_abundance_estimate}
SJI_2018_high_surface_area_ha <- 6036
SJI_2018_high_surface_area_m2 <- 10000*SJI_2018_high_surface_area_ha

SJI_2018_high_stratum_YE_abundance <- SJI_2018_high_surface_area_m2*SJI_2018_ye_mean_high_stratum_density

SJI_2018_high_stratum_YE_variance <- SJI_2018_high_surface_area_m2^2*SJI_2018_mean_high_stratum_density_var
sqrt(SJI_2018_high_stratum_YE_variance)
```

Coefficients of variation for each taxon (as percentages) were calculated as the standard deviation of mean stratum density ($\overline{D}$) divided by the product of the square root of the station count ($N$) multiplied by the mean stratum density ($\overline{D}$):

$$
CV = \frac{\sqrt{Var(\overline{D})}} {\sqrt{N}*\overline{D}} * 100
$$

```{r SJI_2018_CV}
SJI_2018_CV <- sqrt(SJI_2018_mean_high_stratum_density_var)/(sqrt(length(unique(SJI_2018_transects_unique_high$Transect)))*SJI_2018_ye_mean_high_stratum_density)*100
```


# 2018 Vector Survey
I'm a little unsure of what the "explore" transects are, but it seems that they're within the high stratum anyway, so they can probably be treated the same as the other transects.


### Load data

What do the suffixes "-CA-V", "-CA-P1", and "-CA-P2" mean? - P1 and P2
mean part 1 and part 2 - I'm guessing CA-V means Canada-Vector?

```{r load_ROV_data_2018_vector}
ROV_data_path <- here("ROV_data")

# Load counts of species
v18_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2018 Vector Species")

# Rename some of the transects to match with area swept calculations
v18_species %>% 
  # Explore to "Exp"
  mutate(., Transect = gsub("Explore", "Exp", Transect)) %>% 
  # Remove all suffixes
  mutate(., Transect = gsub("-CA.*", "", Transect)) %>% 
  dplyr::rename(Station = Transect) -> v18_species

# Load area swept calculations
v18_areaswept <- read_excel(paste0(ROV_data_path, "/2018_Vector_areaswept.xlsx"), sheet = "2018_Vector_areaswept", skip = 2)
v18_areaswept %>% 
  dplyr::rename(notes = `...5`, avg_tran_width_m = `avg tran width_m`, tran_length_m = `tran length_m`, area_swept = `area swept`)  -> v18_areaswept

# Remove the one low transect
v18_areaswept <- subset(v18_areaswept, Station != "L029")

# # Convert DMS to decimal degrees (no lat/long info currently so this doesn't do anything)
# v18_species %>% 
#   mutate(., latitude = Lat_deg + Lat_decmin/60) %>% 
#   mutate(., longitude = Long_deg - Long_decmin/60) -> v18_species
# 
# # Order so that Bocaccio is on the bottom and gets plotted on top
# v18_species[order(v18_species$SpeciesName),] %>% map_df(rev) -> v18_species

```


### Calculate stratum density

The area swept for each transect ($A_i$) was the product of the meantransect width ($\overline{W_i}$) and the smoothed transect length ($L_i$). Taxon densities for individual transects ($D_i$) were estimated by dividing the species count ($C_i$) by the transect area: 

$$
D_i = \frac{C_i} {L_i\overline{W_i}} = \frac{C_i} {\overline{A_i}}
$$

```{r v18_calculate_taxon_densities_for_individual_transects}
# Summarise fish observations for each transect
v18_species %>% 
  group_by(Station) %>% 
  summarise(., total_ye = sum(FishCount)) -> v18_ye_counts

# Join species observation and area swept values
v18_ye_counts %>% 
  left_join(., v18_areaswept, by = "Station") %>% 
  mutate(., ye_density = total_ye/area_swept) -> v18_density

v18_density
```


The mean stratum density ($\overline{D_s}$) for a given taxon was then the sum of the individual transect densities divided by the number of transects ($N_s$): 
$$
\overline{D_s} = \frac{\sum\limits_{i=1}^N D_i} {N_s}
$$

```{r v18_calculate_mean_stratum_density}
v18_mean_stratum_density <- sum(v18_density$ye_density)/length(unique(v18_areaswept$Station))

```

The variance of the mean stratum density was calculated as: 
$$
Var(\overline{D_s}) = \frac{\sum\limits_{i=1}^N (D_i-\overline{D_s})^2}
{N_s - 1}
$$

```{r v18_calculate_mean_stratum_density_variance}
v18_density %>% 
  mutate(., mean_ye_density = v18_mean_stratum_density) %>% 
  mutate(., square_dens_diff = (ye_density - mean_ye_density)^2) -> v18_density

v18_mean_stratum_density_var <- sum(v18_density$square_dens_diff)/(length(unique(v18_areaswept$Station))-1)
```


#### Calculate abundance estimates

Total abundance ($P$) in numbers of individuals was the product of the stratum surface area ($SA_s$) and the mean taxon density ($D$), with variance calculated as the product of the square of surface area and the variance of mean stratum density: 
$$
P_s = SA_s\overline{D_s};Var(P_s) = SA_s^2Var(\overline{D_s})
$$


```{r v18_abundance_estimate}
# Value from Bob: High stratum surface area in the Strait of Georgia
v18_high_surface_area_ha <- 92031
v18_high_surface_area_m2 <- v18_high_surface_area_ha*10000

v18_high_stratum_YE_abundance <- v18_high_surface_area_m2*v18_mean_stratum_density

v18_high_stratum_YE_variance <- v18_high_surface_area_m2^2*v18_mean_stratum_density_var
```

Coefficients of variation for each taxon (as percentages) were calculated as the standard deviation of mean stratum density ($\overline{D}$) divided by the product of the square root of the station count ($N$) multiplied by the mean stratum density ($\overline{D}$):
  
$$
CV = \frac{\sqrt{Var(\overline{D})}} {\sqrt{N}*\overline{D}} * 100
$$
  
```{r v18_CV}
v18_CV <- sqrt(v18_mean_stratum_density_var)/(sqrt(length(unique(v18_areaswept$Station)))*v18_mean_stratum_density)*100
```

# 2018 Gulf Islands Survey

Note: For this survey, we are only looking at the "inside" portion of the survey area, since all of the "outside" stations were dropped.

```{r load_ROV_data_2018_GI}
ROV_data_path <- here("ROV_data")

GI_2018_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2018 GI Species")

# Rename some of the transects to match with area swept calculations
GI_2018_species %>% 
  # Change "Part 1" to "A"
  mutate(., Transect = gsub(" Part 1", "A", Transect)) %>% 
  dplyr::rename(Station = Transect) -> GI_2018_species

# Load area swept calculations
GI_2018_areaswept <- read_excel(paste0(ROV_data_path, "/2018 CGI transect stats.xlsx"), sheet = "2018 CGI area swept", skip = 3)
GI_2018_areaswept %>% 
  dplyr::rename(Station = `Row Labels`, avg_tran_width_m = `tran width`, tran_length_m = `tran length`, area_swept = `area swept`)  -> GI_2018_areaswept

# Remove all of the explore transects
GI_2018_species <- GI_2018_species[grep("CA", GI_2018_species$Station),]
```


### Calculate stratum density

The area swept for each transect ($A_i$) was the product of the meantransect width ($\overline{W_i}$) and the smoothed transect length ($L_i$). Taxon densities for individual transects ($D_i$) were estimated by dividing the species count ($C_i$) by the transect area: 

$$
D_i = \frac{C_i} {L_i\overline{W_i}} = \frac{C_i} {\overline{A_i}}
$$

```{r GI_2018_calculate_taxon_densities_for_individual_transects}
# Summarise fish observations for each transect
GI_2018_species %>% 
  group_by(Station) %>% 
  summarise(., total_ye = sum(FishCount)) -> GI_2018_ye_counts



# Join species observation and area swept values
GI_2018_ye_counts %>% 
  left_join(., GI_2018_areaswept, by = "Station") %>% 
  mutate(., ye_density = total_ye/area_swept) -> GI_2018_density

GI_2018_density
```


The mean stratum density ($\overline{D_s}$) for a given taxon was then the sum of the individual transect densities divided by the number of transects ($N_s$): 
$$
\overline{D_s} = \frac{\sum\limits_{i=1}^N D_i} {N_s}
$$

```{r GI_2018_calculate_mean_stratum_density}
# Subset medium and high
GI_2018_density_high <- GI_2018_density[grep("H", GI_2018_density$Station),]
GI_2018_density_med <- GI_2018_density[grep("M", GI_2018_density$Station),]

# Calculate high stratum density
GI_2018_mean_high_stratum_density <- sum(GI_2018_density_high$ye_density)/length(grep("H", GI_2018_areaswept$Station))

# Calculate medium stratum density
GI_2018_mean_med_stratum_density <- sum(GI_2018_density_med$ye_density)/length(grep("M", GI_2018_areaswept$Station))
```

The variance of the mean stratum density was calculated as: 
$$
Var(\overline{D_s}) = \frac{\sum\limits_{i=1}^N (D_i-\overline{D_s})^2}
{N_s - 1}
$$

```{r GI_2018_calculate_mean_stratum_density_variance}
# High stratum
GI_2018_density_high %>% 
  mutate(., mean_ye_density = GI_2018_mean_high_stratum_density) %>% 
  mutate(., square_dens_diff = (ye_density - mean_ye_density)^2) -> GI_2018_density_high

GI_2018_mean_high_stratum_density_var <- sum(GI_2018_density_high$square_dens_diff)/(length(grep("H", GI_2018_areaswept$Station))-1)

# Medium stratum
GI_2018_density_med %>% 
  mutate(., mean_ye_density = GI_2018_mean_med_stratum_density) %>% 
  mutate(., square_dens_diff = (ye_density - mean_ye_density)^2) -> GI_2018_density_med

GI_2018_mean_med_stratum_density_var <- sum(GI_2018_density_med$square_dens_diff)/(length(grep("M", GI_2018_areaswept$Station))-1)
```


#### Calculate abundance estimates

Total abundance ($P$) in numbers of individuals was the product of the stratum surface area ($SA_s$) and the mean taxon density ($D$), with variance calculated as the product of the square of surface area and the variance of mean stratum density: 
$$
P_s = SA_s\overline{D_s};Var(P_s) = SA_s^2Var(\overline{D_s})
$$


```{r GI_2018_abundance_estimate}
# High Stratum
# Value from Bob: High stratum surface area for the inside area of the Gulf Islands
GI_2018_high_surface_area_ha <- 6070
GI_2018_high_surface_area_m2 <- GI_2018_high_surface_area_ha*10000

GI_2018_high_stratum_YE_abundance <- GI_2018_high_surface_area_m2*GI_2018_mean_high_stratum_density

GI_2018_high_stratum_YE_variance <- GI_2018_high_surface_area_m2^2*GI_2018_mean_high_stratum_density_var

# Medium stratum
# Value from Bob: High stratum surface area in the Strait of Georgia
GI_2018_med_surface_area_ha <- 21462
GI_2018_med_surface_area_m2 <- GI_2018_med_surface_area_ha*10000

GI_2018_med_stratum_YE_abundance <- GI_2018_med_surface_area_m2*GI_2018_mean_med_stratum_density

GI_2018_med_stratum_YE_variance <- GI_2018_med_surface_area_m2*GI_2018_mean_med_stratum_density_var

```

Coefficients of variation for each taxon (as percentages) were calculated as the standard deviation of mean stratum density ($\overline{D}$) divided by the product of the square root of the station count ($N$) multiplied by the mean stratum density ($\overline{D}$):
  
$$
CV = \frac{\sqrt{Var(\overline{D})}} {\sqrt{N}*\overline{D}} * 100
$$
  
```{r GI_2018_CV}
# High stratum
GI_2018_high_CV <- sqrt(GI_2018_mean_high_stratum_density_var)/(sqrt(length(grep("H", GI_2018_areaswept$Station)))*GI_2018_mean_high_stratum_density)*100

# Medium stratum
GI_2018_med_CV <- sqrt(GI_2018_mean_med_stratum_density_var)/(sqrt(length(grep("M", GI_2018_areaswept$Station)))*GI_2018_mean_med_stratum_density)*100
```

# Summarise results from each survey

Make a table with six fields: survey name, species, abundance, CV (%), area, year(s) of survey

Data for the 2008 and 2010 San Juan Islands surveys just pulled out of the corresponding reports:
- 2008 SJI: Pacusnki et al. 2013, table 5 (page 27)
  - abundance: 47407
  - %CV: 24.8
- 2010 SJI: Pacunski et al. 2020, table 1 (page 24)
  - abundance: 114494
  - %CV: 33
  
- Well these are crazy different...
- 2008 SJI survey design:
  - bottom habitat mapping from MBES (multibeam echosounder); only surveyed rocky habitat, which was divided into "shallow" and "deep" strata
  - random sampling within these strata
  - density from ROV surveys in "shallow rock" and "deep rock" multiplied by total areas of these strata
- 2010 SJI survey design: 
  - Divided into eastern and western SJI, based on knowledge from last survey where most rockfish were found in the western SJI
  - "Stations were placed along a systematic grid from a random starting point, with Eastern stations spaced at 3,000 m intervals and Western stations spaced at 2,100 m intervals" 
  - multiplied densities in each stratum by area of each stratum (eastern or western SJI)
    - probably explains why estimates were much higher
    
- Note: 2018 SJI survey is again different, using the maxent design

- 2008 SJI: Pacusnki et al. 2013, table 5 (page 27)
  - abundance: 47407
  - %CV: 24.8
- 2010 SJI: Pacunski et al. 2020, table 1 (page 24)
  - abundance: 114494
  - %CV: 33
```{r summarise_ROV_results}

survey_names <- c("2008 San Juan Islands", "2010 San Juan Islands", "2015-16 Puget Sound", "2015-16 Puget Sound", "2018 San Juan Islands", "2018 Gulf Islands - High Stratum", "2018 Gulf Islands - Medium Stratum",  "2018 Vector")

survey_areas <- c("San Juan Islands", "San Juan Islands", "Puget Sound Proper (excluding Hood Canal)", "Hood Canal", "San Juan Islands", "Gulf Islands (Inside)", "Gulf Islands (Inside)", "Strait of Georgia (CA)")

years <- c("2008", "2010", "2015, 2016", "2015, 2016", "2018", "2018", "2018", "2018")


YE_ROV_results_summary <- data.frame(survey = survey_names, area = survey_areas, year = years, species = rep("Yelloweye Rockfish", length(survey_names)), abundance = rep(NA,length(survey_names)), CV = rep(NA,length(survey_names)))

# 2008 San Juan Islands
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2008 San Juan Islands",]$abundance <- 47407
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2008 San Juan Islands",]$CV <- 24.8

# 2010 San Juan Islands
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2010 San Juan Islands",]$abundance <- 114494
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2010 San Juan Islands",]$CV <- 33

# 2015-16 Puget Sound results - US DPS
YE_ROV_results_summary[YE_ROV_results_summary$area == "Puget Sound Proper (excluding Hood Canal)",]$abundance <- nonHC_PS_15_16_high_stratum_YE_abundance

YE_ROV_results_summary[YE_ROV_results_summary$area == "Puget Sound Proper (excluding Hood Canal)",]$CV <- nonHC_PS_15_16_CV

  
# 2015-16 Puget Sound results - Hood Canal
YE_ROV_results_summary[YE_ROV_results_summary$area == "Hood Canal",]$abundance <- HC_PS_15_16_high_stratum_YE_abundance
YE_ROV_results_summary[YE_ROV_results_summary$area == "Hood Canal",]$CV <- HC_PS_15_16_CV

# 2018 San Juan Islands
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2018 San Juan Islands",]$abundance <- SJI_2018_high_stratum_YE_abundance
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2018 San Juan Islands",]$CV <- SJI_2018_CV

# 2018 Vector
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2018 Vector",]$abundance <- v18_high_stratum_YE_abundance
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2018 Vector",]$CV <- v18_CV

# 2018 Gulf Islands - High Stratum
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2018 Gulf Islands - High Stratum",]$abundance <- GI_2018_high_stratum_YE_abundance
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2018 Gulf Islands - High Stratum",]$CV <- GI_2018_high_CV

# 2018 Gulf Islands - Medium Stratum
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2018 Gulf Islands - Medium Stratum",]$abundance <- GI_2018_med_stratum_YE_abundance
YE_ROV_results_summary[YE_ROV_results_summary$survey == "2018 Gulf Islands - Medium Stratum",]$CV <- GI_2018_med_CV


# Save results
write.csv(YE_ROV_results_summary, paste0(here("outputs"), "/ROV_survey_abundance_estimates.csv"), row.names=FALSE)
```

