---
title: "ROV_analysis"
author: "Markus Min"
date: "4/15/2021"
output: html_document
---

### Load libraries, set fig_dir
```{r load_libraries}
library(tidyverse)
library(readxl)
library(here)
library(ggthemes)
library(ggpubr)

# Libraries for creating maps
library(rgdal)
library(broom)
library(ggpubr)
library(sf)

fig_dir <- here("figures", "ROV")
```


### Load data

Note: The only species data that has lat/longs of detections is the 2015-2016 PS Survey

Note about unclipped transects: "A number of the transects could not be fully processed due to missing time values that are needed to clip out unusable sections, and some cannot be processed because I don’t have any tracking data and that needs to be hand-keyed (these are identified in one of the attached spreadsheets)."

#### 2015-2016 Puget Sound Survey
```{r load_ROV_data_15_16_PS}
ROV_data_path <- here("ROV_data")

PS_15_16_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2015-16 PS Species")

# Convert DMS to decimal degrees
PS_15_16_species %>% 
  mutate(., latitude = Lat_deg + Lat_decmin/60) %>% 
  mutate(., longitude = Long_deg - Long_decmin/60) -> PS_15_16_species

# Order so that Bocaccio is on the bottom and gets plotted on top
PS_15_16_species[order(PS_15_16_species$SpeciesName),] %>% map_df(rev) -> PS_15_16_species

# Load segments data
PS_15_16_segments <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2015-16 PS Segments")

# For the line lengths, keep only the R values (columns 9 - 15)

# Read in clipped lines
# Note: columns 9:15 are the R script results, while columns 1:7 are the ArcGIS results. For consistency with the unclipped segments, we'll use the ArcGIS results
# R results
# read_excel(paste0(ROV_data_path, "/2015-16_smoothed_line_lengths.xlsx"), sheet = "2015-16 High clipped", skip = 7)[,c(9:15)] %>% 
#   dplyr::rename(Tran_ID = Tran_ID...9, Tran_seg = Tran_seg...10, stdev = stdev...15) -> PS_15_16_linelengths_clipped
# ArcGIS results
read_excel(paste0(ROV_data_path, "/2015-16_smoothed_line_lengths.xlsx"), sheet = "2015-16 High clipped", skip = 7)[,c(1:7)] %>%
  dplyr::rename(Tran_ID = Tran_ID...1, Tran_seg = Tran_seg...2, length_m_25 = length_m...3, length_m_50 = length_m...4, length_m_100 = length_m...5, stdev = stdev...7) -> PS_15_16_linelengths_clipped

# Read in unclipped lines
# Note: The other columns on this sheet are the same as the area swept calculations sheet for the clipped segments
read_excel(paste0(ROV_data_path, "/2015-16_smoothed_line_lengths.xlsx"), sheet = "2015-16 High unclipped", skip = 3)[,c(1:6)] -> PS_15_16_linelengths_unclipped

read_excel(paste0(ROV_data_path, "/2015-16_areaswept_7Apr2021.xlsx"), skip = 3)[,c(1:4)] %>% 
  dplyr::rename(avg_tran_len_m = `avg tran length (m)`, avg_tran_width_m = `avg tran width (m)`, area_swept_m = `area swept (m)`) -> PS_15_16_area_swept
```

#### 2018 San Juan Islands Survey
```{r load_ROV_data_15_16_PS}
ROV_data_path <- here("ROV_data")

SJI_2018_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2018 SJI Species")

# Convert DMS to decimal degrees (no lat/long info currently so this doesn't do anything)
SJI_2018_species %>% 
  mutate(., latitude = Lat_deg + Lat_decmin/60) %>% 
  mutate(., longitude = Long_deg - Long_decmin/60) -> SJI_2018_species

# Order so that Bocaccio is on the bottom and gets plotted on top
SJI_2018_species[order(SJI_2018_species$SpeciesName),] %>% map_df(rev) -> SJI_2018_species
```

#### 2018 Vector Survey
```{r load_ROV_data_15_16_PS}
ROV_data_path <- here("ROV_data")

vector_2018_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2018 Vector Species")

# Convert DMS to decimal degrees (no lat/long info currently so this doesn't do anything)
vector_2018_species %>% 
  mutate(., latitude = Lat_deg + Lat_decmin/60) %>% 
  mutate(., longitude = Long_deg - Long_decmin/60) -> vector_2018_species

# Order so that Bocaccio is on the bottom and gets plotted on top
vector_2018_species[order(vector_2018_species$SpeciesName),] %>% map_df(rev) -> vector_2018_species
```

#### 2018 Gulf Islands Survey
```{r load_ROV_data_15_16_PS}
ROV_data_path <- here("ROV_data")

GI_2018_species <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2018 GI Species")

# Convert DMS to decimal degrees (no lat/long info currently so this doesn't do anything)
GI_2018_species %>% 
  mutate(., latitude = Lat_deg + Lat_decmin/60) %>% 
  mutate(., longitude = Long_deg - Long_decmin/60) -> GI_2018_species

# Order so that Bocaccio is on the bottom and gets plotted on top
GI_2018_species[order(GI_2018_species$SpeciesName),] %>% map_df(rev) -> GI_2018_species
```

## Map individuals from survey

### 2015-2016 Puget Sound Survey Map
```{r map_ESA_rockfishes_PS}
# Load shapefile data
usa_spdf <- readOGR(dsn = here("map_files", "USA_adm0.shp"))
usa_spdf_fort <- tidy(usa_spdf)

# Create base map
PS_map <- ggplot(usa_spdf_fort, aes(x = long, y = lat, group = group))+
  # Create grid using geom_vline and geom_hline
  # geom_vline(xintercept = seq(-123.1, min_lon, 1/nm), color = "gray50", size = 0.1)+
  # geom_hline(yintercept = seq(min_lat, 48.5, 1/60), color = "gray50", size = 0.1)+
  #base map
  geom_polygon(color = "gray20")+
  ylab("Latitude")+
  coord_fixed(ylim = c(47.1,48.25),  xlim = c(-123.1,-122.1), ratio = 1.3)+
  theme(plot.background = element_rect(fill = "white"),
        panel.grid = element_blank())

# Add locations
ESA_ROV_detections_map <- PS_map +
  geom_point(data = PS_15_16_species, aes(x = longitude, y = latitude, color = SpeciesName), inherit.aes = FALSE)

# ESA_ROV_detections_map

ggsave(paste0(fig_dir, "/PS_15_16_ROV_map.png"), ESA_ROV_detections_map, height = 8, width = 8)
```



## 2015-2016 Puget Sound Survey Analysis

Need to understand which transects are missing, and why

1) PS_15_16_species has species observations, linked to transect and segment number
2) PS_15_16_area_swept has the area swept totals for each transect
  - Missing some transects, since this is only for those transects that are "clipped"
```{r reformat_15_16_PS_survey_data}
PS_15_16_species %>% 
  # Rename "Transect" as "Tran_ID" to match area_swept sheet
  dplyr::rename(Tran_ID = Transect) -> PS_15_16_species

# Rename some transects
PS_15_16_species[PS_15_16_species$Tran_ID == "H560 Part 2",]$Tran_ID <- "H560"
PS_15_16_species[PS_15_16_species$Tran_ID == "H408 Part 2",]$Tran_ID <- "H408"

PS_15_16_area_swept
PS_15_16_segments
PS_15_16_linelengths_clipped
```

### Data exploration: Which transects appear to be missing?

Note: Survey design says that while 552 transects were planned in the "high" area, only 515 were completed

It says that they saw two bocaccio, but I only see one in the data
```{r explore_transects}
PS_15_16_transects <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "2015-16 PS Transects")
PS_15_16_transects_missingtimes <- read_excel(paste0(ROV_data_path, "/ROV_NOAAESA5yr_20210405.xlsx"), sheet = "Transects - Need Times")

PS_15_16_transects_missingtimes %>% 
  mutate(., missingtime = "TRUE") -> PS_15_16_transects_missingtimes

PS_15_16_transects %>% 
  mutate(., Survey = "2015-16 PS") %>% 
  mutate(., missingtime = "FALSE") %>% 
  dplyr::select(-AreaSwept) -> PS_15_16_transects

PS_15_16_transects %>% 
  bind_rows(., PS_15_16_transects_missingtimes) %>% 
  subset(., Survey == "2015-16 PS") -> PS_15_16_transects_all

PS_15_16_transects_all[order(PS_15_16_transects_all$Transect),] -> PS_15_16_transects_all

# Extract only the numeric part of the transect ID
PS_15_16_transects_all %>% 
  mutate(., transect_no = parse_number(Transect)) %>% 
  mutate(., transect_habitat = gsub("[0-9]","", Transect)) -> PS_15_16_transects_all

# Look at only high probability
PS_15_16_transects_all %>% 
  subset(., grepl("H", transect_habitat)) -> PS_15_16_high_transects

# Number of unique transects: 506. So missing 9?
length(unique(PS_15_16_high_transects$transect_no))

# Investigate which numbers are missing
numbers <- seq(1,600,1)
missing_transect_nos <- numbers[!numbers %in%  PS_15_16_high_transects$transect_no]

```


### Figure out which unclipped transects have ESA-listed species
```{r look_for_unclipped_transects_of_importance}
positive_transects <- unique(PS_15_16_species$Tran_ID)
clipped_transects <- unique(PS_15_16_linelengths_clipped$Tran_ID)

setdiff(positive_transects, clipped_transects)
# 560 is because it's divided into two parts, not an issue
# H408 is in the unclipped but not the clipped data; also says that it was found in H408 part 2

```

These transects aren't in the clipped or unclipped line lengths, but are found in the "segments" data:
- H177, H233, H259, H287, H307, H557
- None are identified in the "Transects - Need Times" sheet


### Estimate area swept for unclipped segments
```{r est_area_swept_unclipped}


```




### Calculate stratum density

The area swept for each transect ($A_i$) was the product of the mean transect width ($\overline{W_i}$) and the smoothed transect length ($L_i$).Taxon densities for individual transects ($D_i$) were estimated by dividing the species count ($C_i$) by the transect area:
$$
D_i = \frac{C_i} {L_i\overline{W_i}} = \frac{C_i} {\overline{A_i}}
$$

```{r calculate_taxon_densities_for_individual_transects}

```




The mean stratum density ($\overline{D_s}$) for a given taxon was then the sum of the individual transect densities divided by the number of transects ($N_s$):
$$
\overline{D_s} = \frac{\sum\limits_{i=1}^N D_i} {N_s}
$$
The variance of the mean stratum density was calculated as:
$$
Var(\overline{D_s}) = \frac{\sum\limits_{i=1}^N (D_i-\overline{D_s})^2} {N_s - 1}

$$


### Calculate abundance estimates

Total abundance ($P$) in numbers of individuals was the product of the stratum surface area ($SA_s$) and the mean taxon density ($D$), with variance calculated as the product of surface area and the variance of mean stratum density:
$$
P_s = SA_s\overline{D_s};Var(P_s) = SA_sVar(\overline{D_s})
$$

Coefficients of variation for each taxon (as percentages) were calculated as the standard deviation of mean stratum density ($\overline{D}$) divided by the product of the square root of the station count ($N$) multiplied by the mean stratum density ($\overline{D}$):

$$
CV = \frac{\sqrt{Var(\overline{D})}} {\sqrt{N}*\overline{D}} * 100
$$







