---
title: "SS_model_outputs_analysis"
author: "Markus Min"
date: "7/15/2021"
output: html_document
---

#### Description
To calculate values/parameters from the outputs from the stock synthesis models run by Jason Cope. Plots have already been generated, so here we are just extracting values to report in the 5-year review. Because of the size of the model outputs, they are not included in the uploaded data to GitHub but are available upon request.

```{r load_libraries}
library(tidyverse)
library(r4ss)
library(gplots)
library(here)
```


#### Load data
```{r load_yelloweye_USDPS}
# Change here directory to where SS outputs are stored
SS_dir <- "/Users/markusmin/Documents/ESA_RF_2021_SS_runs"

YE_USDPS_high_SS <- SS_output(paste0(SS_dir,"/YEY_USDPS", "/2021-07-15", "/YEY_USDPS_hi"),covar=FALSE,ncols=149)
YE_USDPS_medium_SS <- SS_output(paste0(SS_dir,"/YEY_USDPS", "/2021-07-15", "/YEY_USDPS_med"),covar=FALSE,ncols=149)
YE_USDPS_low_SS <- SS_output(paste0(SS_dir,"/YEY_USDPS", "/2021-07-15", "/YEY_USDPS_low"),covar=FALSE,ncols=149)

YE_USDPS_high_SS$timeseries
YE_USDPS_medium_SS$timeseries

base.summary.ye.usdps <- SSsummarize(list(YE_USDPS_high_SS, YE_USDPS_medium_SS, YE_USDPS_low_SS))
```

```{r load_yelloweye_HC}
YE_HC_high_SS <- SS_output(paste0(SS_dir,"/YEY_HC", "/2021-07-15", "/YEYE_HC_hi"),covar=FALSE,ncols=149)
YE_HC_medium_SS <- SS_output(paste0(SS_dir,"/YEY_HC", "/2021-07-15", "/YEYE_HC_med"),covar=FALSE,ncols=149)
YE_HC_low_SS <- SS_output(paste0(SS_dir,"/YEY_HC", "/2021-07-15", "/YEYE_HC_low"),covar=FALSE,ncols=149)

base.summary.ye.hc <- SSsummarize(list(YE_HC_high_SS, YE_HC_medium_SS, YE_HC_low_SS))
```

```{r load_bocaccio}
BOC_high_SS <- SS_output(paste0(SS_dir,"/Bocaccio", "/2021-07-15", "/Bocaccio_USDPS_high"),covar=FALSE,ncols=149)
BOC_medium_SS <- SS_output(paste0(SS_dir,"/Bocaccio", "/2021-07-15", "/Bocaccio_USDPS_med"),covar=FALSE,ncols=149)
BOC_low_SS <- SS_output(paste0(SS_dir,"/Bocaccio", "/2021-07-15", "/Bocaccio_USDPS_low"),covar=FALSE,ncols=149)

base.summary.boc <- SSsummarize(list(BOC_high_SS, BOC_medium_SS, BOC_low_SS))
```


### Get absolute spawning biomass estimates
```{r absolute_SSB_YE_USDPS}
# Get absolute spawning biomass
spbio_ye.usdps <- as.data.frame(base.summary.ye.usdps$SpawnBio)
colnames(spbio_ye.usdps) <- c("High", "Medium", "Low", "Label", "year")

# Get uncertainty in absolute spawning biomass
# The uncertainty appears to be symmetrical, leading to negative lower bounds:
as.data.frame(base.summary.ye.usdps$SpawnBioLower)

# Let's just take the upper bounds
spbio_upper_ye.usdps <- as.data.frame(base.summary.ye.usdps$SpawnBioUpper)
```


```{r absolute_SSB_YE_HC}
# Get absolute spawning biomass
spbio_ye.hc <- as.data.frame(base.summary.ye.hc$SpawnBio)
colnames(spbio_ye.hc) <- c("High", "Medium", "Low", "Label", "year")

# Get uncertainty in absolute spawning biomass
# The uncertainty appears to be symmetrical, leading to negative lower bounds:
as.data.frame(base.summary.ye.hc$SpawnBioLower)

# Let's just take the upper bounds
spbio_upper_ye.hc <- as.data.frame(base.summary.ye.hc$SpawnBioUpper)
```

```{r absolute_SSB_boc}
# Get absolute spawning biomass
spbio_boc <- as.data.frame(base.summary.boc$SpawnBio)
colnames(spbio_boc) <- c("High", "Medium", "Low", "Label", "year")

# Get uncertainty in absolute spawning biomass
# The uncertainty appears to be symmetrical, leading to negative lower bounds:
as.data.frame(base.summary.boc$SpawnBioLower)

# Let's just take the upper bounds
spbio_upper_boc <- as.data.frame(base.summary.boc$SpawnBioUpper)
```



### Get relative spawning biomass estimates
```{r relative_SSB_YE_USDPS}
# Get relative spawning biomass
rel_spbio_ye.usdps <- as.data.frame(base.summary.ye.usdps$Bratio)
colnames(rel_spbio_ye.usdps) <- c("High", "Medium", "Low", "Label", "year")

# Check what year model is estimating minimum abundance
rel_spbio_ye.usdps[rel_spbio_ye.usdps$High == min(rel_spbio_ye.usdps$High),]
rel_spbio_ye.usdps[rel_spbio_ye.usdps$Medium == min(rel_spbio_ye.usdps$Medium),]
rel_spbio_ye.usdps[rel_spbio_ye.usdps$Low == min(rel_spbio_ye.usdps$Low),]
# 1994 for the high and medium scenarios, 1992 for the low scenario

# Get uncertainty in relative spawning biomass
rel_spbio_lower_ye.usdps <- as.data.frame(base.summary.ye.usdps$BratioLower)
colnames(rel_spbio_lower_ye.usdps) <- c("High", "Medium", "Low", "Label", "year")
rel_spbio_upper_ye.usdps <- as.data.frame(base.summary.ye.usdps$BratioUpper)
colnames(rel_spbio_upper_ye.usdps) <- c("High", "Medium", "Low", "Label", "year")

# Get estimates for 2021
rel_spbio_lower_ye.usdps[rel_spbio_lower_ye.usdps$year == 2021,]
rel_spbio_upper_ye.usdps[rel_spbio_upper_ye.usdps$year == 2021,]
rel_spbio_ye.usdps[rel_spbio_ye.usdps$year == 2021,]

```

```{r relative_SSB_YE_HC}
# Get relative spawning biomass
rel_spbio_ye.hc <- as.data.frame(base.summary.ye.hc$Bratio)
colnames(rel_spbio_ye.hc) <- c("High", "Medium", "Low", "Label", "year")

# Check what year model is estimating minimum abundance
rel_spbio_ye.hc[rel_spbio_ye.hc$High == min(rel_spbio_ye.hc$High),]
rel_spbio_ye.hc[rel_spbio_ye.hc$Medium == min(rel_spbio_ye.hc$Medium),]
rel_spbio_ye.hc[rel_spbio_ye.hc$Low == min(rel_spbio_ye.hc$Low),]
# Estimates are all over the place - 1966, 1981, 1987 (high, medium, low)

# Get uncertainty in relative spawning biomass
rel_spbio_lower_ye.hc <- as.data.frame(base.summary.ye.hc$BratioLower)
colnames(rel_spbio_lower_ye.hc) <- c("High", "Medium", "Low", "Label", "year")
rel_spbio_upper_ye.hc <- as.data.frame(base.summary.ye.hc$BratioUpper)
colnames(rel_spbio_upper_ye.hc) <- c("High", "Medium", "Low", "Label", "year")

# Get estimates for 2021
rel_spbio_lower_ye.hc[rel_spbio_lower_ye.hc$year == 2021,]
rel_spbio_upper_ye.hc[rel_spbio_upper_ye.hc$year == 2021,]
rel_spbio_ye.hc[rel_spbio_ye.hc$year == 2021,]

```

```{r relative_SSB_bocaccio}
# Get relative spawning biomass
rel_spbio_boc <- as.data.frame(base.summary.boc$Bratio)
colnames(rel_spbio_boc) <- c("High", "Medium", "Low", "Label", "year")

# Check what year model is estimating minimum abundance
rel_spbio_boc[rel_spbio_boc$High == min(rel_spbio_boc$High),]
rel_spbio_boc[rel_spbio_boc$Medium == min(rel_spbio_boc$Medium),]
rel_spbio_boc[rel_spbio_boc$Low == min(rel_spbio_boc$Low),]
# 1992 for each, but the big drop really occurs 1979/1980

# Get uncertainty in relative spawning biomass
rel_spbio_lower_boc <- as.data.frame(base.summary.boc$BratioLower)
colnames(rel_spbio_lower_boc) <- c("High", "Medium", "Low", "Label", "year")
rel_spbio_upper_boc <- as.data.frame(base.summary.boc$BratioUpper)
colnames(rel_spbio_upper_boc) <- c("High", "Medium", "Low", "Label", "year")

# Get estimates for 2021
rel_spbio_lower_boc[rel_spbio_lower_boc$year == 2021,]
rel_spbio_upper_boc[rel_spbio_upper_boc$year == 2021,]
rel_spbio_boc[rel_spbio_boc$year == 2021,]

```










# Hood Canal - alternative models
```{r load_ye_HC_data}
# Load SS LO
SS_dir <- "/Users/markusmin/Documents/ESA_RF_2021_SS_runs"

YE_HC_LO <- SS_output(paste0(SS_dir,"/YEYE_HC_LO"),covar=FALSE,ncols=149)
# Get summary
base.summary.ye.ss_lo <- SSsummarize(list(YE_HC_LO))

# Load LBSPR
ye_HC_lbspr <- read.csv(paste0(SS_dir, "/LBSPR_Yelloweye_Hood_Canal_Ests.csv"))

```


## Get values from SS-LO
We have no sense of scale with the SS-LO model - therefore can only get relative points
```{r HC_SS_LO_ref_points}
# Get relative spawning biomass
rel_spbio_ye.hc_SS_LO <- as.data.frame(base.summary.ye.ss_lo$Bratio)

# Get uncertainty in relative spawning biomass
rel_spbio_upper_ye.hc_SS_LO <- as.data.frame(base.summary.ye.ss_lo$BratioUpper)
rel_spbio_lower_ye.hc_SS_LO <- as.data.frame(base.summary.ye.ss_lo$BratioLower)
```

